---
title: "Plots Effects of Contraception"
output:
  html_document:
    toc: true
    toc_depth: 4
    toc_float: true
    code_folding: 'hide'
    self_contained: false
---
  
  
## Data 
```{r results='hide',message=F,warning=F}
source("0_helpers.R")

load("data/cleaned_selected_wrangled.rdata")
```

## Select
```{r}
data = data %>%
  filter(!(contraception_method %contains% "hormonal_other"))
  
```

## Effects of Hormonal Contraceptives {.tabset}
### Uncontrolled
#### Models
```{r}
m_hc_atrr = brm(attractiveness_partner ~ contraception_hormonal,
                data = data, family = gaussian())
m_hc_relsat = brm(relationship_satisfaction ~ contraception_hormonal,
                data = data, family = gaussian())
m_hc_sexsat = brm(satisfaction_sexual_intercourse ~ contraception_hormonal,
                data = data, family = gaussian())
m_hc_libido = brm(diary_libido_mean ~ contraception_hormonal,
                data = data, family = gaussian())
m_hc_sexfreqpen = brm(diary_sex_active_sex_sum ~
                        offset(log(number_of_days)) +
                        contraception_hormonal,
                data = data, family = poisson())
m_hc_masfreq = brm(diary_masturbation_sum ~ offset(log(number_of_days)) +
                     contraception_hormonal,
                data = data, family = poisson())
```

#### Forest Plot for Effect Sizes {.active}
```{r}
models = rbind(
  m_hc_atrr %>%
    spread_draws(b_contraception_hormonalyes) %>%
    pivot_longer(cols = c(b_contraception_hormonalyes),
                 names_to = "condition",
                 values_to = "r_condition") %>%
    mutate(model = "Perceived Partner Attractiveness\nROPE = [-0.07, 0.07]",
           ROPE = 0.07),
  m_hc_relsat %>%
    spread_draws(b_contraception_hormonalyes) %>%
    pivot_longer(cols = c(b_contraception_hormonalyes),
                 names_to = "condition",
                 values_to = "r_condition") %>%
    mutate(model = "Relationship Satisfaction\nROPE = [-0.04, 0.04]",
           ROPE = 0.04),
  m_hc_sexsat %>%
    spread_draws(b_contraception_hormonalyes) %>%
    pivot_longer(cols = c(b_contraception_hormonalyes),
                 names_to = "condition",
                 values_to = "r_condition") %>%
    mutate(model = "Sexual Satisfaction\nROPE = [-0.11, 0.11]",
           ROPE = 0.11),
  m_hc_libido %>%
    spread_draws(b_contraception_hormonalyes) %>%
    pivot_longer(cols = c(b_contraception_hormonalyes),
                 names_to = "condition",
                 values_to = "r_condition") %>%
    mutate(model = "Libido\nROPE = [-0.06, 0.06]",
           ROPE = 0.06),
  m_hc_sexfreqpen %>%
    spread_draws(b_contraception_hormonalyes) %>%
    pivot_longer(cols = c(b_contraception_hormonalyes),
                 names_to = "condition",
                 values_to = "r_condition") %>%
    mutate(model = "Frequency of Vaginal Intercourse\nROPE = [-0.05, 0.05]",
           ROPE = 0.05),
  m_hc_masfreq %>%
    spread_draws(b_contraception_hormonalyes) %>%
    pivot_longer(cols = c(b_contraception_hormonalyes),
                 names_to = "condition",
                 values_to = "r_condition") %>%
    mutate(model = "Frequency of Masturbation\nROPE = [-0.05, 0.05]",
           ROPE = 0.05))

data1 = models %>%
  mutate(model = factor(model,
                   levels = c("Frequency of Masturbation\nROPE = [-0.05, 0.05]",
                              "Frequency of Vaginal Intercourse\nROPE = [-0.05, 0.05]",
                              "Libido\nROPE = [-0.06, 0.06]",
                              "Sexual Satisfaction\nROPE = [-0.11, 0.11]",
                              "Relationship Satisfaction\nROPE = [-0.04, 0.04]",
                              "Perceived Partner Attractiveness\nROPE = [-0.07, 0.07]")))
data2 = models %>%
  group_by(model, ROPE) %>%
  mutate(model = factor(model,
                        levels = c("Frequency of Masturbation\nROPE = [-0.05, 0.05]",
                                   "Frequency of Vaginal Intercourse\nROPE = [-0.05, 0.05]",
                                   "Libido\nROPE = [-0.06, 0.06]",
                                   "Sexual Satisfaction\nROPE = [-0.11, 0.11]",
                                   "Relationship Satisfaction\nROPE = [-0.04, 0.04]",
                                   "Perceived Partner Attractiveness\nROPE = [-0.07, 0.07]"))) %>%
  mean_qi(condition_mean = r_condition,
          .width = c(.90)) %>%
  mutate(text = ifelse(.width == .90,
                       str_c(round(condition_mean, 2),
                             " [",
                             round(.lower, 2),
                             "; ",
                             round(.upper, 2),
                             "]"), NA),
         sig = ifelse(.lower > ROPE | .upper < -ROPE, T, F))


hc_uncontrolled = ggplot() +
  stat_halfeye(data = data1,
               aes(y = model, x = r_condition,
                   color = "grey"),
               .width = .90) +
  geom_vline(xintercept = 0, linetype = "dotted") +
  geom_pointinterval(data = data2,
                     aes(y = model,
                         x = condition_mean,
                         xmin = .lower,
                         xmax = .upper,
                         color = sig)) +
  geom_point(data = data1, aes(y = model, x = ROPE), shape = "|", size = 10, color = "black") +
  geom_point(data = data1, aes(y = model, x = -ROPE), shape = "|", size = 10, color = "black") +
  geom_point(data = data1, aes(y = model, x = ROPE), shape = 58, size = 10, color = "white") +
  geom_point(data = data1, aes(y = model, x = -ROPE), shape = 58, size = 10, color = "white") +
  apatheme +
  scale_color_manual(data2, values = c("skyblue", "grey", "red")) +
  scale_x_continuous(breaks = c(-0.5, -0.4, -0.3, -0.2, -0.1, 0, 0.1, 0.2, 0.3, 0.4, 0.5),
                     limits = c(-0.5, 0.5)) +
  labs(x = "Effect Size Estimates of Hormonal Contraception", y = "Outcomes") +
  theme_tufte(base_size = 10) +
  theme(legend.position = "none")
hc_uncontrolled
```

### Controlled
#### Models
```{r}
m_hc_atrr_controlled = brm(attractiveness_partner ~ contraception_hormonal +
                             age + net_income + relationship_duration_factor +
                              education_years +
                              bfi_extra + bfi_neuro + bfi_agree + bfi_consc + bfi_open +
                              religiosity,
                data = data, family = gaussian())

m_hc_relsat_controlled = brm(relationship_satisfaction ~ contraception_hormonal +
                             age + net_income + relationship_duration_factor +
                              education_years +
                              bfi_extra + bfi_neuro + bfi_agree + bfi_consc + bfi_open +
                              religiosity,
                data = data, family = gaussian())

m_hc_sexsat_controlled = brm(satisfaction_sexual_intercourse ~ contraception_hormonal +
                             age + net_income + relationship_duration_factor +
                              education_years +
                              bfi_extra + bfi_neuro + bfi_agree + bfi_consc + bfi_open +
                              religiosity,
                data = data, family = gaussian())

m_hc_libido_controlled = brm(diary_libido_mean ~ contraception_hormonal +
                             age + net_income + relationship_duration_factor +
                              education_years +
                              bfi_extra + bfi_neuro + bfi_agree + bfi_consc + bfi_open +
                              religiosity,
                data = data, family = gaussian())

m_hc_sexfreqpen_controlled = brm(diary_sex_active_sex_sum ~
                        offset(log(number_of_days)) +
                        contraception_hormonal +
                        age + net_income + relationship_duration_factor +
                              education_years +
                              bfi_extra + bfi_neuro + bfi_agree + bfi_consc + bfi_open +
                              religiosity,
                data = data, family = poisson())

m_hc_masfreq_controlled = brm(diary_masturbation_sum ~
                        offset(log(number_of_days)) +
                        contraception_hormonal +
                        age + net_income + relationship_duration_factor +
                              education_years +
                              bfi_extra + bfi_neuro + bfi_agree + bfi_consc + bfi_open +
                              religiosity,
                data = data, family = poisson())
```

#### Forest Plot for Effect Sizes {.active}
```{r}
models = rbind(
  m_hc_atrr_controlled %>%
    spread_draws(b_contraception_hormonalyes) %>%
    pivot_longer(cols = c(b_contraception_hormonalyes),
                 names_to = "condition",
                 values_to = "r_condition") %>%
    mutate(model = "Perceived Partner Attractiveness\nROPE = [-0.07, 0.07]",
           ROPE = 0.07),
  m_hc_relsat_controlled %>%
    spread_draws(b_contraception_hormonalyes) %>%
    pivot_longer(cols = c(b_contraception_hormonalyes),
                 names_to = "condition",
                 values_to = "r_condition") %>%
    mutate(model = "Relationship Satisfaction\nROPE = [-0.04, 0.04]",
           ROPE = 0.04),
  m_hc_sexsat_controlled %>%
    spread_draws(b_contraception_hormonalyes) %>%
    pivot_longer(cols = c(b_contraception_hormonalyes),
                 names_to = "condition",
                 values_to = "r_condition") %>%
    mutate(model = "Sexual Satisfaction\nROPE = [-0.11, 0.11]",
           ROPE = 0.11),
  m_hc_libido_controlled %>%
    spread_draws(b_contraception_hormonalyes) %>%
    pivot_longer(cols = c(b_contraception_hormonalyes),
                 names_to = "condition",
                 values_to = "r_condition") %>%
    mutate(model = "Libido\nROPE = [-0.06, 0.06]",
           ROPE = 0.06),
  m_hc_sexfreqpen_controlled %>%
    spread_draws(b_contraception_hormonalyes) %>%
    pivot_longer(cols = c(b_contraception_hormonalyes),
                 names_to = "condition",
                 values_to = "r_condition") %>%
    mutate(model = "Frequency of Vaginal Intercourse\nROPE = [-0.05, 0.05]",
           ROPE = 0.05),
  m_hc_masfreq_controlled %>%
    spread_draws(b_contraception_hormonalyes) %>%
    pivot_longer(cols = c(b_contraception_hormonalyes),
                 names_to = "condition",
                 values_to = "r_condition") %>%
    mutate(model = "Frequency of Masturbation\nROPE = [-0.05, 0.05]",
           ROPE = 0.05))

data1 = models %>%
  mutate(model = factor(model,
                   levels = c("Frequency of Masturbation\nROPE = [-0.05, 0.05]",
                              "Frequency of Vaginal Intercourse\nROPE = [-0.05, 0.05]",
                              "Libido\nROPE = [-0.06, 0.06]",
                              "Sexual Satisfaction\nROPE = [-0.11, 0.11]",
                              "Relationship Satisfaction\nROPE = [-0.04, 0.04]",
                              "Perceived Partner Attractiveness\nROPE = [-0.07, 0.07]")))
data2 = models %>%
  group_by(model, ROPE) %>%
  mutate(model = factor(model,
                        levels = c("Frequency of Masturbation\nROPE = [-0.05, 0.05]",
                                   "Frequency of Vaginal Intercourse\nROPE = [-0.05, 0.05]",
                                   "Libido\nROPE = [-0.06, 0.06]",
                                   "Sexual Satisfaction\nROPE = [-0.11, 0.11]",
                                   "Relationship Satisfaction\nROPE = [-0.04, 0.04]",
                                   "Perceived Partner Attractiveness\nROPE = [-0.07, 0.07]"))) %>%
  mean_qi(condition_mean = r_condition,
          .width = c(.90)) %>%
  mutate(text = ifelse(.width == .90,
                       str_c(round(condition_mean, 2),
                             " [",
                             round(.lower, 2),
                             "; ",
                             round(.upper, 2),
                             "]"), NA),
         sig = ifelse(.lower > ROPE | .upper < -ROPE, "declined",
                      ifelse(abs(.lower) < ROPE  & .upper > ROPE, "undecidable", "accepted")))


hc_controlled = ggplot() +
  stat_halfeye(data = data1,
               aes(y = model, x = r_condition,
                   color = "grey"),
               .width = .90) +
  geom_vline(xintercept = 0, linetype = "dotted") +
  geom_pointinterval(data = data2,
                     aes(y = model,
                         x = condition_mean,
                         xmin = .lower,
                         xmax = .upper,
                         color = sig)) +
  geom_point(data = data1, aes(y = model, x = ROPE), shape = "|", size = 10, color = "black") +
  geom_point(data = data1, aes(y = model, x = -ROPE), shape = "|", size = 10, color = "black") +
  geom_point(data = data1, aes(y = model, x = ROPE), shape = 58, size = 10, color = "white") +
  geom_point(data = data1, aes(y = model, x = -ROPE), shape = 58, size = 10, color = "white") +
  apatheme +
  theme(legend.position = "none") +
  scale_color_manual(values = c("red", "green", "skyblue", "grey")) +
  scale_x_continuous(breaks = c(-0.5, -0.4, -0.3, -0.2, -0.1, 0, 0.1, 0.2, 0.3, 0.4, 0.5),
                     limits = c(-0.5, 0.5)) +
  labs(x = "Effect Size Estimates of Hormonal Contraception", y = "Outcomes")  +
  theme_tufte(base_size = 10) +   theme(legend.position = "none")
hc_controlled
```

### Combine Plots
```{r}
hc_plots =
  ggarrange(hc_uncontrolled + theme(plot.margin = margin(1,0,0,0,"cm")),
            hc_controlled + theme(plot.margin = margin(3,0,0,0,"cm")),
          labels = c("Uncontrolled Model", "\nControlled Model"),
          font.label = list(size = 20, color = "black", face = "bold", family = "sans"),
          hjust = -0.1,
          ncol = 1, nrow = 2,
          align = "v")

hc_plots
jpeg('Effect size estimates for hormonal contraceptives on outcomes.jpg', 
     width = 800, height = 1000, quality = 100)
hc_plots
dev.off()
```

## Select
```{r}
load("data/cleaned_selected_wrangled.rdata")
data = data %>%
  filter(!(contraception_method %contains% "hormonal_pill"))
  
```

## Effects of Hormonal Contraceptives {.tabset}
### Uncontrolled
#### Models
```{r}
m_hc_atrr = brm(attractiveness_partner ~ contraception_hormonal,
                data = data, family = gaussian())
m_hc_relsat = brm(relationship_satisfaction ~ contraception_hormonal,
                data = data, family = gaussian())
m_hc_sexsat = brm(satisfaction_sexual_intercourse ~ contraception_hormonal,
                data = data, family = gaussian())
m_hc_libido = brm(diary_libido_mean ~ contraception_hormonal,
                data = data, family = gaussian())
m_hc_sexfreqpen = brm(diary_sex_active_sex_sum ~
                        offset(log(number_of_days)) +
                        contraception_hormonal,
                data = data, family = poisson())
m_hc_masfreq = brm(diary_masturbation_sum ~ offset(log(number_of_days)) +
                     contraception_hormonal,
                data = data, family = poisson())
```

#### Forest Plot for Effect Sizes {.active}
```{r}
models = rbind(
  m_hc_atrr %>%
    spread_draws(b_contraception_hormonalyes) %>%
    pivot_longer(cols = c(b_contraception_hormonalyes),
                 names_to = "condition",
                 values_to = "r_condition") %>%
    mutate(model = "Perceived Partner Attractiveness\nROPE = [-0.07, 0.07]",
           ROPE = 0.07),
  m_hc_relsat %>%
    spread_draws(b_contraception_hormonalyes) %>%
    pivot_longer(cols = c(b_contraception_hormonalyes),
                 names_to = "condition",
                 values_to = "r_condition") %>%
    mutate(model = "Relationship Satisfaction\nROPE = [-0.04, 0.04]",
           ROPE = 0.04),
  m_hc_sexsat %>%
    spread_draws(b_contraception_hormonalyes) %>%
    pivot_longer(cols = c(b_contraception_hormonalyes),
                 names_to = "condition",
                 values_to = "r_condition") %>%
    mutate(model = "Sexual Satisfaction\nROPE = [-0.11, 0.11]",
           ROPE = 0.11),
  m_hc_libido %>%
    spread_draws(b_contraception_hormonalyes) %>%
    pivot_longer(cols = c(b_contraception_hormonalyes),
                 names_to = "condition",
                 values_to = "r_condition") %>%
    mutate(model = "Libido\nROPE = [-0.06, 0.06]",
           ROPE = 0.06),
  m_hc_sexfreqpen %>%
    spread_draws(b_contraception_hormonalyes) %>%
    pivot_longer(cols = c(b_contraception_hormonalyes),
                 names_to = "condition",
                 values_to = "r_condition") %>%
    mutate(model = "Frequency of Vaginal Intercourse\nROPE = [-0.05, 0.05]",
           ROPE = 0.05),
  m_hc_masfreq %>%
    spread_draws(b_contraception_hormonalyes) %>%
    pivot_longer(cols = c(b_contraception_hormonalyes),
                 names_to = "condition",
                 values_to = "r_condition") %>%
    mutate(model = "Frequency of Masturbation\nROPE = [-0.05, 0.05]",
           ROPE = 0.05))

data1 = models %>%
  mutate(model = factor(model,
                   levels = c("Frequency of Masturbation\nROPE = [-0.05, 0.05]",
                              "Frequency of Vaginal Intercourse\nROPE = [-0.05, 0.05]",
                              "Libido\nROPE = [-0.06, 0.06]",
                              "Sexual Satisfaction\nROPE = [-0.11, 0.11]",
                              "Relationship Satisfaction\nROPE = [-0.04, 0.04]",
                              "Perceived Partner Attractiveness\nROPE = [-0.07, 0.07]")))
data2 = models %>%
  group_by(model, ROPE) %>%
  mutate(model = factor(model,
                        levels = c("Frequency of Masturbation\nROPE = [-0.05, 0.05]",
                                   "Frequency of Vaginal Intercourse\nROPE = [-0.05, 0.05]",
                                   "Libido\nROPE = [-0.06, 0.06]",
                                   "Sexual Satisfaction\nROPE = [-0.11, 0.11]",
                                   "Relationship Satisfaction\nROPE = [-0.04, 0.04]",
                                   "Perceived Partner Attractiveness\nROPE = [-0.07, 0.07]"))) %>%
  mean_qi(condition_mean = r_condition,
          .width = c(.90)) %>%
  mutate(text = ifelse(.width == .90,
                       str_c(round(condition_mean, 2),
                             " [",
                             round(.lower, 2),
                             "; ",
                             round(.upper, 2),
                             "]"), NA),
         sig = ifelse(.lower > ROPE | .upper < -ROPE, T, F))


hc_uncontrolled = ggplot() +
  stat_halfeye(data = data1,
               aes(y = model, x = r_condition,
                   color = "grey"),
               .width = .90) +
  geom_vline(xintercept = 0, linetype = "dotted") +
  geom_pointinterval(data = data2,
                     aes(y = model,
                         x = condition_mean,
                         xmin = .lower,
                         xmax = .upper,
                         color = sig)) +
  geom_point(data = data1, aes(y = model, x = ROPE), shape = "|", size = 10, color = "black") +
  geom_point(data = data1, aes(y = model, x = -ROPE), shape = "|", size = 10, color = "black") +
  geom_point(data = data1, aes(y = model, x = ROPE), shape = 58, size = 10, color = "white") +
  geom_point(data = data1, aes(y = model, x = -ROPE), shape = 58, size = 10, color = "white") +
  apatheme +
  scale_color_manual(data2, values = c("skyblue", "grey", "red")) +
  scale_x_continuous(breaks = c(-0.5, -0.4, -0.3, -0.2, -0.1, 0, 0.1, 0.2, 0.3, 0.4, 0.5),
                     limits = c(-0.5, 0.5)) +
  labs(x = "Effect Size Estimates of Hormonal Contraception", y = "Outcomes") +
  theme_tufte(base_size = 10) +
  theme(legend.position = "none")
hc_uncontrolled
```

### Controlled
#### Models
```{r}
m_hc_atrr_controlled = brm(attractiveness_partner ~ contraception_hormonal +
                             age + net_income + relationship_duration_factor +
                              education_years +
                              bfi_extra + bfi_neuro + bfi_agree + bfi_consc + bfi_open +
                              religiosity,
                data = data, family = gaussian())

m_hc_relsat_controlled = brm(relationship_satisfaction ~ contraception_hormonal +
                             age + net_income + relationship_duration_factor +
                              education_years +
                              bfi_extra + bfi_neuro + bfi_agree + bfi_consc + bfi_open +
                              religiosity,
                data = data, family = gaussian())

m_hc_sexsat_controlled = brm(satisfaction_sexual_intercourse ~ contraception_hormonal +
                             age + net_income + relationship_duration_factor +
                              education_years +
                              bfi_extra + bfi_neuro + bfi_agree + bfi_consc + bfi_open +
                              religiosity,
                data = data, family = gaussian())

m_hc_libido_controlled = brm(diary_libido_mean ~ contraception_hormonal +
                             age + net_income + relationship_duration_factor +
                              education_years +
                              bfi_extra + bfi_neuro + bfi_agree + bfi_consc + bfi_open +
                              religiosity,
                data = data, family = gaussian())

m_hc_sexfreqpen_controlled = brm(diary_sex_active_sex_sum ~
                        offset(log(number_of_days)) +
                        contraception_hormonal +
                        age + net_income + relationship_duration_factor +
                              education_years +
                              bfi_extra + bfi_neuro + bfi_agree + bfi_consc + bfi_open +
                              religiosity,
                data = data, family = poisson())

m_hc_masfreq_controlled = brm(diary_masturbation_sum ~
                        offset(log(number_of_days)) +
                        contraception_hormonal +
                        age + net_income + relationship_duration_factor +
                              education_years +
                              bfi_extra + bfi_neuro + bfi_agree + bfi_consc + bfi_open +
                              religiosity,
                data = data, family = poisson())
```

#### Forest Plot for Effect Sizes {.active}
```{r}
models = rbind(
  m_hc_atrr_controlled %>%
    spread_draws(b_contraception_hormonalyes) %>%
    pivot_longer(cols = c(b_contraception_hormonalyes),
                 names_to = "condition",
                 values_to = "r_condition") %>%
    mutate(model = "Perceived Partner Attractiveness\nROPE = [-0.07, 0.07]",
           ROPE = 0.07),
  m_hc_relsat_controlled %>%
    spread_draws(b_contraception_hormonalyes) %>%
    pivot_longer(cols = c(b_contraception_hormonalyes),
                 names_to = "condition",
                 values_to = "r_condition") %>%
    mutate(model = "Relationship Satisfaction\nROPE = [-0.04, 0.04]",
           ROPE = 0.04),
  m_hc_sexsat_controlled %>%
    spread_draws(b_contraception_hormonalyes) %>%
    pivot_longer(cols = c(b_contraception_hormonalyes),
                 names_to = "condition",
                 values_to = "r_condition") %>%
    mutate(model = "Sexual Satisfaction\nROPE = [-0.11, 0.11]",
           ROPE = 0.11),
  m_hc_libido_controlled %>%
    spread_draws(b_contraception_hormonalyes) %>%
    pivot_longer(cols = c(b_contraception_hormonalyes),
                 names_to = "condition",
                 values_to = "r_condition") %>%
    mutate(model = "Libido\nROPE = [-0.06, 0.06]",
           ROPE = 0.06),
  m_hc_sexfreqpen_controlled %>%
    spread_draws(b_contraception_hormonalyes) %>%
    pivot_longer(cols = c(b_contraception_hormonalyes),
                 names_to = "condition",
                 values_to = "r_condition") %>%
    mutate(model = "Frequency of Vaginal Intercourse\nROPE = [-0.05, 0.05]",
           ROPE = 0.05),
  m_hc_masfreq_controlled %>%
    spread_draws(b_contraception_hormonalyes) %>%
    pivot_longer(cols = c(b_contraception_hormonalyes),
                 names_to = "condition",
                 values_to = "r_condition") %>%
    mutate(model = "Frequency of Masturbation\nROPE = [-0.05, 0.05]",
           ROPE = 0.05))

data1 = models %>%
  mutate(model = factor(model,
                   levels = c("Frequency of Masturbation\nROPE = [-0.05, 0.05]",
                              "Frequency of Vaginal Intercourse\nROPE = [-0.05, 0.05]",
                              "Libido\nROPE = [-0.06, 0.06]",
                              "Sexual Satisfaction\nROPE = [-0.11, 0.11]",
                              "Relationship Satisfaction\nROPE = [-0.04, 0.04]",
                              "Perceived Partner Attractiveness\nROPE = [-0.07, 0.07]")))
data2 = models %>%
  group_by(model, ROPE) %>%
  mutate(model = factor(model,
                        levels = c("Frequency of Masturbation\nROPE = [-0.05, 0.05]",
                                   "Frequency of Vaginal Intercourse\nROPE = [-0.05, 0.05]",
                                   "Libido\nROPE = [-0.06, 0.06]",
                                   "Sexual Satisfaction\nROPE = [-0.11, 0.11]",
                                   "Relationship Satisfaction\nROPE = [-0.04, 0.04]",
                                   "Perceived Partner Attractiveness\nROPE = [-0.07, 0.07]"))) %>%
  mean_qi(condition_mean = r_condition,
          .width = c(.90)) %>%
  mutate(text = ifelse(.width == .90,
                       str_c(round(condition_mean, 2),
                             " [",
                             round(.lower, 2),
                             "; ",
                             round(.upper, 2),
                             "]"), NA),
         sig = ifelse(.lower > ROPE | .upper < -ROPE, "declined",
                      ifelse(abs(.lower) < ROPE  & .upper > ROPE, "undecidable", "accepted")))


hc_controlled = ggplot() +
  stat_halfeye(data = data1,
               aes(y = model, x = r_condition,
                   color = "grey"),
               .width = .90) +
  geom_vline(xintercept = 0, linetype = "dotted") +
  geom_pointinterval(data = data2,
                     aes(y = model,
                         x = condition_mean,
                         xmin = .lower,
                         xmax = .upper,
                         color = sig)) +
  geom_point(data = data1, aes(y = model, x = ROPE), shape = "|", size = 10, color = "black") +
  geom_point(data = data1, aes(y = model, x = -ROPE), shape = "|", size = 10, color = "black") +
  geom_point(data = data1, aes(y = model, x = ROPE), shape = 58, size = 10, color = "white") +
  geom_point(data = data1, aes(y = model, x = -ROPE), shape = 58, size = 10, color = "white") +
  apatheme +
  theme(legend.position = "none") +
  scale_color_manual(values = c("red", "green", "skyblue", "grey")) +
  scale_x_continuous(breaks = c(-0.5, -0.4, -0.3, -0.2, -0.1, 0, 0.1, 0.2, 0.3, 0.4, 0.5),
                     limits = c(-0.5, 0.5)) +
  labs(x = "Effect Size Estimates of Hormonal Contraception", y = "Outcomes")  +
  theme_tufte(base_size = 10) +   theme(legend.position = "none")
hc_controlled
```

### Combine Plots
```{r}
hc_plots =
  ggarrange(hc_uncontrolled + theme(plot.margin = margin(1,0,0,0,"cm")),
            hc_controlled + theme(plot.margin = margin(3,0,0,0,"cm")),
          labels = c("Uncontrolled Model", "\nControlled Model"),
          font.label = list(size = 20, color = "black", face = "bold", family = "sans"),
          hjust = -0.1,
          ncol = 1, nrow = 2,
          align = "v")

hc_plots
jpeg('Effect size estimates for hormonal contraceptives on outcomes.jpg', 
     width = 800, height = 1000, quality = 100)
hc_plots
dev.off()
```

