---
title: "Problem for Sensitivity Analysis"
output:
  html_document:
    toc: true
    toc_depth: 4
    toc_float: true
    code_folding: 'hide'
    self_contained: false
---

## Data 
```{r results='hide',message=F,warning=F}
source("0_helpers.R")

load("data/cleaned_selected_wrangled.rdata")
```

## Description
diary_sex_active_sex_sum: Sum of all  sexual active days (piv-sex).
diary_masturbation_sum: Sum of all masturbation active days.
diary_sex_active_sex_mean: Proportion of sexual active days (piv_sex)
diary_masturbation_mean: Proportion of masturbation active days.
number_of_days: Number of diary days filled out.



## Preparations
### Sex freq / number of days
```{r}
data = data %>%
  mutate(diary_sex_active_sex_freq = diary_sex_active_sex_sum/number_of_days,
         diary_masturbation_freq = diary_masturbation_sum/number_of_days)
```

### Change factors to numerics, handcode interaction
```{r}
data = data %>%
  mutate(contraception_hormonal_numeric = ifelse(contraception_hormonal == "yes",
                                                 1,
                                                 ifelse(contraception_hormonal == "no",
                                                        0, NA)),
         congruent_contraception_numeric = ifelse(congruent_contraception == "0",
                                                  0,
                                                  ifelse(congruent_contraception == "1",
                                                         1, NA)),
         hc_con_interaction = ifelse(is.na(congruent_contraception), NA,
                                     ifelse(contraception_hormonal == "yes" &
                                              congruent_contraception == "1", 1, 0)))
```


### Covariates
```{r}
covariates = list("age",
                   "net_incomeeuro_500_1000", "net_incomeeuro_1000_2000",
                   "net_incomeeuro_2000_3000", "net_incomeeuro_gt_3000",
                    "net_incomedont_tell",
                   "relationship_duration_factorPartnered_upto28months",
                   "relationship_duration_factorPartnered_upto52months",
                   "relationship_duration_factorPartnered_morethan52months",
                   "education_years", "bfi_extra", "bfi_neuro", "bfi_agree",
                   "bfi_consc", "bfi_open", "religiosity")
names(covariates) = c("age",
                   "net_incomeeuro_500_1000", "net_incomeeuro_1000_2000",
                   "net_incomeeuro_2000_3000", "net_incomeeuro_gt_3000",
                    "net_incomedont_tell",
                   "relationship_duration_factorPartnered_upto28months",
                   "relationship_duration_factorPartnered_upto52months",
                   "relationship_duration_factorPartnered_morethan52months",
                   "education_years", "bfi_extra", "bfi_neuro", "bfi_agree",
                   "bfi_consc", "bfi_open", "religiosity")
```

## Investigate
```{r}
qplot(data$diary_sex_active_sex_sum)
summary(data$diary_sex_active_sex_sum)

qplot(data$diary_masturbation_sum)
summary(data$diary_masturbation_sum)

qplot(data$diary_sex_active_sex_mean)
summary(data$diary_sex_active_sex_mean)

qplot(data$diary_masturbation_mean)
summary(data$diary_masturbation_mean)

cor.test(data$diary_sex_active_sex_sum, data$diary_sex_active_sex_mean)
cor.test(data$diary_masturbation_sum, data$diary_masturbation_mean)


```

### Difference between mean and freq variable
```{r}
qplot(data$diary_sex_active_sex_mean, data$diary_sex_active_sex_freq)
qplot(data$diary_masturbation_mean, data$diary_masturbation_freq)

investigation007 = data %>% select(session, diary_sex_active_sex_sum, diary_sex_active_sex_mean, diary_sex_active_sex_freq,
                                   diary_masturbation_sum, diary_masturbation_mean, diary_masturbation_freq,
                                   number_of_days)

investigation007_sex = investigation007 %>% filter(diary_sex_active_sex_mean != diary_sex_active_sex_freq)
investigation007_mas = investigation007 %>% filter(diary_masturbation_mean != diary_masturbation_freq)


data_diary_1 = data_diary %>% filter(session == "1unjd9r8gR6pOFAA5NkKJEc9WtIqnZ2269y-TmVZ6sBQIIHZjx-_EtAJuDB6euO6")
data_diary_means_1 = data_diary_means %>% filter(session == "1unjd9r8gR6pOFAA5NkKJEc9WtIqnZ2269y-TmVZ6sBQIIHZjx-_EtAJuDB6euO6")
table(data_diary_1$sex_activity_sex)
```

## Models {.tabset .active}
### Poisson
#### Controlled
##### Model
```{r}
m_hc_sexfreqpen = glm(diary_sex_active_sex_sum ~
                        offset(log(number_of_days)) +
                        contraception_hormonal_numeric,
                data = data, family = poisson())
qplot(residuals(m_hc_sexfreqpen))
```

##### Summary
```{r}
kable(tidy(m_hc_sexfreqpen, intervals = T, prob = 0.90))
summary(m_hc_sexfreqpen, intervals = T, prob = 0.90)
```

##### Sensitivity 
```{r}
m_hc_sexfreqpen_sensitivity <- sensemakr(estimate = 0.2496,
                                         se = 0.0248,
                                         dof = 895,
                                         treatment = "contraception_hormonal_numeric",
                                         kd = 1:3, #these arguments parameterize how many times
                                          #stronger the confounder is related to the
                                          #treatment
                                ky = 1:3, #these arguments parameterize how many times
                                          #stronger the confounder is related to the outcome
                                q = 1, #fraction of the effect estimate that would have to be
                                       #explained away to be problematic. Setting q = 1,
                                       #means that a reduction of 100% of the current effect
                                       #estimate, that is, a true effect of zero, would be
                                       #deemed problematic.
                                alpha = 0.05,
                                reduce = TRUE #confounder reduce absolute effect size
                                )

m_hc_sexfreqpen_sensitivity
summary(m_hc_sexfreqpen_sensitivity)
```

#### Controlled Model
##### Model
```{r}
m_hc_sexfreqpen = glm(formula = diary_sex_active_sex_sum ~ offset(log(number_of_days)) + 
     contraception_hormonal_numeric + age + net_income + relationship_duration_factor + 
     education_years + bfi_extra + bfi_neuro + bfi_agree + bfi_consc + 
     bfi_open + religiosity, family = "poisson", data = data)
```

##### Summary
```{r}
kable(tidy(m_hc_sexfreqpen, intervals = T, prob = 0.90))
summary(m_hc_sexfreqpen, intervals = T, prob = 0.90)
```

##### Sensitivity 
```{r}
m_hc_sexfreqpen_sensitivity <- sensemakr(estimate = 0.165323,
                                         se = 0.026331,
                                         dof = 878,
                                         treatment = "contraception_hormonal_numeric",
                                         benchmark_covariates = covariates, #covariates that will be
                                                                   #used to bound the
                                                                   #plausible strength of the
                                                                   #unobserved confounders
                                kd = 1:3, #these arguments parameterize how many times
                                          #stronger the confounder is related to the
                                          #treatment
                                ky = 1:3, #these arguments parameterize how many times
                                          #stronger the confounder is related to the outcome
                                q = 1, #fraction of the effect estimate that would have to be
                                       #explained away to be problematic. Setting q = 1,
                                       #means that a reduction of 100% of the current effect
                                       #estimate, that is, a true effect of zero, would be
                                       #deemed problematic.
                                alpha = 0.05,
                                reduce = TRUE #confounder reduce absolute effect size
                                )

m_hc_sexfreqpen_sensitivity
summary(m_hc_sexfreqpen_sensitivity)
```


### Linear
#### Uncontrolled
##### Model
```{r}
m_hc_sexfreqpen_linear = lm(diary_sex_active_sex_mean ~ contraception_hormonal_numeric,
               data = data)
```

##### Summary
```{r}
kable(tidy(m_hc_sexfreqpen_linear, intervals = T, prob = 0.90))
summary(m_hc_sexfreqpen_linear, intervals = T, prob = 0.90)
```

##### Sensitivity 
```{r}
m_hc_sexfreqpen_linear_sensitivity <- sensemakr(model = m_hc_sexfreqpen_linear,
                                         treatment = "contraception_hormonal_numeric",
                                        kd = 1:3, #these arguments parameterize how many times
                                          #stronger the confounder is related to the
                                          #treatment
                                ky = 1:3, #these arguments parameterize how many times
                                          #stronger the confounder is related to the outcome
                                q = 1, #fraction of the effect estimate that would have to be
                                       #explained away to be problematic. Setting q = 1,
                                       #means that a reduction of 100% of the current effect
                                       #estimate, that is, a true effect of zero, would be
                                       #deemed problematic.
                                alpha = 0.05,
                                reduce = TRUE #confounder reduce absolute effect size
                                )


m_hc_sexfreqpen_linear_sensitivity
summary(m_hc_sexfreqpen_linear_sensitivity)
```

#### Controlled
##### Model
```{r}
m_hc_sexfreqpen_linear = lm(diary_sex_active_sex_mean ~ contraception_hormonal_numeric + age + net_income + relationship_duration_factor + 
     education_years + bfi_extra + bfi_neuro + bfi_agree + bfi_consc + 
     bfi_open + religiosity,
               data = data)
```

##### Summary
```{r}
kable(tidy(m_hc_sexfreqpen_linear, intervals = T, prob = 0.90))
summary(m_hc_sexfreqpen_linear, intervals = T, prob = 0.90)
```

##### Sensitivity 
```{r}
m_hc_sexfreqpen_linear_sensitivity <- sensemakr(model = m_hc_sexfreqpen_linear,
                                         treatment = "contraception_hormonal_numeric",
                                          benchmark_covariates = covariates, #covariates that will be
                                                                   #used to bound the
                                                                   #plausible strength of the
                                                                   #unobserved confounders
                                        kd = 1:3, #these arguments parameterize how many times
                                          #stronger the confounder is related to the
                                          #treatment
                                ky = 1:3, #these arguments parameterize how many times
                                          #stronger the confounder is related to the outcome
                                q = 1, #fraction of the effect estimate that would have to be
                                       #explained away to be problematic. Setting q = 1,
                                       #means that a reduction of 100% of the current effect
                                       #estimate, that is, a true effect of zero, would be
                                       #deemed problematic.
                                alpha = 0.05,
                                reduce = TRUE #confounder reduce absolute effect size
                                )


m_hc_sexfreqpen_linear_sensitivity
summary(m_hc_sexfreqpen_linear_sensitivity)
```
