---
title: "Marginal Effects in Controlled Models"
output:
  html_document:
    toc: true
    toc_depth: 4
    toc_float: true
    code_folding: 'hide'
    self_contained: false
editor_options: 
  chunk_output_type: console
---
  
  
## Data 
```{r results='hide',message=F,warning=F}
source("0_helpers.R")
library(modelr)
library(tidybayes)

load("data/cleaned_selected_wrangled.rdata")
```

## Controlled Models: Effects of Hormonal Contraceptives {.tabset}

### Sexual Frequency (Penetrative Intercourse) {.tabset}
#### Model
```{r}
m_hc_sexfreqpen_controlled = brm(diary_sex_active_sex_sum ~
                        offset(log(number_of_days)) +
                        contraception_hormonal +
                        age + net_income + relationship_duration_factor +
                              education_years +
                              bfi_extra + bfi_neuro + bfi_agree + bfi_consc + bfi_open +
                              religiosity,
                data = data, family = poisson(),
                file = "m_hc_sexfreqpen_controlled")
```

#### Fitted draws
```{r}
data_pred = add_epred_draws(data, m_hc_sexfreqpen_controlled,
                   value = "E[y|A,B]")
```

#### Compare means
```{r}
means_emp = data %>%
  group_by(contraception_hormonal) %>%
  summarise(mean_emp = mean(diary_sex_active_sex_sum, na.rm = T))
means_emp

means = data_pred %>%
  group_by(contraception_hormonal) %>%
  summarise(mean_emp = mean(diary_sex_active_sex_sum, na.rm = T),
            mean_fit = mean(`E[y|A,B]`, na.rm = T))
means
```

#### Plot
```{r}
marginal_effects = data_pred %>%
  group_by(contraception_hormonal, .draw) %>%  # group by predictors to keep
  summarise(`E[y|A]` = mean(`E[y|A,B]`, na.rm = T)) 

mean_diffs = marginal_effects %>%
  compare_levels(`E[y|A]`, by = contraception_hormonal) %>%  # pairwise differences in `E[y|A]`, by levels of A
  rename(`mean difference` = `E[y|A]`) 

mean_diffs %>%
  ggplot(aes(x = `mean difference`, y = contraception_hormonal)) +
  stat_halfeye() +
  geom_vline(xintercept = 0, linetype = "dashed")
```

#### Frequencies?
```{r}
mean_freq = data_pred %>%
  mutate(emp_freq = diary_sex_active_sex_sum/number_of_days,
         pred_freq = `E[y|A,B]`/number_of_days) %>%
  group_by(contraception_hormonal) %>%
  summarise(mean_emp = mean(emp_freq, na.rm = T),
            mean_fit = mean(pred_freq, na.rm = T))
mean_freq
```


### Masturbation Frequency {.tabset}
#### Model
```{r}
m_hc_masfreq_controlled = brm(diary_masturbation_sum ~
                        offset(log(number_of_days)) +
                        contraception_hormonal +
                        age + net_income + relationship_duration_factor +
                              education_years +
                              bfi_extra + bfi_neuro + bfi_agree + bfi_consc + bfi_open +
                              religiosity,
                data = data, family = poisson(),
                file = "m_hc_masfreq_controlled")
```

#### Fitted draws
```{r}
data_pred = add_epred_draws(data, m_hc_masfreq_controlled,
                   value = "E[y|A,B]")
```

#### Compare means
```{r}
means_emp = data %>%
  group_by(contraception_hormonal) %>%
  summarise(mean_emp = mean(diary_masturbation_sum, na.rm = T))
means_emp

means = data_pred %>%
  group_by(contraception_hormonal) %>%
  summarise(mean_emp = mean(diary_masturbation_sum, na.rm = T),
            mean_fit = mean(`E[y|A,B]`, na.rm = T))
means
```

#### Plot
```{r}
marginal_effects = data_pred %>%
  group_by(contraception_hormonal, .draw) %>%  # group by predictors to keep
  summarise(`E[y|A]` = mean(`E[y|A,B]`, na.rm = T)) 

mean_diffs = marginal_effects %>%
  compare_levels(`E[y|A]`, by = contraception_hormonal) %>%  # pairwise differences in `E[y|A]`, by levels of A
  rename(`mean difference` = `E[y|A]`) 

mean_diffs %>%
  ggplot(aes(x = `mean difference`, y = contraception_hormonal)) +
  stat_halfeye() +
  geom_vline(xintercept = 0, linetype = "dashed")
```

#### Frequencies?
```{r}
mean_freq = data_pred %>%
  mutate(emp_freq = diary_masturbation_sum/number_of_days,
         pred_freq = `E[y|A,B]`/number_of_days) %>%
  group_by(contraception_hormonal) %>%
  summarise(mean_emp = mean(emp_freq, na.rm = T),
            mean_fit = mean(pred_freq, na.rm = T))
mean_freq
```


### Very broad continous categories

#### Model
```{r}
m_hc_sexfreqpen_controlled = brm(diary_sex_active_sex_sum ~
                        offset(log(number_of_days)) +
                        contraception_hormonal +
                        age + net_income + relationship_duration_factor +
                              education_years +
                              bfi_extra + bfi_neuro + bfi_agree + bfi_consc + bfi_open +
                              religiosity,
                data = data, family = poisson(),
                file = "m_hc_sexfreqpen_controlled")
```


#### Data grid
```{r}
marginal_effects = data %>%
  data_grid(seq_range(number_of_days, n = 2), #measured in full days
            contraception_hormonal,
            seq_range(age, n = 2), # measured in full years
            net_income,
            relationship_duration_factor,
            seq_range(education_years, n = 2), # measured in full years
            seq_range(bfi_extra, n = 2), 
            seq_range(bfi_neuro, n = 2), 
            seq_range(bfi_agree, n = 2), 
            seq_range(bfi_consc, n = 2), 
            seq_range(bfi_open, n = 2), 
            seq_range(religiosity, n = 2) 
  )

marginal_effects = marginal_effects %>%
  rename(number_of_days = 'seq_range(number_of_days, n = 2)',
         age = "seq_range(age, n = 2)",
         education_years =  "seq_range(education_years, n = 2)",
         bfi_extra = "seq_range(bfi_extra, n = 2)",
         bfi_neuro = "seq_range(bfi_neuro, n = 2)",
         bfi_agree = "seq_range(bfi_agree, n = 2)",
         bfi_consc = "seq_range(bfi_consc, n = 2)",
         bfi_open = "seq_range(bfi_open, n = 2)",
         religiosity = "seq_range(religiosity, n = 2)")
```


#### Add predicted values
```{r}
#memory.limit(9999999999999)
data_pred = add_epred_draws(marginal_effects, m_hc_sexfreqpen_controlled,
                   value = "E[y|A,B]")
```

#### Compare means
```{r}
means_emp = data %>%
  group_by(contraception_hormonal) %>%
  summarise(mean_emp = mean(diary_sex_active_sex_sum, na.rm = T))
means_emp

means = data_pred %>%
  group_by(contraception_hormonal) %>%
  summarise(mean_fit = mean(`E[y|A,B]`, na.rm = T))
means
```

#### Plot
```{r}
marginal_effects = data_pred %>%
  group_by(contraception_hormonal, .draw) %>%  # group by predictors to keep
  summarise(`E[y|A]` = mean(`E[y|A,B]`, na.rm = T)) 

mean_diffs = marginal_effects %>%
  compare_levels(`E[y|A]`, by = contraception_hormonal) %>%  # pairwise differences in `E[y|A]`, by levels of A
  rename(`mean difference` = `E[y|A]`) 

mean_diffs %>%
  ggplot(aes(x = `mean difference`, y = contraception_hormonal)) +
  stat_halfeye() +
  geom_vline(xintercept = 0, linetype = "dashed")
```

#### Frequencies?
```{r}
mean_freq = data_pred %>%
  mutate(#emp_freq = diary_sex_active_sex_sum/number_of_days,
         pred_freq = `E[y|A,B]`/number_of_days) %>%
  group_by(contraception_hormonal) %>%
  summarise(#mean_emp = mean(emp_freq, na.rm = T),
            mean_fit = mean(pred_freq, na.rm = T))
mean_freq
```


------------------------------------------------------------------------------------------
## Old Stuff from here on ###
## Categorical Variables
```{r}
data = data %>%
  mutate(age_cat = factor(age),
         education_years_cat = factor(education_years),
         bfi_extra_cat = factor(round(bfi_extra, 0)),
         bfi_agree_cat = factor(round(bfi_agree, 0)),
         bfi_neuro_cat = factor(round(bfi_neuro, 0)),
         bfi_consc_cat = factor(round(bfi_consc, 0)),
         bfi_open_cat = factor(round(bfi_open, 0)),
         religiosity_cat = factor(religiosity))
```


## Controlled Models: Effects of Hormonal Contraceptives {.tabset}

### Sexual Frequency (Penetrative Intercourse) {.tabset}
#### Model
```{r}
m_hc_sexfreqpen_controlled_cat = brm(diary_sex_active_sex_sum ~
                        offset(log(number_of_days)) +
                        contraception_hormonal +
                        age_cat + net_income + relationship_duration_factor +
                        education_years_cat +
                        bfi_extra_cat + bfi_neuro_cat + bfi_agree_cat +
                        bfi_consc_cat + bfi_open_cat +
                              religiosity_cat,
                data = data, family = poisson(),
                file = "m_hc_sexfreqpen_controlled_cat")

kable(tidy(m_hc_sexfreqpen_controlled_cat, intervals = T, prob = 0.90))
```

#### Average Marginal effects
```{r}


memory.limit(9999999999999) # here i run into problems with the memory limit on my computer... 
marginal_effects = data %>%
  filter(!is.na(diary_sex_active_sex_sum),
         !is.na(number_of_days),
         !is.na(contraception_hormonal),
         !is.na(age_cat),
         !is.na(education_years)) %>%
  data_grid(seq_range(number_of_days, by = 1), #measured in full days
            contraception_hormonal,
            seq_range(age, by = 1), # measured in full years
            net_income,
            relationship_duration_factor,
            seq_range(education_years, by = 1), # measured in full years
            seq_range(bfi_extra, n = 16), #32 unique values length(table(data$bfi_extra))
            #seq_range(bfi_neuro, n = 16), #33 uniqe values length(table(data$bfi_neuro))
            seq_range(bfi_agree, n = 16), #32 unique values length(table(data$bfi_agree))
            seq_range(bfi_consc, n = 16), #32 unique values length(table(data$bfi_consc))
            seq_range(bfi_open, n = 35), #35 unique values length(table(data$bfi_open))
            seq_range(religiosity, n = 6) # 6 unique values length(table(data$religiosity))
  )


marginal_effects_cat = data %>%
  filter(!is.na(diary_sex_active_sex_sum),
         !is.na(number_of_days),
         !is.na(contraception_hormonal),
         !is.na(age_cat),
         !is.na(education_years)) %>%
  data_grid(number_of_days,
            contraception_hormonal,
            age_cat,
            net_income,
            relationship_duration_factor,
            education_years_cat,
            bfi_extra_cat,
            bfi_neuro_cat,
            bfi_agree_cat,
            bfi_consc_cat,
            bfi_open_cat,
            religiosity_cat)
# even with categorical vectors my computer says "kann Vektor der Größe 130.2 GB nicht allozieren"

### Code from here is not tested yet and doesnt work
ames = marginal_effects %>%
  add_fitted_draws(marginal_effects_cat,
                   value = "E[y|A,B]") %>%  # get conditional expectations
  group_by(contraception_hormonal, .draw) %>%                       # group by predictors to keep
  summarise(`E[y|A]` = mean(`E[y|A,B]`)) 

means = ames %>%
  ungroup() %>%
  group_by(contraception_hormonal) %>%
  summarize(mean = mean(ames$`E[y|A]`))

mean_diffs = ames %>%
  ungroup() %>%
  compare_levels(`E[y|A]`, by = contraception_hormonal) %>%         # pairwise differences in `E[y|A]`, by levels of A
  rename(`mean difference` = `E[y|A]`) 

mean_diffs %>%
  ggplot(aes(x = `mean difference`, y = contraception_hormonal)) +
  stat_halfeye() +
  geom_vline(xintercept = 0, linetype = "dashed")
```

### Masturabation Frequency {.tabset}
#### Model
```{r}
m_hc_masfreq_controlled = brm(diary_masturbation_sum ~
                        offset(log(number_of_days)) +
                        contraception_hormonal +
                        age + net_income + relationship_duration_factor +
                              education_years +
                              bfi_extra + bfi_neuro + bfi_agree + bfi_consc + bfi_open +
                              religiosity,
                data = data, family = poisson(),
                file = "m_hc_masfreq_controlled")
```
