---
title: "Codebook Effects of Contraception"
output:
  html_document:
    toc: true
    toc_depth: 4
    toc_float: true
    code_folding: 'hide'
    self_contained: false
---
  
```{r results='hide',message=F,warning=F}
source("0_helpers.R")
knitr::opts_chunk$set(warning = FALSE, message = FALSE)
pander::panderOptions("table.split.table", Inf)
pander::panderOptions('round',2)
pander::panderOptions('digits',2)
pander::panderOptions('keep.trailing.zeros',TRUE)

load("data/cleaned_selected.rdata")

knitr::opts_chunk$set(echo = FALSE, error = TRUE, dev = "CairoPNG")
library(ggplot2)
theme_set(theme_bw())

library(codebook)
```


## Included variables for codebook
```{r}
data = all_surveys %>%
  select(session,
         age,
         education_years,
         net_income,
         starts_with("bfi_agree"),
         starts_with("bfi_consc"),
         starts_with("bfi_open"),
         starts_with("bfi_extra"),
         starts_with("bfi_neuro"),
         religiosity,
         pregnant_stress,
         duration_relationship_years,
         duration_relationship_month,
         days_with_partner,
         nights_with_partner,
         starts_with("soi_r"),
         soi_r_behavior,
         soi_r_desire,
         number_sexual_partner,
         contraception_method,
         contraception_approach,
         contraception_method_broad,
         contraception_meeting_partner,
         partner_attractiveness_face,
         partner_attractiveness_body,
         relationship_satisfaction_overall,
         relationship_satisfaction_2,
         relationship_satisfaction_3,
         relationship_problems_R,
         relationship_conflict_R,
         satisfaction_sexual_intercourse,
         reasons_for_exclusion,
         pregnant_trying)

# based on diary:
data_diary = diary %>%
  select(session,
         high_libido,
         sex_active, sex_activity_anal_sex, sex_activity_bdsm_dom, sex_activity_bdsm_sub,
         sex_activity_cuddling, sex_activity_cunnilingus, sex_activity_cybersex, sex_activity_dirty_talk,
         sex_activity_fellatio, sex_activity_kissing,  sex_activity_masturbated_by_partner,
         sex_activity_masturbated_partner, sex_activity_masturbation, sex_activity_other,
         sex_activity_phone_skype_sex, sex_activity_pornography, sex_activity_sex, sex_activity_touch_other, 
         sex_activity_toys, sex_activity_unclear,  sex_other, sex_solo, sex_unclear,
         days_done)
```


## Exclusion
For now based on old exclusion criteria --> update later
```{r}
n_excluded = data %>% filter(reasons_for_exclusion != "") %>% nrow()
data = data %>% filter(reasons_for_exclusion == "")
```
`r n_excluded` people were excluded.

## Wrangle data
created contraception_approach
```{r}
data = data %>% mutate(
    contraception_method = if_else(is.na(contraception_method), "", as.character(contraception_method)),
    com = contraception_method,
    contraception_approach = if_else(
        condition = com %contains% "hormonal_pill" | com %contains% "hormonal_other", # condition
        # true
        true = if_else(
            condition = com == "hormonal_pill" | com == "hormonal_other" | com == "hormonal_morning_after_pill", # condition
            true = if_else(com == "hormonal_pill", 
                                            true = "hormonal_pill_only", 
                                            false = "hormonal_other_only"
            ),
                                            false = "hormonal+barrier"
            ),
        if_else(
            condition = ! com %contains% "awareness", 
            true = if_else(condition = com != "",
                true = if_else(condition = com %contains% "barrier_intrauterine_pessar", 
                               true = "barrier_pessar",
                                if_else(condition = com %contains% "barrier_condoms", true = "condoms", false = "other")),
                false = "nothing"),
                false = "awareness")
        )
          # false
    )
data$contraception_approach = factor( all_surveys$contraception_approach, levels = c("condoms", "barrier_pessar", "hormonal+barrier", "hormonal_pill_only", "hormonal_other_only", "awareness", "nothing", "other") )
qplot(data$contraception_approach) + coord_flip()
```

create current contraceptive status (hormonal vs. non hormonal)
```{r}
data = data %>% mutate(
  contraception_hormonal = factor(ifelse(contraception_approach %contains% "hormonal", "yes", "no")))
qplot(data$contraception_hormonal) + coord_flip()
```

create variable to indicate whether people changed contraception since meeting their partner
```{r}
crosstabs(~contraception_hormonal + contraception_meeting_partner, data = data)
data = data %>% mutate(
  contraception_change_since_meeting_partner = ifelse(
    contraception_hormonal == "yes" & contraception_meeting_partner == 1, "congruent_hormonal",
    ifelse(
      contraception_hormonal == "no" & contraception_meeting_partner == 0, "congruent_nonhormonal",
      ifelse(
        contraception_hormonal == "yes" & contraception_meeting_partner == 0, "switched_to_hormonal",
        ifelse(
          contraception_hormonal == "no" & contraception_meeting_partner == 1, "switched_to_nonhormonal",
          NA)))))
qplot(data$contraception_change_since_meeting_partner) + coord_flip()
```

calculate mean of libido, sex_active_frequency and actual sex frequency based on diary
```{r}
data_diary_means = data_diary %>%
  mutate(days_done = as.numeric(days_done)) %>%
  #restrict analyses to people who filled out more than 30 days
  filter(days_done > 30) %>% 
  group_by(session) %>%
  summarise(diary_libido_mean = mean(high_libido, na.rm = T),
            diary_sex_active_mean = mean(sex_active, na.rm = T),
            diary_sex_active_sex_mean = mean(sex_activity_sex, na.rm = T))

qplot(data_diary_means$diary_libido_mean)
qplot(data_diary_means$diary_sex_active_mean)
qplot(data_diary_means$diary_sex_active_sex_mean)

data = left_join(data, data_diary_means, by = "session")
```

relationship status (single vs partnered)
```{r}
data = data %>% mutate(
  relationship_status = ifelse(is.na(duration_relationship_month), "Single", "Partnered")
)

qplot(data$relationship_status)
```

## Restricted codebook to 100 people
```{r}
data = data %>% filter(row_number() < 101)
```

## Selection Variables Codebook
```{r}
codebook_selection_data = data %>%
  select(-session,
         -starts_with("contraception_"),
         -starts_with("partner_"), -starts_with("relationship_satisfaction"),
         -relationship_problems_R, -relationship_conflict_R, -satisfaction_sexual_intercourse,
         -reasons_for_exclusion, -pregnant_trying)

codebook(codebook_selection_data,  missingness_report = FALSE, indent = "##")
```

## Contraception Codebook
```{r}
codebook_contraception_data = data %>%
  select(contraception_hormonal, contraception_meeting_partner, contraception_change_since_meeting_partner)

codebook(codebook_contraception_data,  missingness_report = FALSE, indent = "##")
```

## Outcomes Codebook 
```{r}
codebook_outcome_data = data %>%
  select(partner_attractiveness_face,
         partner_attractiveness_body,
         relationship_satisfaction_overall,
         relationship_satisfaction_2,
         relationship_satisfaction_3,
         relationship_problems_R,
         relationship_conflict_R,
         satisfaction_sexual_intercourse,
         diary_libido_mean,
         diary_sex_active_mean,
         diary_sex_active_sex_mean)
codebook(codebook_outcome_data,  missingness_report = FALSE, indent = "##")
```


## Differences in contraception status by relationship status
```{r}
ggplot(data, aes(x = relationship_status, fill = contraception_hormonal)) + geom_bar(position = "dodge")
```

## Differences in Gaussian variables by HC and RS {.tabset}
### Hormonal contraception
```{r}
ggplot(data, aes(x = contraception_hormonal, y = partner_attractiveness_face)) + geom_jitter() + stat_summary(fun.y = mean, geom = "point", color = "red") + 
    stat_summary(fun.data = mean_cl_normal, geom = "errorbar", color = "red")

ggplot(data, aes(x = contraception_hormonal, y = partner_attractiveness_body)) + geom_jitter() + stat_summary(fun.y = mean, geom = "point", color = "red") + 
    stat_summary(fun.data = mean_cl_normal, geom = "errorbar", color = "red")

ggplot(data, aes(x = contraception_hormonal, y = relationship_satisfaction_overall)) + geom_jitter() + stat_summary(fun.y = mean, geom = "point", color = "red") + 
    stat_summary(fun.data = mean_cl_normal, geom = "errorbar", color = "red")

ggplot(data, aes(x = contraception_hormonal, y = relationship_satisfaction_2)) + geom_jitter() + stat_summary(fun.y = mean, geom = "point", color = "red") + 
    stat_summary(fun.data = mean_cl_normal, geom = "errorbar", color = "red")

ggplot(data, aes(x = contraception_hormonal, y = relationship_satisfaction_3)) + geom_jitter() + stat_summary(fun.y = mean, geom = "point", color = "red") + 
    stat_summary(fun.data = mean_cl_normal, geom = "errorbar", color = "red")

ggplot(data, aes(x = contraception_hormonal, y = relationship_problems_R)) + geom_jitter() + stat_summary(fun.y = mean, geom = "point", color = "red") + 
    stat_summary(fun.data = mean_cl_normal, geom = "errorbar", color = "red")

ggplot(data, aes(x = contraception_hormonal, y = relationship_conflict_R)) + geom_jitter() + stat_summary(fun.y = mean, geom = "point", color = "red") + 
    stat_summary(fun.data = mean_cl_normal, geom = "errorbar", color = "red")

ggplot(data, aes(x = contraception_hormonal, y = satisfaction_sexual_intercourse)) + geom_jitter() + stat_summary(fun.y = mean, geom = "point", color = "red") + 
    stat_summary(fun.data = mean_cl_normal, geom = "errorbar", color = "red")

ggplot(data, aes(x = contraception_hormonal, y = diary_libido_mean)) + geom_jitter() + stat_summary(fun.y = mean, geom = "point", color = "red") + 
    stat_summary(fun.data = mean_cl_normal, geom = "errorbar", color = "red")

ggplot(data, aes(x = contraception_hormonal, y = diary_sex_active_mean)) + geom_jitter() + stat_summary(fun.y = mean, geom = "point", color = "red") + 
    stat_summary(fun.data = mean_cl_normal, geom = "errorbar", color = "red")

ggplot(data, aes(x = contraception_hormonal, y = diary_sex_active_sex_mean)) + geom_jitter() + stat_summary(fun.y = mean, geom = "point", color = "red") + 
    stat_summary(fun.data = mean_cl_normal, geom = "errorbar", color = "red")
```

### Relationship status
```{r}
ggplot(data, aes(x = relationship_status, y = diary_libido_mean)) + geom_jitter() + stat_summary(fun.y = mean, geom = "point", color = "red") + 
    stat_summary(fun.data = mean_cl_normal, geom = "errorbar", color = "red")

ggplot(data, aes(x = relationship_status, y = diary_sex_active_mean)) + geom_jitter() + stat_summary(fun.y = mean, geom = "point", color = "red") + 
    stat_summary(fun.data = mean_cl_normal, geom = "errorbar", color = "red")

ggplot(data, aes(x = relationship_status, y = diary_sex_active_sex_mean)) + geom_jitter() + stat_summary(fun.y = mean, geom = "point", color = "red") + 
    stat_summary(fun.data = mean_cl_normal, geom = "errorbar", color = "red")
```


## Correlations {.tabset}
### Selection
```{r}
lapply(selection_variables,class)

selection_variables = codebook_selection_data %>% select(
  -starts_with("bfi_agree_"), -starts_with("bfi_consc_"), -starts_with("bfi_open_"),
  -starts_with("bfi_extra_"), -starts_with("bfi_neuro_"), -relationship_status, -net_income)


cor(selection_variables, use="complete.obs")
```

### Outcomes
```{r}
cor(codebook_outcome_data, use="complete.obs")
```

