
# Datawrangling {.tabset}

## Data and Functions
```{r data and function, results='hide',message=F,warning=F}
source("0_helpers.R")
knitr::opts_chunk$set(warning = FALSE, message = FALSE)
pander::panderOptions("table.split.table", Inf)
pander::panderOptions('round',2)
pander::panderOptions('digits',2)
pander::panderOptions('keep.trailing.zeros',TRUE)

load("data/cleaned_selected.rdata")
```


## Select Variables {.tabset}
### Initial Survey
```{r select variables}
data = all_surveys %>%
  select(session,
         age,
         education_years,
         net_income,
         starts_with("bfi_agree"),
         starts_with("bfi_consc"),
         starts_with("bfi_open"),
         starts_with("bfi_extra"),
         starts_with("bfi_neuro"),
         religiosity,
         pregnant_stress,
         duration_relationship_years,
         duration_relationship_month,
         days_with_partner,
         nights_with_partner,
         starts_with("soi_r"),
         soi_r_behavior,
         soi_r_desire,
         number_sexual_partner,
         contraception_method,
         contraception_approach,
         contraception_method_broad,
         contraception_meeting_partner,
         partner_attractiveness_face,
         partner_attractiveness_body,
         relationship_satisfaction_overall,
         relationship_satisfaction_2,
         relationship_satisfaction_3,
         relationship_problems_R,
         relationship_conflict_R,
         satisfaction_sexual_intercourse,
         reasons_for_exclusion,
         pregnant_trying)
```

### Diary
```{r select variables diary}
data_diary = diary %>%
  select(session,
         reasons_for_exclusion,
         high_libido,
         sex_active, sex_activity_anal_sex, sex_activity_bdsm_dom, sex_activity_bdsm_sub,
         sex_activity_cuddling, sex_activity_cunnilingus, sex_activity_cybersex,
         sex_activity_dirty_talk,
         sex_activity_fellatio, sex_activity_kissing,  sex_activity_masturbated_by_partner,
         sex_activity_masturbated_partner, sex_activity_masturbation, sex_activity_other,
         sex_activity_phone_skype_sex, sex_activity_pornography, sex_activity_sex, 
         sex_activity_touch_other, 
         sex_activity_toys, sex_activity_unclear,  sex_other, sex_solo, sex_unclear,
         days_done)
```


## Exclusion {.tabset}
### Initial Survey
```{r exclusion initial survey}
n_excluded = data %>% filter(reasons_for_exclusion != "") %>% nrow()
data = data %>% filter(reasons_for_exclusion == "")
```
`r n_excluded` people were excluded.

### Diary  {.tabset}
#### Exclusion criteria based on initial
```{r}
session_codes = data$session

data_diary = data_diary %>%
  filter(session %in% session_codes)

length(data_diary$session)
```
The `r length(unique(data_diary$session))` participants filled out `r length(data_diary$session)`.

#### Skipped diary entry
```{r}
n_skipped_diary = data_diary %>%
  filter(reasons_for_exclusion %contains% "skipped_diary_entry") %>%
  count()

data_diary = data_diary %>%
  filter(!(reasons_for_exclusion %contains% "skipped_diary_entry"))
```
`r n_skipped_diary` days were skipped.

#### Dishonest answers
```{r}
n_dishonest = data_diary %>%
  filter(reasons_for_exclusion %contains% "dishonest") %>%
  count()

data_diary = data_diary %>%
  filter(!(reasons_for_exclusion %contains% "dishonest"))
```
`r n_dishonest` days contained dishonest answers.

#### Filled out less than 30 days
```{r}
number_of_days = data_diary %>%
  group_by(session) %>%
  summarise(n = n()) %>%
  rename(number_of_days = n)
  
data_diary = left_join(data_diary, number_of_days, by = "session")

data_diary_include = data_diary %>%
  filter(as.numeric(number_of_days) > 30)

data_diary_exclude = data_diary %>%
  filter(as.numeric(number_of_days) <= 30)

data_diary = data_diary_include
```
`r length(unique(data_diary_exclude$session))` participants were excluded because they filled out less than 30 days - resulting in `r length(data_diary_exclude$session)` excluded days.

#### Summary {.active}
In total `r length(unique(data_diary$session))` participants with `r length(data_diary$session)` diary days were included for the analyses in which outcomes were based on diary information. 

## Wrangle data {.tabset}
### Contraception approach
```{r contraception approach}
data = data %>% mutate(
    contraception_method = if_else(is.na(contraception_method), "",
                                   as.character(contraception_method)),
    com = contraception_method,
    contraception_approach = if_else(
        condition = com %contains% "hormonal_pill" | com %contains% "hormonal_other",
        true = if_else(
            condition = com == "hormonal_pill" | com == "hormonal_other" |
              com == "hormonal_morning_after_pill",
            true = if_else(com == "hormonal_pill", 
                           true = "hormonal_pill_only",
                           false = "hormonal_other_only"),
            false = "hormonal+barrier"),
        if_else(
            condition = ! com %contains% "awareness", 
            true = if_else(condition = com != "",
                           true = if_else(condition = com %contains% "barrier_intrauterine_pessar",
                                          true = "barrier_pessar",
                                          if_else(condition = com %contains% "barrier_condoms",
                                                  true = "condoms",
                                                  false = "other")),
                           false = "nothing"),
            false = "awareness")))



data$contraception_approach = factor(data$contraception_approach,
                                            levels = c("condoms", "barrier_pessar",
                                                       "hormonal+barrier",
                                                       "hormonal_pill_only", "hormonal_other_only",
                                                       "awareness", "nothing", "other"))

qplot(data$contraception_approach) + coord_flip()
table(data$contraception_approach)
```

### Current contraceptive status (hormonal vs. non hormonal)
```{r}
data = data %>% mutate(
  contraception_hormonal = factor(ifelse(contraception_approach %contains% "hormonal",
                                         "yes",
                                         "no")))
qplot(data$contraception_hormonal) + coord_flip()
```

### Changed contraception since meeting their partner
There will be NAs because we asked about contracetion when meeting partner only if participants were currently in a relationship
```{r}
crosstabs(~contraception_hormonal + contraception_meeting_partner, data = data)
data = data %>% mutate(
  contraception_change_since_meeting_partner =
    ifelse(contraception_hormonal == "yes" & contraception_meeting_partner == 1,
           "congruent_hormonal",
           ifelse(contraception_hormonal == "no" & contraception_meeting_partner == 0,
                  "congruent_nonhormonal",
                  ifelse(contraception_hormonal == "yes" & contraception_meeting_partner == 0,
                         "switched_to_hormonal",
                         ifelse(contraception_hormonal == "no" &
                                  contraception_meeting_partner == 1, "switched_to_nonhormonal",
                                NA)))))

qplot(data$contraception_change_since_meeting_partner) + coord_flip()
```

### Relationship status (single vs partnered)
```{r}
data = data %>% mutate(
  relationship_status = ifelse(is.na(duration_relationship_month), "Single", "Partnered"))

qplot(data$relationship_status) + coord_flip()
```

### Diary information
calculate mean of libido, sex_active_frequency and actual sex frequency based on diary
```{r}
data_diary_means = data_diary %>%
  group_by(session) %>%
  summarise(diary_libido_mean = mean(high_libido, na.rm = T),
            diary_sex_active_mean = mean(sex_active, na.rm = T),
            diary_sex_active_sex_mean = mean(sex_activity_sex, na.rm = T))

qplot(data_diary_means$diary_libido_mean)
qplot(data_diary_means$diary_sex_active_mean)
qplot(data_diary_means$diary_sex_active_sex_mean)

data = left_join(data, data_diary_means, by = "session")
```


## Save Data
```{r}
save(data, data, file = "data/cleaned_selected_wrangled.rdata")
```

