---
title: "data_excludedwrangling for excluded people"
output:
  html_document:
    toc: true
    toc_depth: 4
    toc_float: true
    code_folding: 'show'
    self_contained: false
---


## data_excluded and Functions
```{r data_excluded and function, results='hide',message=F,warning=F}
source("0_helpers.R")
knitr::opts_chunk$set(warning = FALSE, message = FALSE)
pander::panderOptions("table.split.table", Inf)
pander::panderOptions('round',2)
pander::panderOptions('digits',2)
pander::panderOptions('keep.trailing.zeros',TRUE)

load("data_excluded/cleaned_selected.rdata_excluded")
```


## Select Variables {.tabset}
### Initial Survey
```{r select variables}
data_excluded = all_surveys %>%
  select(session,
         age,
         education_years,
         net_income,
         starts_with("bfi_agree"),
         starts_with("bfi_consc"),
         starts_with("bfi_open"),
         starts_with("bfi_extra"),
         starts_with("bfi_neuro"),
         religiosity,
         duration_relationship_years,
         duration_relationship_month,
         contraception_at_all,
         contraception_method,
         contraception_approach,
         contraception_method_broad,
         contraception_meeting_partner,
         partner_attractiveness_face,
         partner_attractiveness_body,
         relationship_satisfaction_overall,
         relationship_satisfaction_2,
         relationship_satisfaction_3,
         relationship_problems_R,
         relationship_conflict_R,
         satisfaction_sexual_intercourse,
         reasons_for_exclusion)
```

### Diary
```{r select variables diary}
data_excluded_diary = diary %>%
  select(session,
         reasons_for_exclusion,
         high_libido, sexual_desire_for_whom,
         sex_active, sex_activity_anal_sex, sex_activity_bdsm_dom, sex_activity_bdsm_sub,
         sex_activity_cuddling, sex_activity_cunnilingus, sex_activity_cybersex,
         sex_activity_dirty_talk,
         sex_activity_fellatio, sex_activity_kissing,  sex_activity_masturbated_by_partner,
         sex_activity_masturbated_partner, sex_activity_masturbation, sex_activity_other,
         sex_activity_phone_skype_sex, sex_activity_pornography, sex_activity_sex, 
         sex_activity_touch_other, 
         sex_activity_toys, sex_activity_unclear,  sex_other, sex_solo, sex_unclear,
         days_done)
```


## Exclusion {.tabset}
### Initial Survey
```{r exclusion initial survey}
n_excluded = data_excluded %>% filter(reasons_for_exclusion != "") %>% nrow()
data_excluded = data_excluded %>% filter(reasons_for_exclusion != "" & !(reasons_for_exclusion %contains% "didnt_finish_initial"))
```
`r n_excluded` people were excluded.

### Diary  {.tabset}

```{r}
number_of_days = data_excluded_diary %>%
  group_by(session) %>%
  summarise(n = n()) %>%
  rename(number_of_days = n)
  
data_excluded_diary = left_join(data_excluded_diary, number_of_days, by = "session")

data_excluded_diary = data_excluded_diary %>%
  filter(reasons_for_exclusion != "" & !(reasons_for_exclusion %contains% "didnt_finish_initial"))
```


## Wrangle data_excluded {.tabset}

### Income
Set factor level correctly
```{r}
data_excluded = data_excluded %>%
  mutate(net_income = factor(net_income,
                             levels = c("euro_lt_500", "euro_500_1000",
                                        "euro_1000_2000", "euro_2000_3000",
                                        "euro_gt_3000", "dont_tell")))
```


### Relationship status (single vs partnered)
```{r}
data_excluded = data_excluded %>% mutate(
  relationship_status = ifelse(is.na(duration_relationship_month), "Single", "Partnered"))

qplot(data_excluded$relationship_status) + coord_flip()
```

### Relationship duration
```{r}
data_excluded = data_excluded %>%
  mutate(relationship_duration = duration_relationship_years * 12 +
           duration_relationship_month)

qplot(data_excluded$relationship_duration)


data_excluded = data_excluded %>%
   mutate(relationship_duration_factor = 
            factor(ifelse(relationship_status == "Single",
                   "Single",
                   ifelse(relationship_duration <= 12,
                          "Partnered_upto12months",
                          ifelse(relationship_duration <= 28, 
                                 "Partnered_upto28months",
                                 ifelse(relationship_duration <= 52,
                                        "Partnered_upto52months",
                                        ifelse(relationship_duration > 52,
                                        "Partnered_morethan52months",
                                        NA))))),
                   levels = c("Single", "Partnered_upto12months",
                              "Partnered_upto28months", "Partnered_upto52months",
                              "Partnered_morethan52months")))

qplot(data_excluded$relationship_duration_factor)

ggplot(data_excluded, aes(relationship_duration)) +
  geom_histogram(aes(fill = relationship_duration_factor), bins = 100)
```



### Contraception approach
```{r contraception approach}
data_excluded = data_excluded %>%
  mutate(# Participants, who indicated having no penetrative sex:
         contraception_method = if_else(contraception_at_all == 5,
                                   "barrier_no_penetrative_sex",
                                   contraception_method),
         # Participants, who indicated having no penetrative sex
         # use no contraceptives
         contraception_approach = factor(ifelse(
           contraception_method =="barrier_no_penetrative_sex",
           "nothing",
           as.character(contraception_approach))),
         # Fixed contraception_approach for
         # "hormonal_pill, barrier_coitus_interruptus"
         contraception_approach = factor(ifelse(
           contraception_method == "hormonal_pill, barrier_coitus_interruptus",
           "hormonal_pill_only",
           as.character(contraception_approach))),
         # Fixed contraception_approach for
         # "hormonal_pill, barrier_no_penetrative_sex"
         contraception_approach = factor(ifelse(
           contraception_method == "hormonal_pill, barrier_no_penetrative_sex",
           "hormonal_pill_only",
           as.character(contraception_approach))),
         # Fixed contraception_approach for
         # "hormonal_other, barrier_condoms"
         contraception_approach = factor(ifelse(
           contraception_method == "hormonal_other, barrier_condoms",
           "hormonal_other+condoms",
           as.character(contraception_approach))),
         # Fixed contraception_approach for
         # "hormonal_other, barrier_condoms, barrier_coitus_interruptus"
         contraception_approach = factor(ifelse(
           contraception_method ==
             "hormonal_other, barrier_condoms, barrier_coitus_interruptus",
           "hormonal_other+condoms",
           as.character(contraception_approach))),
         contraception_approach = factor(ifelse(
           contraception_approach == "hormonal+barrier",
           "hormonal_pill+condoms",
           as.character(contraception_approach))),
         contraception_approach = factor(ifelse(
           contraception_method %contains% "awareness" &
             contraception_method %contains% "condoms" &
             !(contraception_method %contains% "hormonal"),
           "awareness+condoms",
           as.character(contraception_approach))))


data_excluded = data_excluded %>%
  mutate(contraception_approach = factor(contraception_approach,
                                         levels = c("hormonal_pill_only",
                                                    "hormonal_other_only",
                                                    "hormonal_pill+condoms",
                                                    "hormonal_other+condoms",
                                                    "barrier_pessar",
                                                    "awareness",
                                                    "awareness+condoms",
                                                    "condoms",
                                                    "other",
                                                    "nothing")))

qplot(factor(data_excluded$contraception_approach, levels = rev(levels(data_excluded$contraception_approach)))) +
  coord_flip()
table(data_excluded$contraception_approach)
```

### Current contraceptive status (hormonal vs. non hormonal)
```{r}
data_excluded = data_excluded %>% mutate(
  contraception_hormonal = factor(ifelse(contraception_approach %contains% "hormonal",
                                         "yes",
                                         "no")))
qplot(data_excluded$contraception_hormonal) + coord_flip()
table(data_excluded$contraception_hormonal)
```


### Changed contraception since meeting their partner
There will be NAs because we asked about contracetion when meeting partner only if participants were currently in a relationship
```{r}
crosstabs(~contraception_hormonal + contraception_meeting_partner, data_excluded = data_excluded)
data_excluded = data_excluded %>% mutate(
  contraception_change_since_meeting_partner =
    ifelse(contraception_hormonal == "yes" & contraception_meeting_partner == 1,
           "congruent_hormonal",
           ifelse(contraception_hormonal == "no" & contraception_meeting_partner == 0,
                  "congruent_nonhormonal",
                  ifelse(contraception_hormonal == "yes" & contraception_meeting_partner == 0,
                         "switched_to_hormonal",
                         ifelse(contraception_hormonal == "no" &
                                  contraception_meeting_partner == 1, "switched_to_nonhormonal",
                                NA)))))

qplot(data_excluded$contraception_change_since_meeting_partner) + coord_flip()

data_excluded = data_excluded %>% 
  mutate(congruent_contraception = 
           factor(ifelse(contraception_change_since_meeting_partner %contains% "congruent",
                  1, 0)))
```

### Contraception meeting partner
```{r}
data_excluded = data_excluded %>%
  mutate(contraception_meeting_partner = factor(if_else(
    contraception_meeting_partner == 1,
    "yes", "no")))
```

### Attractiveness Partner Scale
```{r}
data_excluded = data_excluded %>%
  mutate(attractiveness_partner = as.numeric(
    (partner_attractiveness_face + partner_attractiveness_body)/2))
```

### Relationship Satisfaction Scale
```{r}
data_excluded = data_excluded %>%
  mutate(relationship_satisfaction = as.numeric(
           (relationship_satisfaction_overall +
              relationship_satisfaction_2 +
              relationship_satisfaction_3 +
              (6 - relationship_problems_R) +
              (6 - relationship_conflict_R))/5))
```

### Diary information
Distinguish between solitary libido and dyadic libido in singles (was not measured for partnered women...).
```{r}
crosstabs(~ high_libido + sexual_desire_for_whom, data_excluded = data_excluded_diary)
# 1 = niemand bestimmtes
# 2 = mit mir selbst
# 3 = Bekannter/Freund
# 4 = Bekannte/Freundin
# 5 = Fremder
# 6 = Fremde

data_excluded_diary = data_excluded_diary %>%
  mutate(high_libido_dyadic = ifelse(sexual_desire_for_whom >= 3, high_libido, NA),
         high_libido_solitary = ifelse(sexual_desire_for_whom == 2, high_libido, NA))
```


calculate mean of libido, sex_active_frequency and actual sex frequency based on diary
```{r}
data_excluded_diary_means = data_excluded_diary %>%
  group_by(session, number_of_days) %>%
  summarise(diary_libido_mean = mean(high_libido, na.rm = T),
            diary_libido_solitary_mean = mean(high_libido_solitary, na.rm = T),
            diary_libido_dyadic_mean = mean(high_libido_dyadic, na.rm = T),
            diary_sex_active_mean = mean(sex_active, na.rm = T),
            diary_sex_active_sex_mean = mean(sex_activity_sex, na.rm = T),
            diary_masturbation_mean = mean(sex_activity_masturbation, na.rm = T))

qplot(data_excluded_diary_means$diary_libido_mean)
qplot(data_excluded_diary_means$diary_libido_solitary_mean)
qplot(data_excluded_diary_means$diary_libido_dyadic_mean)
qplot(data_excluded_diary_means$diary_sex_active_mean)
qplot(data_excluded_diary_means$diary_sex_active_sex_mean)

data_excluded_diary_means = data_excluded_diary_means %>%
  mutate(diary_sex_active_sex_sum = as.integer(round(diary_sex_active_sex_mean*number_of_days, 1)),
         diary_sex_active_sum = as.integer(round(diary_sex_active_mean*number_of_days, 1)),
         diary_masturbation_sum = as.integer(round(diary_masturbation_mean*number_of_days, 1)))

data_excluded = left_join(data_excluded, data_excluded_diary_means, by = "session")

```

### Set sex_freq and mas_freq as missing, if participants indicated having no penetrative sexual intercourse and using no other form of contraception
```{r}
data_excluded = data_excluded %>%
  mutate(diary_sex_active_sex_mean =
           ifelse(contraception_method == "barrier_no_penetrative_sex",
                  NA,
                  diary_sex_active_sex_mean),
         diary_sex_active_sex_sum =
           ifelse(contraception_method == "barrier_no_penetrative_sex",
                  NA,
                  diary_sex_active_sex_sum),
         diary_sex_active_mean =
           ifelse(contraception_method == "barrier_no_penetrative_sex",
                  NA,
                  diary_sex_active_mean),
         diary_sex_active_sum =
           ifelse(contraception_method == "barrier_no_penetrative_sex",
                  NA,
                  diary_sex_active_sum),
         diary_masturbation_mean =
           ifelse(contraception_method == "barrier_no_penetrative_sex",
                  NA,
                  diary_masturbation_mean),
         diary_masturbation_sum =
           ifelse(contraception_method == "barrier_no_penetrative_sex",
                  NA,
                  diary_masturbation_sum))
```

## Select data_excluded
```{r}
data_excluded = data_excluded %>%
  select(-duration_relationship_years, -duration_relationship_month,
         -contraception_at_all, -contraception_approach, -contraception_method_broad)
```

## Descriptives for diary
```{r}
data_excluded = data_excluded %>% filter(number_of_days >= 14)
table(is.na(data_excluded$diary_libido_mean))

mean(data_excluded$diary_libido_mean)

mean(data_excluded$diary_sex_active_sex_sum, na.rm = T)
sd(data_excluded$diary_sex_active_sex_sum, na.rm = T)

mean(data_excluded$diary_masturbation_sum, na.rm = T)
sd(data_excluded$diary_masturbation_sum, na.rm = T)

t.test(data$diary_sex_active_sex_sum, data_excluded$diary_sex_active_sex_sum)
cohen.d.ci(0.06,n=1045,n2=148,n1=897,alpha=.05)

```

