
# Datawrangling {.tabset}

## Data and Functions
```{r data and function, results='hide',message=F,warning=F}
source("0_helpers.R")
knitr::opts_chunk$set(warning = FALSE, message = FALSE)
pander::panderOptions("table.split.table", Inf)
pander::panderOptions('round',2)
pander::panderOptions('digits',2)
pander::panderOptions('keep.trailing.zeros',TRUE)

load("data/cleaned_selected.rdata")
```


## Select Variables {.tabset}
### Initial Survey
```{r select variables}
data = all_surveys %>%
  select(session,
         age,
         education_years,
         net_income,
         starts_with("bfi_agree"),
         starts_with("bfi_consc"),
         starts_with("bfi_open"),
         starts_with("bfi_extra"),
         starts_with("bfi_neuro"),
         religiosity,
         pregnant_stress,
         duration_relationship_years,
         duration_relationship_month,
         days_with_partner,
         nights_with_partner,
         starts_with("soi_r"),
         soi_r_behavior,
         soi_r_desire,
         number_sexual_partner,
         contraception_at_all,
         contraception_method,
         contraception_approach,
         contraception_method_broad,
         contraception_meeting_partner,
         partner_attractiveness_face,
         partner_attractiveness_body,
         relationship_satisfaction_overall,
         relationship_satisfaction_2,
         relationship_satisfaction_3,
         relationship_problems_R,
         relationship_conflict_R,
         satisfaction_sexual_intercourse,
         reasons_for_exclusion,
         pregnant_trying)
```

### Diary
```{r select variables diary}
data_diary = diary %>%
  select(session,
         reasons_for_exclusion,
         high_libido,
         sex_active, sex_activity_anal_sex, sex_activity_bdsm_dom, sex_activity_bdsm_sub,
         sex_activity_cuddling, sex_activity_cunnilingus, sex_activity_cybersex,
         sex_activity_dirty_talk,
         sex_activity_fellatio, sex_activity_kissing,  sex_activity_masturbated_by_partner,
         sex_activity_masturbated_partner, sex_activity_masturbation, sex_activity_other,
         sex_activity_phone_skype_sex, sex_activity_pornography, sex_activity_sex, 
         sex_activity_touch_other, 
         sex_activity_toys, sex_activity_unclear,  sex_other, sex_solo, sex_unclear,
         days_done)
```


## Exclusion {.tabset}
### Initial Survey
```{r exclusion initial survey}
n_excluded = data %>% filter(reasons_for_exclusion != "") %>% nrow()
data = data %>% filter(reasons_for_exclusion == "")
```
`r n_excluded` people were excluded.

### Diary  {.tabset}
#### Exclusion criteria based on initial
```{r}
session_codes = data$session

data_diary = data_diary %>%
  filter(session %in% session_codes)

length(data_diary$session)
```
The `r length(unique(data_diary$session))` participants filled out `r length(data_diary$session)`.

#### Skipped diary entry
```{r}
n_skipped_diary = data_diary %>%
  filter(reasons_for_exclusion %contains% "skipped_diary_entry") %>%
  count()

data_diary = data_diary %>%
  filter(!(reasons_for_exclusion %contains% "skipped_diary_entry"))
```
`r n_skipped_diary` days were skipped.

#### Dishonest answers
```{r}
n_dishonest = data_diary %>%
  filter(reasons_for_exclusion %contains% "dishonest") %>%
  count()

data_diary = data_diary %>%
  filter(!(reasons_for_exclusion %contains% "dishonest"))
```
`r n_dishonest` days contained dishonest answers.

#### Filled out less than 14 days
```{r}
number_of_days = data_diary %>%
  group_by(session) %>%
  summarise(n = n()) %>%
  rename(number_of_days = n)
  
data_diary = left_join(data_diary, number_of_days, by = "session")

data_diary_include = data_diary %>%
  filter(as.numeric(number_of_days) >= 14)

data_diary_exclude = data_diary %>%
  filter(as.numeric(number_of_days) < 14)

data_diary = data_diary_include
```
`r length(unique(data_diary_exclude$session))` participants were excluded because they filled out less than 14 days - resulting in `r length(data_diary_exclude$session)` excluded days.

#### Summary {.active}
In total `r length(unique(data_diary$session))` participants with `r length(data_diary$session)` diary days were included for the analyses in which outcomes were based on diary information. 

## Wrangle data {.tabset}

### Income
Set factor level correctly
```{r}
data = data %>%
  mutate(net_income = factor(net_income,
                             levels = c("euro_lt_500", "euro_500_1000",
                                        "euro_1000_2000", "euro_2000_3000",
                                        "euro_gt_3000", "dont_tell")))
```

### Relationship status (single vs partnered)
```{r}
data = data %>% mutate(
  relationship_status = ifelse(is.na(duration_relationship_month), "Single", "Partnered"))

qplot(data$relationship_status) + coord_flip()
```

### Relationship duration
```{r}
data = data %>%
  mutate(relationship_duration = duration_relationship_years * 12 +
           duration_relationship_month)

qplot(data$relationship_duration)


data = data %>%
   mutate(relationship_duration_factor = 
            factor(ifelse(relationship_status == "Single",
                   "Single",
                   ifelse(relationship_duration <= 12,
                          "Partnered_upto12months",
                          ifelse(relationship_duration <= 28, 
                                 "Partnered_upto28months",
                                 ifelse(relationship_duration <= 52,
                                        "Partnered_upto52months",
                                        ifelse(relationship_duration > 52,
                                        "Partnered_morethan52months",
                                        NA))))),
                   levels = c("Single", "Partnered_upto12months",
                              "Partnered_upto28months", "Partnered_upto52months",
                              "Partnered_morethan52months")))

qplot(data$relationship_duration_factor)

ggplot(data, aes(relationship_duration)) +
  geom_histogram(aes(fill = relationship_duration_factor), bins = 100)

quantiles = quantile(as.numeric(data$relationship_duration),
                     na.rm = T,
                     probs = c(0, 0.125, 0.25, 0.375, 0.5,0.625, 0.75, 0.875, 1))

data = data %>%
  mutate(relationship_duration_factor2 = 
           factor(ifelse(relationship_status == "Single",
                  "Single",
                  ifelse(relationship_duration <= quantiles[2],
                         "Partnered_upto6months",
                         ifelse(relationship_duration <= quantiles[3],
                                "Partnered_upto12months",
                                ifelse(relationship_duration <= quantiles[4],
                                       "Partnered_upto20months",
                                       ifelse(relationship_duration <= quantiles[5],
                                              "Partnered_upto28months",
           ifelse(relationship_duration <= quantiles[6],
                  "Partnered_upto38months",
                  ifelse(relationship_duration <= quantiles[7],
                         "Partnered_upto52months",
                         ifelse(relationship_duration <= quantiles[8],
                                "Partnered_upto85months",
                                ifelse(relationship_duration > quantiles[8],
                                       "Partnered_morethan85months",
                                       NA))))))))),
           levels = c("Single", "Partnered_upto6months", "Partnered_upto12months",
                      "Partnered_upto20months", "Partnered_upto28months",
                      "Partnered_upto38months", "Partnered_upto52months",
                      "Partnered_upto85months", "Partnered_morethan85months")))
```


### Contraception approach
```{r contraception approach}
data = data %>%
  mutate(# Participants, who indicated having no penetrative sex:
         contraception_method = if_else(contraception_at_all == 5,
                                   "barrier_no_penetrative_sex",
                                   contraception_method),
         # Participants, who indicated having no penetrative sex
         # use no contraceptives
         contraception_approach = factor(ifelse(
           contraception_method =="barrier_no_penetrative_sex",
           "nothing",
           as.character(contraception_approach))),
         # Fixed contraception_approach for
         # "hormonal_pill, barrier_coitus_interruptus"
         contraception_approach = factor(ifelse(
           contraception_method == "hormonal_pill, barrier_coitus_interruptus",
           "hormonal_pill_only",
           as.character(contraception_approach))),
         # Fixed contraception_approach for
         # "hormonal_pill, barrier_no_penetrative_sex"
         contraception_approach = factor(ifelse(
           contraception_method == "hormonal_pill, barrier_no_penetrative_sex",
           "hormonal_pill_only",
           as.character(contraception_approach))),
         # Fixed contraception_approach for
         # "hormonal_other, barrier_condoms"
         contraception_approach = factor(ifelse(
           contraception_method == "hormonal_other, barrier_condoms",
           "hormonal_other+condoms",
           as.character(contraception_approach))),
         # Fixed contraception_approach for
         # "hormonal_other, barrier_condoms, barrier_coitus_interruptus"
         contraception_approach = factor(ifelse(
           contraception_method ==
             "hormonal_other, barrier_condoms, barrier_coitus_interruptus",
           "hormonal_other+condoms",
           as.character(contraception_approach))),
         contraception_approach = factor(ifelse(
           contraception_approach == "hormonal+barrier",
           "hormonal_pill+condoms",
           as.character(contraception_approach))),
         contraception_approach = factor(ifelse(
           contraception_method %contains% "awareness" &
             contraception_method %contains% "condoms" &
             !(contraception_method %contains% "hormonal"),
           "awareness+condoms",
           as.character(contraception_approach))))


data = data %>%
  mutate(contraception_approach = factor(contraception_approach,
                                         levels = c("hormonal_pill_only",
                                                    "hormonal_other_only",
                                                    "hormonal_pill+condoms",
                                                    "hormonal_other+condoms",
                                                    "barrier_pessar",
                                                    "awareness",
                                                    "awareness+condoms",
                                                    "condoms",
                                                    "other",
                                                    "nothing")))

qplot(factor(data$contraception_approach, levels = rev(levels(data$contraception_approach)))) +
  coord_flip()
table(data$contraception_approach)
```

### Current contraceptive status (hormonal vs. non hormonal)
```{r}
data = data %>% mutate(
  contraception_hormonal = factor(ifelse(contraception_approach %contains% "hormonal",
                                         "yes",
                                         "no")))
qplot(data$contraception_hormonal) + coord_flip()
table(data$contraception_hormonal)
```


### Changed contraception since meeting their partner
There will be NAs because we asked about contracetion when meeting partner only if participants were currently in a relationship
```{r}
crosstabs(~contraception_hormonal + contraception_meeting_partner, data = data)
data = data %>% mutate(
  contraception_change_since_meeting_partner =
    ifelse(contraception_hormonal == "yes" & contraception_meeting_partner == 1,
           "congruent_hormonal",
           ifelse(contraception_hormonal == "no" & contraception_meeting_partner == 0,
                  "congruent_nonhormonal",
                  ifelse(contraception_hormonal == "yes" & contraception_meeting_partner == 0,
                         "switched_to_hormonal",
                         ifelse(contraception_hormonal == "no" &
                                  contraception_meeting_partner == 1, "switched_to_nonhormonal",
                                NA)))))

qplot(data$contraception_change_since_meeting_partner) + coord_flip()
```

### Contraception meeting partner
```{r}
data = data %>%
  mutate(contraception_meeting_partner = factor(if_else(
    contraception_meeting_partner == 1,
    "yes", "no")))
```



### Diary information
calculate mean of libido, sex_active_frequency and actual sex frequency based on diary
```{r}
data_diary_means = data_diary %>%
  group_by(session) %>%
  summarise(diary_libido_mean = mean(high_libido, na.rm = T),
            diary_sex_active_mean = mean(sex_active, na.rm = T),
            diary_sex_active_sex_mean = mean(sex_activity_sex, na.rm = T))

qplot(data_diary_means$diary_libido_mean)
qplot(data_diary_means$diary_sex_active_mean)
qplot(data_diary_means$diary_sex_active_sex_mean)

data = left_join(data, data_diary_means, by = "session")
```


## Save Data
```{r}
save(data, data, file = "data/cleaned_selected_wrangled.rdata")
```

