---
title: "Analyses Selection Effects"
output:
  html_document:
    toc: true
    toc_depth: 4
    toc_float: true
    code_folding: 'hide'
    self_contained: false
---
  
## Data 
```{r results='hide',message=F,warning=F}
source("0_helpers.R")

load("data/cleaned_selected_wrangled.rdata")
```


## Selection Model {.tabset}
### Hormonal Contraception {.tabset}
#### Simple Model {.tabset}
##### Model
```{r}
m_selection_hc_simple = brm(contraception_hormonal ~
                              age + net_income + relationship_duration_factor,
                            data = data,
                            family = bernoulli("probit"),
                            file = "m_selection_hc_simple")
```

##### Summary
```{r}
kable(tidy(m_selection_hc_simple, intervals = T, prob = 0.90))
summary(m_selection_hc_simple, intervals = T, prob = 0.90)
```

##### Plots
```{r}
conditional_effects(m_selection_hc_simple, ask = FALSE)
```

##### Forest Plot for Effect Sizes {.active}
```{r}
m_selection_hc_simple %>%
  spread_draws(b_age,
               b_net_incomeeuro_500_1000, b_net_incomeeuro_1000_2000, 
               b_net_incomeeuro_2000_3000, b_net_incomeeuro_gt_3000, b_net_incomedont_tell,
               b_relationship_duration_factorPartnered_upto12months,
               b_relationship_duration_factorPartnered_upto28months,
               b_relationship_duration_factorPartnered_upto52months,
               b_relationship_duration_factorPartnered_morethan52months) %>%
  pivot_longer(cols = c(b_age,
               b_net_incomeeuro_500_1000, b_net_incomeeuro_1000_2000, 
               b_net_incomeeuro_2000_3000, b_net_incomeeuro_gt_3000, b_net_incomedont_tell,
               b_relationship_duration_factorPartnered_upto12months,
               b_relationship_duration_factorPartnered_upto28months,
               b_relationship_duration_factorPartnered_upto52months,
               b_relationship_duration_factorPartnered_morethan52months),
               names_to = "condition",
               values_to = "r_condition") %>%
  mutate(condition_mean = r_condition,
         group = ifelse(condition %contains% "b_relationship_duration_factor",
                        "Relationship Duration",
                        ifelse(condition %contains% "b_net_income",
                               "Income",
                               NA)),
         condition = ifelse(condition == "b_age", "Age",
                ifelse(condition == "b_net_incomeeuro_500_1000", "500-1000 Euro",
                ifelse(condition == "b_net_incomeeuro_1000_2000", "1000-2000 Euro",
                ifelse(condition == "b_net_incomeeuro_2000_3000", "2000-3000 Euro",
                ifelse(condition == "b_net_incomeeuro_gt_3000", ">3000 Euro",
                ifelse(condition == "b_net_incomedont_tell", "do not tell",
                ifelse(condition == "b_relationship_duration_factorPartnered_upto12months",
                       "0-12 months",
                ifelse(condition == "b_relationship_duration_factorPartnered_upto28months",
                       "13-28 months",
                ifelse(condition == "b_relationship_duration_factorPartnered_upto52months",
                       "29-52 months",
                ifelse(condition == "b_relationship_duration_factorPartnered_morethan52months",
                       ">52 months",
                       condition)))))))))),
         group = ifelse(is.na(group), condition, group),
         condition = factor(condition, levels = rev(c("Age",
                                        "500-1000 Euro", "1000-2000 Euro",
                                        "2000-3000 Euro", ">3000 Euro", "do not tell",
                                        "0-12 months", "13-28 months", "29-52 months",
                                        ">52 months")))) %>%
  ggplot(aes(y = condition, x = condition_mean, color = group)) +
  stat_halfeye() +
  geom_vline(xintercept = 0, linetype = "dotted", size = 1) +
  apatheme +
  theme(legend.title = element_blank()) +
  labs(x = "Effect Size Estimates", y = "Predictors")
```

#### Complex Model {.tabset}
##### Model
```{r}
m_selection_hc_complex = brm(contraception_hormonal ~
                              age + net_income + relationship_duration_factor +
                              education_years +
                              bfi_extra + bfi_neuro + bfi_agree + bfi_consc + bfi_open +
                              religiosity,
                            data = data,
                            family = bernoulli("probit"),
                            file = "m_selection_hc_complex")
```

##### Summary
```{r}
kable(tidy(m_selection_hc_complex, intervals = T, prob = 0.90))
summary(m_selection_hc_complex, intervals = T, prob = 0.90)
```

##### Plots
```{r}
conditional_effects(m_selection_hc_complex, ask = FALSE)
```

##### Forest Plot for Effect Sizes {.active}
```{r}
m_selection_hc_complex %>%
  spread_draws(b_age,
               b_net_incomeeuro_500_1000, b_net_incomeeuro_1000_2000, 
               b_net_incomeeuro_2000_3000, b_net_incomeeuro_gt_3000, b_net_incomedont_tell,
               b_relationship_duration_factorPartnered_upto12months,
               b_relationship_duration_factorPartnered_upto28months,
               b_relationship_duration_factorPartnered_upto52months,
               b_relationship_duration_factorPartnered_morethan52months,
               b_education_years,
               b_bfi_extra, b_bfi_neuro, b_bfi_agree, b_bfi_consc, b_bfi_open, 
               b_religiosity) %>%
  pivot_longer(cols = c(b_age,
               b_net_incomeeuro_500_1000, b_net_incomeeuro_1000_2000, 
               b_net_incomeeuro_2000_3000, b_net_incomeeuro_gt_3000, b_net_incomedont_tell,
               b_relationship_duration_factorPartnered_upto12months,
               b_relationship_duration_factorPartnered_upto28months,
               b_relationship_duration_factorPartnered_upto52months,
               b_relationship_duration_factorPartnered_morethan52months,
               b_education_years,
               b_bfi_extra, b_bfi_neuro, b_bfi_agree, b_bfi_consc, b_bfi_open, 
               b_religiosity),
               names_to = "condition",
               values_to = "r_condition") %>%
  mutate(condition_mean = r_condition,
         group = ifelse(condition %contains% "b_relationship_duration_factor",
                        "Relationship Duration",
                        ifelse(condition %contains% "b_net_income",
                               "Income",
                               NA)),
         condition = ifelse(condition == "b_age", "Age",
                ifelse(condition == "b_net_incomeeuro_500_1000", "500-1000 Euro",
                ifelse(condition == "b_net_incomeeuro_1000_2000", "1000-2000 Euro",
                ifelse(condition == "b_net_incomeeuro_2000_3000", "2000-3000 Euro",
                ifelse(condition == "b_net_incomeeuro_gt_3000", ">3000 Euro",
                ifelse(condition == "b_net_incomedont_tell", "do not tell",
                ifelse(condition == "b_relationship_duration_factorPartnered_upto12months",
                       "0-12 months",
                ifelse(condition == "b_relationship_duration_factorPartnered_upto28months",
                       "13-28 months",
                ifelse(condition == "b_relationship_duration_factorPartnered_upto52months",
                       "29-52 months",
                ifelse(condition == "b_relationship_duration_factorPartnered_morethan52months",
                       ">52 months",
                ifelse(condition == "b_education_years", "Years of Education",
                ifelse(condition == "b_bfi_extra", "Extraversion",
                ifelse(condition == "b_bfi_neuro", "Neuroticism",
                ifelse(condition == "b_bfi_agree", "Agreeableness",
                ifelse(condition == "b_bfi_consc", "Conscientiousness",
                ifelse(condition == "b_bfi_open", "Openness",
                ifelse(condition == "b_religiosity", "Religiosity",
                       condition))))))))))))))))),
         group = ifelse(is.na(group), condition, group),
         condition = factor(condition, levels = rev(c("Age",
                                        "500-1000 Euro", "1000-2000 Euro",
                                        "2000-3000 Euro", ">3000 Euro", "do not tell",
                                        "0-12 months", "13-28 months", "29-52 months",
                                        ">52 months",
                                        "Years of Education",
                                        "Extraversion", "Neuroticism", "Agreeableness",
                                         "Conscientiousness","Openness","Religiosity"))),
         group = factor(group, levels = c("Age", "Income", "Relationship Duration",
                                          
                                          "Years of Education",
                                          "Extraversion", "Neuroticism", "Agreeableness",
                                         "Conscientiousness","Openness","Religiosity"))) %>%
  ggplot(aes(y = condition, x = condition_mean, color = group)) +
  stat_halfeye() +
  geom_vline(xintercept = 0, linetype = "dotted", size = 1) +
  apatheme +
  theme(legend.title = element_blank()) +
  labs(x = "Effect Size Estimates", y = "Predictors")
```


#### Comparison {.active}
```{r}
compare_models = loo(m_selection_hc_simple, m_selection_hc_complex)
```
LooIC first model: `r round(compare_models$loos$m_selection_hc_simple$estimates[3,1], 2)`

LooIC second model: `r round(compare_models$loos$m_selection_hc_complex$estimates[3,1], 2)`

Model Comparisons: The difference between models is `r round(compare_models$diffs[2,1], 2)` compared to a standard error of `r round(compare_models$diffs[2,2], 2)`

```{r}
compare_models
```

### (In)congruent use of hormonal contraceptives {.tabset}
#### Simple Model {.tabset}
##### Model
```{r}
m_selection_congruent_simple = brm(congruent_contraception ~
                              age + net_income + relationship_duration_factor,
                            data = data,
                            family = bernoulli("probit"),
                            file = "m_selection_congruent_simple")
```

##### Summary
```{r}
kable(tidy(m_selection_congruent_simple, intervals = T, prob = 0.90))
summary(m_selection_congruent_simple, intervals = T, prob = 0.90)
```

##### Plots
```{r}
conditional_effects(m_selection_congruent_simple, ask = FALSE)

```

##### Forest Plot for Effect Sizes {.active}
```{r}
m_selection_congruent_simple %>%
  spread_draws(b_age,
               b_net_incomeeuro_500_1000, b_net_incomeeuro_1000_2000, 
               b_net_incomeeuro_2000_3000, b_net_incomeeuro_gt_3000, b_net_incomedont_tell,
               b_relationship_duration_factorPartnered_upto28months,
               b_relationship_duration_factorPartnered_upto52months,
               b_relationship_duration_factorPartnered_morethan52months) %>%
  pivot_longer(cols = c(b_age,
               b_net_incomeeuro_500_1000, b_net_incomeeuro_1000_2000, 
               b_net_incomeeuro_2000_3000, b_net_incomeeuro_gt_3000, b_net_incomedont_tell,
               b_relationship_duration_factorPartnered_upto28months,
               b_relationship_duration_factorPartnered_upto52months,
               b_relationship_duration_factorPartnered_morethan52months),
               names_to = "condition",
               values_to = "r_condition") %>%
  mutate(condition_mean = r_condition,
         group = ifelse(condition %contains% "b_relationship_duration_factor",
                        "Relationship Duration",
                        ifelse(condition %contains% "b_net_income",
                               "Income",
                               NA)),
         condition = ifelse(condition == "b_age", "Age",
                ifelse(condition == "b_net_incomeeuro_500_1000", "500-1000 Euro",
                ifelse(condition == "b_net_incomeeuro_1000_2000", "1000-2000 Euro",
                ifelse(condition == "b_net_incomeeuro_2000_3000", "2000-3000 Euro",
                ifelse(condition == "b_net_incomeeuro_gt_3000", ">3000 Euro",
                ifelse(condition == "b_net_incomedont_tell", "do not tell",
                ifelse(condition == "b_relationship_duration_factorPartnered_upto12months",
                       "0-12 months",
                ifelse(condition == "b_relationship_duration_factorPartnered_upto28months",
                       "13-28 months",
                ifelse(condition == "b_relationship_duration_factorPartnered_upto52months",
                       "29-52 months",
                ifelse(condition == "b_relationship_duration_factorPartnered_morethan52months",
                       ">52 months",
                       condition)))))))))),
         group = ifelse(is.na(group), condition, group),
         condition = factor(condition, levels = rev(c("Age",
                                        "500-1000 Euro", "1000-2000 Euro",
                                        "2000-3000 Euro", ">3000 Euro", "do not tell",
                                        "13-28 months", "29-52 months",
                                        ">52 months")))) %>%
  ggplot(aes(y = condition, x = condition_mean, color = group)) +
  stat_halfeye() +
  geom_vline(xintercept = 0, linetype = "dotted", size = 1) +
  apatheme +
  theme(legend.title = element_blank()) +
  labs(x = "Effect Size Estimates", y = "Predictors")

```


#### Complex Model {.tabset}
##### Model
```{r}
m_selection_congruent_complex = brm(congruent_contraception ~
                              age + net_income + relationship_duration_factor +
                              education_years +
                              bfi_extra + bfi_neuro + bfi_agree + bfi_consc + bfi_open +
                              religiosity,
                            data = data,
                            family = bernoulli("probit"),
                            file = "m_selection_congruent_complex")
```

##### Summary
```{r}
kable(tidy(m_selection_congruent_complex, intervals = T, prob = 0.90))
summary(m_selection_congruent_complex, intervals = T, prob = 0.90)


```

##### Plots
```{r}
conditional_effects(m_selection_congruent_complex, ask = FALSE)
```

##### Forest Plot for Effect Sizes {.active}
```{r}
m_selection_congruent_complex %>%
  spread_draws(b_age,
               b_net_incomeeuro_500_1000, b_net_incomeeuro_1000_2000, 
               b_net_incomeeuro_2000_3000, b_net_incomeeuro_gt_3000, b_net_incomedont_tell,
               b_relationship_duration_factorPartnered_upto28months,
               b_relationship_duration_factorPartnered_upto52months,
               b_relationship_duration_factorPartnered_morethan52months,
               b_education_years,
               b_bfi_extra, b_bfi_neuro, b_bfi_agree, b_bfi_consc, b_bfi_open, 
               b_religiosity) %>%
  pivot_longer(cols = c(b_age,
               b_net_incomeeuro_500_1000, b_net_incomeeuro_1000_2000, 
               b_net_incomeeuro_2000_3000, b_net_incomeeuro_gt_3000, b_net_incomedont_tell,
               b_relationship_duration_factorPartnered_upto28months,
               b_relationship_duration_factorPartnered_upto52months,
               b_relationship_duration_factorPartnered_morethan52months,
               b_education_years,
               b_bfi_extra, b_bfi_neuro, b_bfi_agree, b_bfi_consc, b_bfi_open, 
               b_religiosity),
               names_to = "condition",
               values_to = "r_condition") %>%
  mutate(condition_mean = r_condition,
         group = ifelse(condition %contains% "b_relationship_duration_factor",
                        "Relationship Duration",
                        ifelse(condition %contains% "b_net_income",
                               "Income",
                               NA)),
         condition = ifelse(condition == "b_age", "Age",
                ifelse(condition == "b_net_incomeeuro_500_1000", "500-1000 Euro",
                ifelse(condition == "b_net_incomeeuro_1000_2000", "1000-2000 Euro",
                ifelse(condition == "b_net_incomeeuro_2000_3000", "2000-3000 Euro",
                ifelse(condition == "b_net_incomeeuro_gt_3000", ">3000 Euro",
                ifelse(condition == "b_net_incomedont_tell", "do not tell",
                ifelse(condition == "b_relationship_duration_factorPartnered_upto12months",
                       "0-12 months",
                ifelse(condition == "b_relationship_duration_factorPartnered_upto28months",
                       "13-28 months",
                ifelse(condition == "b_relationship_duration_factorPartnered_upto52months",
                       "29-52 months",
                ifelse(condition == "b_relationship_duration_factorPartnered_morethan52months",
                       ">52 months",
                ifelse(condition == "b_education_years", "Years of Education",
                ifelse(condition == "b_bfi_extra", "Extraversion",
                ifelse(condition == "b_bfi_neuro", "Neuroticism",
                ifelse(condition == "b_bfi_agree", "Agreeableness",
                ifelse(condition == "b_bfi_consc", "Conscientiousness",
                ifelse(condition == "b_bfi_open", "Openness",
                ifelse(condition == "b_religiosity", "Religiosity",
                       condition))))))))))))))))),
         group = ifelse(is.na(group), condition, group),
         condition = factor(condition, levels = rev(c("Age",
                                        "500-1000 Euro", "1000-2000 Euro",
                                        "2000-3000 Euro", ">3000 Euro", "do not tell",
                                        "13-28 months", "29-52 months",
                                        ">52 months",
                                        "Years of Education",
                                        "Extraversion", "Neuroticism", "Agreeableness",
                                         "Conscientiousness","Openness","Religiosity"))),
         group = factor(group, levels = c("Age", "Income", "Relationship Duration",
                                          
                                          "Years of Education",
                                          "Extraversion", "Neuroticism", "Agreeableness",
                                         "Conscientiousness","Openness","Religiosity"))) %>%
  ggplot(aes(y = condition, x = condition_mean, color = group)) +
  stat_halfeye() +
  geom_vline(xintercept = 0, linetype = "dotted", size = 1) +
  apatheme +
  theme(legend.title = element_blank()) +
  labs(x = "Effect Size Estimates", y = "Predictors")

```


#### Comparison {.active}
```{r}
compare_models = loo(m_selection_congruent_simple, m_selection_congruent_complex)
```
LooIC first model: `r round(compare_models$loos$m_selection_congruent_simple$estimates[3,1], 2)`

LooIC second model: `r round(compare_models$loos$m_selection_congruent_complex$estimates[3,1], 2)`

Model Comparisons: The difference between models is `r round(compare_models$diffs[2,1], 2)` compared to a standard error of `r round(compare_models$diffs[2,2], 2)`

```{r}
compare_models
```

### (In)congruent use of hormonal contraceptives inclduing current contraceptive method {.tabset}
#### Simple Model {.tabset}
##### Model
```{r}
m_selection_congruent_simple_includinghc = brm(congruent_contraception ~
                              (age + net_income + relationship_duration_factor) *
                                contraception_meeting_partner,
                            data = data,
                            family = bernoulli("probit"),
                            file = "m_selection_congruent_simple_includinghc")
```

##### Summary
```{r}
kable(tidy(m_selection_congruent_simple_includinghc, intervals = T, prob = 0.90))
summary(m_selection_congruent_simple_includinghc, intervals = T, prob = 0.90)
```

##### Plots
```{r}
conditional_effects(m_selection_congruent_simple_includinghc, ask = FALSE)
```

##### Forest Plot for Effect Sizes {.active}
```{r}
```


#### Complex Model {.tabset}
##### Model
```{r}
m_selection_congruent_complex_includinghc = brm(congruent_contraception  ~
                              (age + net_income + relationship_duration_factor +
                                 education_years +
                              bfi_extra + bfi_neuro + bfi_agree + bfi_consc + bfi_open +
                              religiosity) *
                                contraception_meeting_partner,
                            data = data,
                            family = bernoulli("probit"),
                            inits = "0",
                            file = "m_selection_congruent_complex_includinghc")
```

##### Summary
```{r}
kable(tidy(m_selection_congruent_complex_includinghc, intervals = T, prob = 0.90))
summary(m_selection_congruent_complex_includinghc, intervals = T, prob = 0.90)
```

##### Plots
```{r}
conditional_effects(m_selection_congruent_complex_includinghc, ask = FALSE)
```

##### Forest Plot for Effect Sizes {.active}
```{r}
```


#### Comparison {.active}
```{r}
compare_models = loo(m_selection_congruent_simple_includinghc,
                     m_selection_congruent_complex_includinghc)
```
LooIC first model: `r round(compare_models$loos$m_selection_congruent_simple_includinghc$estimates[3,1], 2)`

LooIC second model: `r round(compare_models$loos$m_selection_congruent_complex_includinghc$estimates[3,1], 2)`

Model Comparisons: The difference between models is `r round(compare_models$diffs[2,1], 2)` compared to a standard error of `r round(compare_models$diffs[2,2], 2)`

```{r}
compare_models
```

```{r}
compare_models = loo(m_selection_congruent_simple,
                     m_selection_congruent_simple_includinghc)
```
LooIC first model: `r round(compare_models$loos$m_selection_congruent_simple$estimates[3,1], 2)`

LooIC second model: `r round(compare_models$loos$m_selection_congruent_simple_includinghc$estimates[3,1], 2)`

Model Comparisons: The difference between models is `r round(compare_models$diffs[2,1], 2)` compared to a standard error of `r round(compare_models$diffs[2,2], 2)`

```{r}
compare_models
```


```{r}
compare_models = loo(m_selection_congruent_complex,
                     m_selection_congruent_complex_includinghc)
```
LooIC first model: `r round(compare_models$loos$m_selection_congruent_complex$estimates[3,1], 2)`

LooIC second model: `r round(compare_models$loos$m_selection_congruent_complex_includinghc$estimates[3,1], 2)`

Model Comparisons: The difference between models is `r round(compare_models$diffs[2,1], 2)` compared to a standard error of `r round(compare_models$diffs[2,2], 2)`

```{r}
compare_models
```


