---
title: "Analyses Effects of Contraception"
output:
  html_document:
    toc: true
    toc_depth: 4
    toc_float: true
    code_folding: 'hide'
    self_contained: false
---
  
## Data 
```{r results='hide',message=F,warning=F}
source("0_helpers.R")

load("data/cleaned_selected_wrangled.rdata")
```


## Selection Model {.tabset}
### Hormonal Contraception {.tabset}
#### Simple Model {.tabset}
##### Model
```{r}
m_selection_hc_simple = brm(contraception_hormonal ~
                              age + net_income + relationship_duration_factor,
                            data = data,
                            family = bernoulli("probit"),
                            file = "m_selection_hc_simple")
```

##### Summary
```{r}
kable(tidy(m_selection_hc_simple, intervals = T, prob = 0.95))
summary(m_selection_hc_simple)
```

##### Plots
```{r}
conditional_effects(m_selection_hc_simple, ask = FALSE)
```

##### Forest Plot for Effect Sizes {.active}
```{r}
m_selection_hc_simple %>%
  spread_draws(b_age,
               b_net_incomeeuro_500_1000, b_net_incomeeuro_1000_2000, 
               b_net_incomeeuro_2000_3000, b_net_incomeeuro_gt_3000, b_net_incomedont_tell,
               b_relationship_duration_factorPartnered_upto12months,
               b_relationship_duration_factorPartnered_upto28months,
               b_relationship_duration_factorPartnered_upto52months,
               b_relationship_duration_factorPartnered_morethan52months) %>%
  pivot_longer(cols = c(b_age,
               b_net_incomeeuro_500_1000, b_net_incomeeuro_1000_2000, 
               b_net_incomeeuro_2000_3000, b_net_incomeeuro_gt_3000, b_net_incomedont_tell,
               b_relationship_duration_factorPartnered_upto12months,
               b_relationship_duration_factorPartnered_upto28months,
               b_relationship_duration_factorPartnered_upto52months,
               b_relationship_duration_factorPartnered_morethan52months),
               names_to = "condition",
               values_to = "r_condition") %>%
  mutate(condition_mean = r_condition,
         group = ifelse(condition %contains% "b_relationship_duration_factor",
                        "Relationship Duration",
                        ifelse(condition %contains% "b_net_income",
                               "Income",
                               NA)),
         condition = ifelse(condition == "b_age", "Age",
                ifelse(condition == "b_net_incomeeuro_500_1000", "500-1000 Euro",
                ifelse(condition == "b_net_incomeeuro_1000_2000", "1000-2000 Euro",
                ifelse(condition == "b_net_incomeeuro_2000_3000", "2000-3000 Euro",
                ifelse(condition == "b_net_incomeeuro_gt_3000", ">3000 Euro",
                ifelse(condition == "b_net_incomedont_tell", "do not tell",
                ifelse(condition == "b_relationship_duration_factorPartnered_upto12months",
                       "0-12 months",
                ifelse(condition == "b_relationship_duration_factorPartnered_upto28months",
                       "13-28 months",
                ifelse(condition == "b_relationship_duration_factorPartnered_upto52months",
                       "29-52 months",
                ifelse(condition == "b_relationship_duration_factorPartnered_morethan52months",
                       ">52 months",
                       condition)))))))))),
         group = ifelse(is.na(group), condition, group),
         condition = factor(condition, levels = rev(c("Age",
                                        "500-1000 Euro", "1000-2000 Euro",
                                        "2000-3000 Euro", ">3000 Euro", "do not tell",
                                        "0-12 months", "13-28 months", "29-52 months",
                                        ">52 months")))) %>%
  ggplot(aes(y = condition, x = condition_mean, color = group)) +
  stat_halfeye() +
  geom_vline(xintercept = 0, linetype = "dotted", size = 1) +
  apatheme +
  theme(legend.title = element_blank()) +
  labs(x = "Effect Size Estimate", y = "Predictor")
```

#### Complex Model {.tabset}
##### Model
```{r}
m_selection_hc_complex = brm(contraception_hormonal ~
                              age + net_income + relationship_duration_factor +
                              education_years +
                              bfi_extra + bfi_neuro + bfi_agree + bfi_consc + bfi_open +
                              religiosity,
                            data = data,
                            family = bernoulli("probit"),
                            file = "m_selection_hc_complex")
```

##### Summary
```{r}
tidy(m_selection_hc_complex, intervals = T, prob = 0.95)
summary(m_selection_hc_complex)
```

##### Plots
```{r}
conditional_effects(m_selection_hc_complex, ask = FALSE)
```

##### Forest Plot for Effect Sizes {.active}
```{r}
m_selection_hc_complex %>%
  spread_draws(b_age,
               b_net_incomeeuro_500_1000, b_net_incomeeuro_1000_2000, 
               b_net_incomeeuro_2000_3000, b_net_incomeeuro_gt_3000, b_net_incomedont_tell,
               b_relationship_duration_factorPartnered_upto12months,
               b_relationship_duration_factorPartnered_upto28months,
               b_relationship_duration_factorPartnered_upto52months,
               b_relationship_duration_factorPartnered_morethan52months,
               b_education_years,
               b_bfi_extra, b_bfi_neuro, b_bfi_agree, b_bfi_consc, b_bfi_open, 
               b_religiosity) %>%
  pivot_longer(cols = c(b_age,
               b_net_incomeeuro_500_1000, b_net_incomeeuro_1000_2000, 
               b_net_incomeeuro_2000_3000, b_net_incomeeuro_gt_3000, b_net_incomedont_tell,
               b_relationship_duration_factorPartnered_upto12months,
               b_relationship_duration_factorPartnered_upto28months,
               b_relationship_duration_factorPartnered_upto52months,
               b_relationship_duration_factorPartnered_morethan52months,
               b_education_years,
               b_bfi_extra, b_bfi_neuro, b_bfi_agree, b_bfi_consc, b_bfi_open, 
               b_religiosity),
               names_to = "condition",
               values_to = "r_condition") %>%
  mutate(condition_mean = r_condition,
         group = ifelse(condition %contains% "b_relationship_duration_factor",
                        "Relationship Duration",
                        ifelse(condition %contains% "b_net_income",
                               "Income",
                               NA)),
         condition = ifelse(condition == "b_age", "Age",
                ifelse(condition == "b_net_incomeeuro_500_1000", "500-1000 Euro",
                ifelse(condition == "b_net_incomeeuro_1000_2000", "1000-2000 Euro",
                ifelse(condition == "b_net_incomeeuro_2000_3000", "2000-3000 Euro",
                ifelse(condition == "b_net_incomeeuro_gt_3000", ">3000 Euro",
                ifelse(condition == "b_net_incomedont_tell", "do not tell",
                ifelse(condition == "b_relationship_duration_factorPartnered_upto12months",
                       "0-12 months",
                ifelse(condition == "b_relationship_duration_factorPartnered_upto28months",
                       "13-28 months",
                ifelse(condition == "b_relationship_duration_factorPartnered_upto52months",
                       "29-52 months",
                ifelse(condition == "b_relationship_duration_factorPartnered_morethan52months",
                       ">52 months",
                ifelse(condition == "b_education_years", "Years of Education",
                ifelse(condition == "b_bfi_extra", "Extraversion",
                ifelse(condition == "b_bfi_neuro", "Neuroticism",
                ifelse(condition == "b_bfi_agree", "Agreeableness",
                ifelse(condition == "b_bfi_consc", "Conscientiousness",
                ifelse(condition == "b_bfi_open", "Openness",
                ifelse(condition == "b_religiosity", "Religiosity",
                       condition))))))))))))))))),
         group = ifelse(is.na(group), condition, group),
         condition = factor(condition, levels = rev(c("Age",
                                        "500-1000 Euro", "1000-2000 Euro",
                                        "2000-3000 Euro", ">3000 Euro", "do not tell",
                                        "0-12 months", "13-28 months", "29-52 months",
                                        ">52 months",
                                        "Years of Education",
                                        "Extraversion", "Neuroticism", "Agreeableness",
                                         "Conscientiousness","Openness","Religiosity"))),
         group = factor(group, levels = c("Age", "Income", "Relationship Duration",
                                          
                                          "Years of Education",
                                          "Extraversion", "Neuroticism", "Agreeableness",
                                         "Conscientiousness","Openness","Religiosity"))) %>%
  ggplot(aes(y = condition, x = condition_mean, color = group)) +
  stat_halfeye() +
  geom_vline(xintercept = 0, linetype = "dotted", size = 1) +
  apatheme +
  theme(legend.title = element_blank()) +
  labs(x = "Effect Size Estimate", y = "Predictor")
```


#### Comparison {.active}
```{r}
compare_models = loo(m_selection_hc_simple, m_selection_hc_complex)
```
LooIC first model: `r round(compare_models$loos$m_selection_hc_simple$estimates[3,1], 2)`

LooIC second model: `r round(compare_models$loos$m_selection_hc_complex$estimates[3,1], 2)`

Model Comparisons: The difference between models is `r round(compare_models$diffs[2,1], 2)` compared to a standard error of `r round(compare_models$diffs[2,2], 2)`

```{r}
compare_models
```

### (In)congruent use of hormonal contraceptives {.tabset}
#### Simple Model {.tabset}
##### Model
```{r}
m_selection_congruent_simple = brm(congruent_contraception ~
                              age + net_income + relationship_duration_factor,
                            data = data,
                            family = bernoulli("probit"),
                            file = "m_selection_congruent_simple")

m_selection_congruent_simple_includinghc = brm(congruent_contraception ~
                              age + net_income + relationship_duration_factor +
                                contraception_hormonal,
                            data = data,
                            family = bernoulli("probit"),
                            file = "m_selection_congruent_simple_includinghc")
```

##### Summary
```{r}
kable(tidy(m_selection_congruent_simple, intervals = T, prob = 0.95))
summary(m_selection_congruent_simple)

kable(tidy(m_selection_congruent_simple_includinghc, intervals = T, prob = 0.95))
summary(m_selection_congruent_simple_includinghc)
```

##### Plots
```{r}
conditional_effects(m_selection_congruent_simple, ask = FALSE)

conditional_effects(m_selection_congruent_simple_includinghc, ask = FALSE)

```

##### Forest Plot for Effect Sizes {.active}
```{r}
m_selection_congruent_simple %>%
  spread_draws(b_age,
               b_net_incomeeuro_500_1000, b_net_incomeeuro_1000_2000, 
               b_net_incomeeuro_2000_3000, b_net_incomeeuro_gt_3000, b_net_incomedont_tell,
               b_relationship_duration_factorPartnered_upto28months,
               b_relationship_duration_factorPartnered_upto52months,
               b_relationship_duration_factorPartnered_morethan52months) %>%
  pivot_longer(cols = c(b_age,
               b_net_incomeeuro_500_1000, b_net_incomeeuro_1000_2000, 
               b_net_incomeeuro_2000_3000, b_net_incomeeuro_gt_3000, b_net_incomedont_tell,
               b_relationship_duration_factorPartnered_upto28months,
               b_relationship_duration_factorPartnered_upto52months,
               b_relationship_duration_factorPartnered_morethan52months),
               names_to = "condition",
               values_to = "r_condition") %>%
  mutate(condition_mean = r_condition,
         group = ifelse(condition %contains% "b_relationship_duration_factor",
                        "Relationship Duration",
                        ifelse(condition %contains% "b_net_income",
                               "Income",
                               NA)),
         condition = ifelse(condition == "b_age", "Age",
                ifelse(condition == "b_net_incomeeuro_500_1000", "500-1000 Euro",
                ifelse(condition == "b_net_incomeeuro_1000_2000", "1000-2000 Euro",
                ifelse(condition == "b_net_incomeeuro_2000_3000", "2000-3000 Euro",
                ifelse(condition == "b_net_incomeeuro_gt_3000", ">3000 Euro",
                ifelse(condition == "b_net_incomedont_tell", "do not tell",
                ifelse(condition == "b_relationship_duration_factorPartnered_upto12months",
                       "0-12 months",
                ifelse(condition == "b_relationship_duration_factorPartnered_upto28months",
                       "13-28 months",
                ifelse(condition == "b_relationship_duration_factorPartnered_upto52months",
                       "29-52 months",
                ifelse(condition == "b_relationship_duration_factorPartnered_morethan52months",
                       ">52 months",
                       condition)))))))))),
         group = ifelse(is.na(group), condition, group),
         condition = factor(condition, levels = rev(c("Age",
                                        "500-1000 Euro", "1000-2000 Euro",
                                        "2000-3000 Euro", ">3000 Euro", "do not tell",
                                        "13-28 months", "29-52 months",
                                        ">52 months")))) %>%
  ggplot(aes(y = condition, x = condition_mean, color = group)) +
  stat_halfeye() +
  geom_vline(xintercept = 0, linetype = "dotted", size = 1) +
  apatheme +
  theme(legend.title = element_blank()) +
  labs(x = "Effect Size Estimate", y = "Predictor")

m_selection_congruent_simple_includinghc %>%
  spread_draws(b_age,
               b_net_incomeeuro_500_1000, b_net_incomeeuro_1000_2000, 
               b_net_incomeeuro_2000_3000, b_net_incomeeuro_gt_3000, b_net_incomedont_tell,
               b_relationship_duration_factorPartnered_upto28months,
               b_relationship_duration_factorPartnered_upto52months,
               b_relationship_duration_factorPartnered_morethan52months,
               b_contraception_hormonalyes) %>%
  pivot_longer(cols = c(b_age,
               b_net_incomeeuro_500_1000, b_net_incomeeuro_1000_2000, 
               b_net_incomeeuro_2000_3000, b_net_incomeeuro_gt_3000, b_net_incomedont_tell,
               b_relationship_duration_factorPartnered_upto28months,
               b_relationship_duration_factorPartnered_upto52months,
               b_relationship_duration_factorPartnered_morethan52months,
               b_contraception_hormonalyes),
               names_to = "condition",
               values_to = "r_condition") %>%
  mutate(condition_mean = r_condition,
         group = ifelse(condition %contains% "b_relationship_duration_factor",
                        "Relationship Duration",
                        ifelse(condition %contains% "b_net_income",
                               "Income",
                               NA)),
         condition = ifelse(condition == "b_age", "Age",
                ifelse(condition == "b_net_incomeeuro_500_1000", "500-1000 Euro",
                ifelse(condition == "b_net_incomeeuro_1000_2000", "1000-2000 Euro",
                ifelse(condition == "b_net_incomeeuro_2000_3000", "2000-3000 Euro",
                ifelse(condition == "b_net_incomeeuro_gt_3000", ">3000 Euro",
                ifelse(condition == "b_net_incomedont_tell", "do not tell",
                ifelse(condition == "b_relationship_duration_factorPartnered_upto12months",
                       "0-12 months",
                ifelse(condition == "b_relationship_duration_factorPartnered_upto28months",
                       "13-28 months",
                ifelse(condition == "b_relationship_duration_factorPartnered_upto52months",
                       "29-52 months",
                ifelse(condition == "b_relationship_duration_factorPartnered_morethan52months",
                       ">52 months",
                ifelse(condition == "b_contraception_hormonalyes",
                       "Currently Using HCs",
                       condition))))))))))),
         group = ifelse(is.na(group), condition, group),
         condition = factor(condition, levels = rev(c("Age",
                                        "500-1000 Euro", "1000-2000 Euro",
                                        "2000-3000 Euro", ">3000 Euro", "do not tell",
                                        "13-28 months", "29-52 months",
                                        ">52 months",
                                        "Currently Using HCs"))),
         group = factor(group, levels = c("Age", "Income", "Relationship Duration",
                                          "Currently Using HCs"))) %>%
  ggplot(aes(y = condition, x = condition_mean, color = group)) +
  stat_halfeye() +
  geom_vline(xintercept = 0, linetype = "dotted", size = 1) +
  apatheme +
  theme(legend.title = element_blank()) +
  labs(x = "Effect Size Estimate", y = "Predictor")
```


#### Complex Model {.tabset}
##### Model
```{r}
m_selection_congruent_complex = brm(congruent_contraception ~
                              age + net_income + relationship_duration_factor +
                              education_years +
                              bfi_extra + bfi_neuro + bfi_agree + bfi_consc + bfi_open +
                              religiosity,
                            data = data,
                            family = bernoulli("probit"),
                            file = "m_selection_congruent_complex")

m_selection_congruent_complex_includinghc = brm(congruent_contraception ~
                              age + net_income + relationship_duration_factor  +
                                contraception_hormonal +
                                education_years +
                              bfi_extra + bfi_neuro + bfi_agree + bfi_consc + bfi_open +
                              religiosity,
                            data = data,
                            family = bernoulli("probit"),
                            file = "m_selection_congruent_complex_includinghc")
```

##### Summary
```{r}
tidy(m_selection_congruent_complex, intervals = T, prob = 0.95)
summary(m_selection_congruent_complex)

tidy(m_selection_congruent_complex_includinghc, intervals = T, prob = 0.95)
summary(m_selection_congruent_complex_includinghc)
```

##### Plots
```{r}
conditional_effects(m_selection_congruent_complex, ask = FALSE)
conditional_effects(m_selection_congruent_complex_includinghc, ask = FALSE)
```

##### Forest Plot for Effect Sizes {.active}
```{r}
m_selection_congruent_complex %>%
  spread_draws(b_age,
               b_net_incomeeuro_500_1000, b_net_incomeeuro_1000_2000, 
               b_net_incomeeuro_2000_3000, b_net_incomeeuro_gt_3000, b_net_incomedont_tell,
               b_relationship_duration_factorPartnered_upto28months,
               b_relationship_duration_factorPartnered_upto52months,
               b_relationship_duration_factorPartnered_morethan52months,
               b_education_years,
               b_bfi_extra, b_bfi_neuro, b_bfi_agree, b_bfi_consc, b_bfi_open, 
               b_religiosity) %>%
  pivot_longer(cols = c(b_age,
               b_net_incomeeuro_500_1000, b_net_incomeeuro_1000_2000, 
               b_net_incomeeuro_2000_3000, b_net_incomeeuro_gt_3000, b_net_incomedont_tell,
               b_relationship_duration_factorPartnered_upto28months,
               b_relationship_duration_factorPartnered_upto52months,
               b_relationship_duration_factorPartnered_morethan52months,
               b_education_years,
               b_bfi_extra, b_bfi_neuro, b_bfi_agree, b_bfi_consc, b_bfi_open, 
               b_religiosity),
               names_to = "condition",
               values_to = "r_condition") %>%
  mutate(condition_mean = r_condition,
         group = ifelse(condition %contains% "b_relationship_duration_factor",
                        "Relationship Duration",
                        ifelse(condition %contains% "b_net_income",
                               "Income",
                               NA)),
         condition = ifelse(condition == "b_age", "Age",
                ifelse(condition == "b_net_incomeeuro_500_1000", "500-1000 Euro",
                ifelse(condition == "b_net_incomeeuro_1000_2000", "1000-2000 Euro",
                ifelse(condition == "b_net_incomeeuro_2000_3000", "2000-3000 Euro",
                ifelse(condition == "b_net_incomeeuro_gt_3000", ">3000 Euro",
                ifelse(condition == "b_net_incomedont_tell", "do not tell",
                ifelse(condition == "b_relationship_duration_factorPartnered_upto12months",
                       "0-12 months",
                ifelse(condition == "b_relationship_duration_factorPartnered_upto28months",
                       "13-28 months",
                ifelse(condition == "b_relationship_duration_factorPartnered_upto52months",
                       "29-52 months",
                ifelse(condition == "b_relationship_duration_factorPartnered_morethan52months",
                       ">52 months",
                ifelse(condition == "b_education_years", "Years of Education",
                ifelse(condition == "b_bfi_extra", "Extraversion",
                ifelse(condition == "b_bfi_neuro", "Neuroticism",
                ifelse(condition == "b_bfi_agree", "Agreeableness",
                ifelse(condition == "b_bfi_consc", "Conscientiousness",
                ifelse(condition == "b_bfi_open", "Openness",
                ifelse(condition == "b_religiosity", "Religiosity",
                       condition))))))))))))))))),
         group = ifelse(is.na(group), condition, group),
         condition = factor(condition, levels = rev(c("Age",
                                        "500-1000 Euro", "1000-2000 Euro",
                                        "2000-3000 Euro", ">3000 Euro", "do not tell",
                                        "13-28 months", "29-52 months",
                                        ">52 months",
                                        "Years of Education",
                                        "Extraversion", "Neuroticism", "Agreeableness",
                                         "Conscientiousness","Openness","Religiosity"))),
         group = factor(group, levels = c("Age", "Income", "Relationship Duration",
                                          
                                          "Years of Education",
                                          "Extraversion", "Neuroticism", "Agreeableness",
                                         "Conscientiousness","Openness","Religiosity"))) %>%
  ggplot(aes(y = condition, x = condition_mean, color = group)) +
  stat_halfeye() +
  geom_vline(xintercept = 0, linetype = "dotted", size = 1) +
  apatheme +
  theme(legend.title = element_blank()) +
  labs(x = "Effect Size Estimate", y = "Predictor")

m_selection_congruent_complex_includinghc %>%
  tidy(., intervals = T, prob = 0.95) %>%
  filter(term != "b_Intercept",
         term != "lp__") %>%
  mutate(group = ifelse(term %contains% "b_relationship_duration_factor",
                        "Relationship Duration",
                        ifelse(term %contains% "b_net_income",
                               "Income",
                               NA)),
         term = ifelse(term == "b_age", "Age",
                ifelse(term == "b_net_incomeeuro_500_1000", "500-1000 Euro",
                ifelse(term == "b_net_incomeeuro_1000_2000", "1000-2000 Euro",
                ifelse(term == "b_net_incomeeuro_2000_3000", "2000-3000 Euro",
                ifelse(term == "b_net_incomeeuro_gt_3000", ">3000 Euro",
                ifelse(term == "b_net_incomedont_tell", "do not tell",
                ifelse(term == "b_relationship_duration_factorPartnered_upto12months",
                       "0-12 months",
                ifelse(term == "b_relationship_duration_factorPartnered_upto28months",
                       "13-28 months",
                ifelse(term == "b_relationship_duration_factorPartnered_upto52months",
                       "29-52 months",
                ifelse(term == "b_relationship_duration_factorPartnered_morethan52months",
                       ">52 months",
                ifelse(term == "b_contraception_hormonalyes",
                       "Currently Using HCs",
                ifelse(term == "b_education_years", "Years of Education",
                ifelse(term == "b_bfi_extra", "Extraversion",
                ifelse(term == "b_bfi_neuro", "Neuroticism",
                ifelse(term == "b_bfi_agree", "Agreeableness",
                ifelse(term == "b_bfi_consc", "Conscientiousness",
                ifelse(term == "b_bfi_open", "Openness",
                ifelse(term == "b_religiosity", "Religiosity",
                       term)))))))))))))))))),
         group = ifelse(is.na(group), term, group),
         term = factor(term, levels = rev(c("Age",
                                        "500-1000 Euro", "1000-2000 Euro",
                                        "2000-3000 Euro", ">3000 Euro", "do not tell",
                                        "0-12 months", "13-28 months", "29-52 months",
                                        ">52 months",
                                        "Currently Using HCs",
                                        "Years of Education",
                                        "Extraversion", "Neuroticism", "Agreeableness",
                                         "Conscientiousness","Openness","Religiosity")))) %>%
  ggplot(., aes(y = term, x = estimate, xmin = lower, xmax = upper, color = group)) +
  geom_pointinterval() + 
  apatheme +
  theme(legend.title = element_blank()) +
  labs(x = "Effect Size Estimate", y = "Predictor")
```


#### Comparison {.active}
```{r}
compare_models = loo(m_selection_congruent_simple, m_selection_congruent_complex)
```
LooIC first model: `r round(compare_models$loos$m_selection_congruent_simple$estimates[3,1], 2)`

LooIC second model: `r round(compare_models$loos$m_selection_congruent_complex$estimates[3,1], 2)`

Model Comparisons: The difference between models is `r round(compare_models$diffs[2,1], 2)` compared to a standard error of `r round(compare_models$diffs[2,2], 2)`

```{r}
compare_models
```

## Effects of Hormonl Contraceptives {.tabset}
### Attractiveness of Partner {.tabset}
#### Model
```{r}
m_hc_atrr = brm(attractiveness_partner ~ contraception_hormonal,
                data = data, family = gaussian(),
                file = "m_hc_atrr")
```

#### Summary
```{r}
tidy(m_hc_atrr, intervals = T, prob = 0.95)
summary(m_hc_atrr, intervals = T, prob = 0.95)
```

#### Comparison with ROPE
```{r}
plot(equivalence_test(m_hc_atrr, range = c(-0.07, 0.07)), ci = 0.95)
equivalence_test(m_hc_atrr, range = c(-0.07, 0.07), ci = 0.95)
```

#### Plots
```{r}
conditional_effects(m_hc_atrr, ask = FALSE)
```

#### Forest Plot for Effect Sizes {.active}
```{r}
m_hc_atrr %>%
  spread_draws(b_contraception_hormonalyes) %>%
  pivot_longer(cols = c(b_contraception_hormonalyes),
               names_to = "condition",
               values_to = "r_condition") %>%
  mutate(condition_mean = r_condition,
         group = ifelse(condition %contains% "b_contraception_hormonalyes",
                        "Contraception", NA),
         condition = ifelse(condition %contains% "b_contraception_hormonalyes",
                        "Hormonal Contraception", NA)) %>%
  ggplot(aes(y = condition,
             x = condition_mean,
             fill = stat(abs(x) < 0.07))) +
  stat_halfeye() +
  geom_vline(xintercept = c(-0.07, 0.07), linetype = "dotted") +
  apatheme +
  theme(legend.position = "none") +
  scale_fill_manual(values = c("gray80", "skyblue")) +
  labs(x = "Effect Size Estimate", y = "Predictor") +
  xlim (-0.6, 0.6)
```

### Relationship Satisfaction {.tabset}
#### Model
```{r}
m_hc_relsat = brm(relationship_satisfaction ~ contraception_hormonal,
                data = data, family = gaussian(),
                file = "m_hc_relsat")
```

#### Summary
```{r}
tidy(m_hc_relsat, intervals = T, prob = 0.95)
summary(m_hc_relsat, intervals = T, prob = 0.95)
```

#### Comparison with ROPE
```{r}
plot(equivalence_test(m_hc_relsat, range = c(-0.04, 0.04)), ci = 0.95)
equivalence_test(m_hc_relsat, range = c(-0.04, 0.04), ci = 0.95)
```

#### Plots
```{r}
conditional_effects(m_hc_relsat, ask = FALSE)
```

#### Forest Plot for Effect Sizes {.active}
```{r}
m_hc_relsat %>%
  spread_draws(b_contraception_hormonalyes) %>%
  pivot_longer(cols = c(b_contraception_hormonalyes),
               names_to = "condition",
               values_to = "r_condition") %>%
  mutate(condition_mean = r_condition,
         group = ifelse(condition %contains% "b_contraception_hormonalyes",
                        "Contraception", NA),
         condition = ifelse(condition %contains% "b_contraception_hormonalyes",
                        "Hormonal Contraception", NA)) %>%
  ggplot(aes(y = condition,
             x = condition_mean,
             fill = stat(abs(x) < 0.04))) +
  stat_halfeye() +
  geom_vline(xintercept = c(-0.04, 0.04), linetype = "dotted") +
  apatheme +
  theme(legend.position = "none") +
  scale_fill_manual(values = c("gray80", "skyblue")) +
  labs(x = "Effect Size Estimate", y = "Predictor") +
  xlim (-0.6, 0.6)
```


### Sexual Satisfaction {.tabset}
#### Model
```{r}
m_hc_sexsat = brm(satisfaction_sexual_intercourse ~ contraception_hormonal,
                data = data, family = gaussian(),
                file = "m_hc_sexsat")
```

#### Summary
```{r}
tidy(m_hc_sexsat, intervals = T, prob = 0.95)
summary(m_hc_sexsat)
```

#### Comparison with ROPE
```{r}
plot(equivalence_test(m_hc_sexsat, range = c(-0.11, 0.11)), ci = 0.95)
equivalence_test(m_hc_sexsat, range = c(-0.11, 0.11), ci = 0.95)
```

#### Plots
```{r}
conditional_effects(m_hc_sexsat, ask = FALSE)
```

#### Forest Plot for Effect Sizes {.active}
```{r}
m_hc_sexsat %>%
  spread_draws(b_contraception_hormonalyes) %>%
  pivot_longer(cols = c(b_contraception_hormonalyes),
               names_to = "condition",
               values_to = "r_condition") %>%
  mutate(condition_mean = r_condition,
         group = ifelse(condition %contains% "b_contraception_hormonalyes",
                        "Contraception", NA),
         condition = ifelse(condition %contains% "b_contraception_hormonalyes",
                        "Hormonal Contraception", NA)) %>%
  ggplot(aes(y = condition,
             x = condition_mean,
             fill = stat(abs(x) < 0.11))) +
  stat_halfeye() +
  geom_vline(xintercept = c(-0.11, 0.11), linetype = "dotted") +
  apatheme +
  theme(legend.position = "none") +
  scale_fill_manual(values = c("gray80", "skyblue")) +
  labs(x = "Effect Size Estimate", y = "Predictor") +
  xlim (-0.6, 0.6)
```

### Libido

#### Model
```{r}
m_hc_libido = brm(diary_libido_mean ~ contraception_hormonal,
                data = data, family = gaussian(),
                file = "m_hc_libido")
```

#### Summary
```{r}
tidy(m_hc_libido, intervals = T, prob = 0.95)
summary(m_hc_libido)
```

#### Comparison with ROPE
```{r}
plot(equivalence_test(m_hc_libido, range = c(-0.06, 0.06)), ci = 0.95)
equivalence_test(m_hc_libido, range = c(-0.06, 0.06), ci = 0.95)
```

#### Plots
```{r}
conditional_effects(m_hc_libido, ask = FALSE)
```

#### Forest Plot for Effect Sizes {.active}
```{r}
m_hc_libido %>%
  spread_draws(b_contraception_hormonalyes) %>%
  pivot_longer(cols = c(b_contraception_hormonalyes),
               names_to = "condition",
               values_to = "r_condition") %>%
  mutate(condition_mean = r_condition,
         group = ifelse(condition %contains% "b_contraception_hormonalyes",
                        "Contraception", NA),
         condition = ifelse(condition %contains% "b_contraception_hormonalyes",
                        "Hormonal Contraception", NA)) %>%
  ggplot(aes(y = condition,
             x = condition_mean,
             fill = stat(abs(x) < 0.06))) +
  stat_halfeye() +
  geom_vline(xintercept = c(-0.06, 0.06), linetype = "dotted") +
  apatheme +
  theme(legend.position = "none") +
  scale_fill_manual(values = c("gray80", "skyblue")) +
  labs(x = "Effect Size Estimate", y = "Predictor") +
  xlim (-0.6, 0.6)
```

### Sexual Frequency (Penetrative Intercourse) {.tabset}
#### Model
```{r}
m_hc_sexfreqpen = brm(diary_sex_active_sex_sum ~
                        offset(log(number_of_days)) +
                        contraception_hormonal,
                data = data, family = poisson(),
                file = "m_hc_sexfreqpen")
```

#### Summary
```{r}
tidy(m_hc_sexfreqpen, intervals = T, prob = 0.95)
summary(m_hc_sexfreqpen)
```

#### Comparison with ROPE
```{r}
plot(equivalence_test(m_hc_sexfreqpen, range = c()), ci = 0.95)
equivalence_test(m_hc_sexfreqpen, range = c(-0.71, 0.71), ci = 0.95)
```

#### Plots
```{r}
conditional_effects(m_hc_sexfreqpen, ask = FALSE)
```

#### Forest Plot for Effect Sizes {.active}
```{r}
m_hc_sexfreqpen %>%
  spread_draws(b_contraception_hormonalyes) %>%
  pivot_longer(cols = c(b_contraception_hormonalyes),
               names_to = "condition",
               values_to = "r_condition") %>%
  mutate(condition_mean = r_condition,
         group = ifelse(condition %contains% "b_contraception_hormonalyes",
                        "Contraception", NA),
         condition = ifelse(condition %contains% "b_contraception_hormonalyes",
                        "Hormonal Contraception", NA)) %>%
  ggplot(aes(y = condition,
             x = condition_mean,
             fill = stat(abs(x) < 0.71))) +
  stat_halfeye() +
  geom_vline(xintercept = c(-0.71, 0.71), linetype = "dotted") +
  apatheme +
  theme(legend.position = "none") +
  scale_fill_manual(values = c("gray80", "skyblue")) +
  labs(x = "Effect Size Estimate", y = "Predictor")
```

### Sexual Frequency {.tabset}
#### Model
```{r}
m_hc_sexfreq = brm(diary_sex_active_sum ~ offset(log(number_of_days)) +
                     contraception_hormonal,
                data = data, family = gaussian(),
                file = "m_hc_sexfreq")
```

#### Summary
```{r}
tidy(m_hc_sexfreq, intervals = T, prob = 0.95)
summary(m_hc_sexfreq)
```

#### Comparison with ROPE
```{r}
plot(equivalence_test(m_hc_sexfreq, range = c(-1.12, 1.12)), ci = 0.95)
equivalence_test(m_hc_sexfreq, range = c(-1.12, 1.12), ci = 0.95)
```

#### Plots
```{r}
conditional_effects(m_hc_sexfreq, ask = FALSE)
```

#### Forest Plot for Effect Sizes {.active}
```{r}
m_hc_sexfreq %>%
  spread_draws(b_contraception_hormonalyes) %>%
  pivot_longer(cols = c(b_contraception_hormonalyes),
               names_to = "condition",
               values_to = "r_condition") %>%
  mutate(condition_mean = r_condition,
         group = ifelse(condition %contains% "b_contraception_hormonalyes",
                        "Contraception", NA),
         condition = ifelse(condition %contains% "b_contraception_hormonalyes",
                        "Hormonal Contraception", NA)) %>%
  ggplot(aes(y = condition,
             x = condition_mean,
             fill = stat(abs(x) < 1.12))) +
  stat_halfeye() +
  geom_vline(xintercept = c(-1.12, 1.12), linetype = "dotted") +
  apatheme +
  theme(legend.position = "none") +
  scale_fill_manual(values = c("gray80", "skyblue")) +
  labs(x = "Effect Size Estimate", y = "Predictor")
```

## Effects of (in)congruenct HC use {.tabset}
### Attractiveness of Partner  {.tabset}
#### Model
```{r}
m_congruency_atrr = brm(attractiveness_partner ~
                          contraception_hormonal * congruent_contraception,
                data = data, family = gaussian(),
                file = "m_congruency_atrr")
```

#### Summary
```{r}
tidy(m_congruency_atrr, intervals = T, prob = 0.95)
summary(m_congruency_atrr)
```

#### Comparison with ROPE
```{r}
plot(equivalence_test(m_congruency_atrr, range = c(-0.07, 0.07)), ci = 0.95)
equivalence_test(m_congruency_atrr, range = c(-0.07, 0.07), ci = 0.95)
```

#### Plots
```{r}
conditional_effects(m_congruency_atrr, ask = FALSE)
```

#### Forest Plot for Effect Sizes {.active}
```{r}
m_congruency_atrr %>%
  spread_draws(b_contraception_hormonalyes, b_congruent_contraception1,
               `b_contraception_hormonalyes:congruent_contraception1`) %>%
  pivot_longer(cols = c(b_contraception_hormonalyes, b_congruent_contraception1,
               `b_contraception_hormonalyes:congruent_contraception1`),
               names_to = "condition",
               values_to = "r_condition") %>%
  mutate(condition_mean = r_condition,
         group = ifelse(condition %contains% "ontraception",
                        "Contraception", NA),
         condition = ifelse(condition == "b_contraception_hormonalyes",
                        "Hormonal Contraception",
                     ifelse(condition == "b_congruent_contraception1",
                            "Congruent Contraception",
                     ifelse(condition == "b_contraception_hormonalyes:congruent_contraception1",
                            "Interaction Hormonal Contracpetion and Congruent Contraception",
                            condition))),
         condition = factor(condition, levels = rev(c("Hormonal Contraception",
                                            "Congruent Contraception",
                                            "Interaction Hormonal Contracpetion and Congruent Contraception")))) %>%
  ggplot(aes(y = condition,
             x = condition_mean,
             fill = stat(abs(x) < 0.07))) +
  stat_halfeye() +
  geom_vline(xintercept = c(-0.07, 0.07), linetype = "dotted") +
  apatheme +
  theme(legend.position = "none") +
  scale_fill_manual(values = c("gray80", "skyblue")) +
  labs(x = "Effect Size Estimate", y = "Predictor") +
  xlim (-0.6, 0.6)


  
```

### Relationship Satisfaction {.tabset}
#### Model
```{r}
m_congruency_relsat = brm(relationship_satisfaction ~
                          contraception_hormonal * congruent_contraception,
                data = data, family = gaussian(),
                file = "m_congruency_relsat")
```

#### Summary
```{r}
tidy(m_congruency_relsat, intervals = T, prob = 0.95)
summary(m_congruency_relsat)
```

#### Comparison with ROPE
```{r}
plot(equivalence_test(m_congruency_relsat, range = c(-0.04, 0.04)), ci = 0.95)
equivalence_test(m_congruency_relsat, range = c(-0.04, 0.04), ci = .95)
```

#### Plots
```{r}
conditional_effects(m_congruency_relsat, ask = FALSE)
```

#### Forest Plot for Effect Sizes {.active}
```{r}
m_congruency_relsat %>%
  spread_draws(b_contraception_hormonalyes, b_congruent_contraception1,
               `b_contraception_hormonalyes:congruent_contraception1`) %>%
  pivot_longer(cols = c(b_contraception_hormonalyes, b_congruent_contraception1,
               `b_contraception_hormonalyes:congruent_contraception1`),
               names_to = "condition",
               values_to = "r_condition") %>%
  mutate(condition_mean = r_condition,
         group = ifelse(condition %contains% "ontraception",
                        "Contraception", NA),
         condition = ifelse(condition == "b_contraception_hormonalyes",
                        "Hormonal Contraception",
                     ifelse(condition == "b_congruent_contraception1",
                            "Congruent Contraception",
                     ifelse(condition == "b_contraception_hormonalyes:congruent_contraception1",
                            "Interaction Hormonal Contracpetion and Congruent Contraception",
                            condition))),
         condition = factor(condition, levels = rev(c("Hormonal Contraception",
                                            "Congruent Contraception",
                                            "Interaction Hormonal Contracpetion and Congruent Contraception")))) %>%
  ggplot(aes(y = condition,
             x = condition_mean,
             fill = stat(abs(x) < 0.04))) +
  stat_halfeye() +
  geom_vline(xintercept = c(-0.04, 0.04), linetype = "dotted") +
  apatheme +
  theme(legend.position = "none") +
  scale_fill_manual(values = c("gray80", "skyblue")) +
  labs(x = "Effect Size Estimate", y = "Predictor") +
  xlim (-0.6, 0.6)

```

### Sexual Satisfaction {.tabset}
#### Model
```{r}
m_congruency_sexsat = brm(satisfaction_sexual_intercourse ~
                          contraception_hormonal * congruent_contraception,
                data = data, family = gaussian(),
                file = "m_congruency_sexsat")
```

#### Summary
```{r}
tidy(m_congruency_sexsat, intervals = T, prob = 0.95)
summary(m_congruency_sexsat)
```

#### Comparison with ROPE
```{r}
plot(equivalence_test(m_congruency_sexsat, range = c(-0.11, 0.11)), ci = 0.95)
equivalence_test(m_congruency_sexsat, range = c(-0.11, 0.11), ci = 0.95)
```

#### Plots
```{r}
conditional_effects(m_congruency_sexsat, ask = FALSE)
```

#### Forest Plot for Effect Sizes {.active}
```{r}
m_congruency_sexsat %>%
  spread_draws(b_contraception_hormonalyes, b_congruent_contraception1,
               `b_contraception_hormonalyes:congruent_contraception1`) %>%
  pivot_longer(cols = c(b_contraception_hormonalyes, b_congruent_contraception1,
               `b_contraception_hormonalyes:congruent_contraception1`),
               names_to = "condition",
               values_to = "r_condition") %>%
  mutate(condition_mean = r_condition,
         group = ifelse(condition %contains% "ontraception",
                        "Contraception", NA),
         condition = ifelse(condition == "b_contraception_hormonalyes",
                        "Hormonal Contraception",
                     ifelse(condition == "b_congruent_contraception1",
                            "Congruent Contraception",
                     ifelse(condition == "b_contraception_hormonalyes:congruent_contraception1",
                            "Interaction Hormonal Contracpetion and Congruent Contraception",
                            condition))),
         condition = factor(condition, levels = rev(c("Hormonal Contraception",
                                            "Congruent Contraception",
                                            "Interaction Hormonal Contracpetion and Congruent Contraception")))) %>%
  ggplot(aes(y = condition,
             x = condition_mean,
             fill = stat(abs(x) < 0.11))) +
  stat_halfeye() +
  geom_vline(xintercept = c(-0.11, 0.11), linetype = "dotted") +
  apatheme +
  theme(legend.position = "none") +
  scale_fill_manual(values = c("gray80", "skyblue")) +
  labs(x = "Effect Size Estimate", y = "Predictor") +
  xlim (-0.6, 0.6)
```

### Libido {.tabset}
#### Model
```{r}
m_congruency_libido = brm(diary_libido_mean ~
                          contraception_hormonal * congruent_contraception,
                data = data, family = gaussian(),
                file = "m_congruency_libido")

```

#### Summary
```{r}
tidy(m_congruency_libido, intervals = T, prob = 0.95)
summary(m_congruency_libido)
```

#### Comparison with ROPE
```{r}
plot(equivalence_test(m_congruency_libido, range = c(-0.06, 0.06)), ci = 0.95)
equivalence_test(m_congruency_libido, range = c(-0.06, 0.06), ci = 0.95)
```

#### Plots
```{r}
conditional_effects(m_congruency_libido, ask = FALSE)
```

#### Forest Plot for Effect Sizes {.active}
```{r}
m_congruency_libido %>%
  spread_draws(b_contraception_hormonalyes, b_congruent_contraception1,
               `b_contraception_hormonalyes:congruent_contraception1`) %>%
  pivot_longer(cols = c(b_contraception_hormonalyes, b_congruent_contraception1,
               `b_contraception_hormonalyes:congruent_contraception1`),
               names_to = "condition",
               values_to = "r_condition") %>%
  mutate(condition_mean = r_condition,
         group = ifelse(condition %contains% "ontraception",
                        "Contraception", NA),
         condition = ifelse(condition == "b_contraception_hormonalyes",
                        "Hormonal Contraception",
                     ifelse(condition == "b_congruent_contraception1",
                            "Congruent Contraception",
                     ifelse(condition == "b_contraception_hormonalyes:congruent_contraception1",
                            "Interaction Hormonal Contracpetion and Congruent Contraception",
                            condition))),
         condition = factor(condition, levels = rev(c("Hormonal Contraception",
                                            "Congruent Contraception",
                                            "Interaction Hormonal Contracpetion and Congruent Contraception")))) %>%
  ggplot(aes(y = condition,
             x = condition_mean,
             fill = stat(abs(x) < 0.06))) +
  stat_halfeye() +
  geom_vline(xintercept = c(-0.06, 0.06), linetype = "dotted") +
  apatheme +
  theme(legend.position = "none") +
  scale_fill_manual(values = c("gray80", "skyblue")) +
  labs(x = "Effect Size Estimate", y = "Predictor") +
  xlim (-0.6, 0.6)
```

### Sexual Frequency (Penetrative Intercourse) {.tabset}
#### Model
```{r}
m_congruency_sexfreqpen = brm(diary_sex_active_sex_sum ~ offset(log(number_of_days)) +
                     contraception_hormonal * congruent_contraception,
                data = data, family = gaussian(),
                file = "m_congruency_sexfreqpen")
```

#### Summary
```{r}
tidy(m_congruency_sexfreqpen, intervals = T, prob = 0.95)
summary(m_congruency_sexfreqpen)
```

#### Comparison with ROPE
```{r}
plot(equivalence_test(m_congruency_sexfreqpen, range = c(-0.71, 0.71)), ci = 0.95)
equivalence_test(m_congruency_sexfreqpen, range = c(-0.71, 0.71), ci = 0.95)
```

#### Plots
```{r}
conditional_effects(m_congruency_sexfreqpen, ask = FALSE)
```

#### Forest Plot for Effect Sizes {.active}
```{r}
m_congruency_sexfreqpen %>%
  spread_draws(b_contraception_hormonalyes, b_congruent_contraception1,
               `b_contraception_hormonalyes:congruent_contraception1`) %>%
  pivot_longer(cols = c(b_contraception_hormonalyes, b_congruent_contraception1,
               `b_contraception_hormonalyes:congruent_contraception1`),
               names_to = "condition",
               values_to = "r_condition") %>%
  mutate(condition_mean = r_condition,
         group = ifelse(condition %contains% "ontraception",
                        "Contraception", NA),
         condition = ifelse(condition == "b_contraception_hormonalyes",
                        "Hormonal Contraception",
                     ifelse(condition == "b_congruent_contraception1",
                            "Congruent Contraception",
                     ifelse(condition == "b_contraception_hormonalyes:congruent_contraception1",
                            "Interaction Hormonal Contracpetion and Congruent Contraception",
                            condition))),
         condition = factor(condition, levels = rev(c("Hormonal Contraception",
                                            "Congruent Contraception",
                                            "Interaction Hormonal Contracpetion and Congruent Contraception")))) %>%
  ggplot(aes(y = condition,
             x = condition_mean,
             fill = stat(abs(x) < 0.71))) +
  stat_halfeye() +
  geom_vline(xintercept = c(-0.71, 0.71), linetype = "dotted") +
  apatheme +
  theme(legend.position = "none") +
  scale_fill_manual(values = c("gray80", "skyblue")) +
  labs(x = "Effect Size Estimate", y = "Predictor")
```

### Sexual Frequency {.tabset}
#### Model
```{r}
m_congruency_sexfreq = brm(diary_sex_active_sum ~ offset(log(number_of_days)) +
                             contraception_hormonal * congruent_contraception,
                data = data, family = gaussian(),
                file = "m_congruency_sexfreq")
```

#### Summary
```{r}
tidy(m_congruency_sexfreq, intervals = T, prob = 0.95)
summary(m_congruency_sexfreq)
```

#### Comparison with ROPE
```{r}
plot(equivalence_test(m_congruency_sexfreq, range = c(-1.12, 1.12)), ci = 0.95)
equivalence_test(m_congruency_sexfreq, range = c(-1.12, 1.12), ci = 0.95)
```

#### Plots
```{r}
conditional_effects(m_congruency_sexfreq, ask = FALSE)
```

#### Forest Plot for Effect Sizes {.active}
```{r}
m_congruency_sexfreq %>%
spread_draws(b_contraception_hormonalyes, b_congruent_contraception1,
               `b_contraception_hormonalyes:congruent_contraception1`) %>%
  pivot_longer(cols = c(b_contraception_hormonalyes, b_congruent_contraception1,
               `b_contraception_hormonalyes:congruent_contraception1`),
               names_to = "condition",
               values_to = "r_condition") %>%
  mutate(condition_mean = r_condition,
         group = ifelse(condition %contains% "ontraception",
                        "Contraception", NA),
         condition = ifelse(condition == "b_contraception_hormonalyes",
                        "Hormonal Contraception",
                     ifelse(condition == "b_congruent_contraception1",
                            "Congruent Contraception",
                     ifelse(condition == "b_contraception_hormonalyes:congruent_contraception1",
                            "Interaction Hormonal Contracpetion and Congruent Contraception",
                            condition))),
         condition = factor(condition, levels = rev(c("Hormonal Contraception",
                                            "Congruent Contraception",
                                            "Interaction Hormonal Contracpetion and Congruent Contraception")))) %>%
  ggplot(aes(y = condition,
             x = condition_mean,
             fill = stat(abs(x) < 1.12))) +
  stat_halfeye() +
  geom_vline(xintercept = c(-1.12, 1.12), linetype = "dotted") +
  apatheme +
  theme(legend.position = "none") +
  scale_fill_manual(values = c("gray80", "skyblue")) +
  labs(x = "Effect Size Estimate", y = "Predictor")
```

## Controlloed Models
```{r}
m_hc_atrr_controlled = brm(attractiveness_partner ~ contraception_hormonal +
                             age + net_income + relationship_duration_factor +
                              education_years +
                              bfi_extra + bfi_neuro + bfi_agree + bfi_consc + bfi_open +
                              religiosity,
                data = data, family = gaussian(),
                file = "m_hc_atrr_controlled")

m_hc_relsat_controlled = brm(relationship_satisfaction ~ contraception_hormonal +
                             age + net_income + relationship_duration_factor +
                              education_years +
                              bfi_extra + bfi_neuro + bfi_agree + bfi_consc + bfi_open +
                              religiosity,
                data = data, family = gaussian(),
                file = "m_hc_relsat_controlled")

m_hc_sexsat_controlled = brm(satisfaction_sexual_intercourse ~ contraception_hormonal +
                             age + net_income + relationship_duration_factor +
                              education_years +
                              bfi_extra + bfi_neuro + bfi_agree + bfi_consc + bfi_open +
                              religiosity,
                data = data, family = gaussian(),
                file = "m_hc_sexsat_controlled")

m_hc_libido_controlled = brm(diary_libido_mean ~ contraception_hormonal +
                             age + net_income + relationship_duration_factor +
                              education_years +
                              bfi_extra + bfi_neuro + bfi_agree + bfi_consc + bfi_open +
                              religiosity,
                data = data, family = gaussian(),
                file = "m_hc_libido_controlled")

m_hc_sexfreqpen = brm(diary_sex_active_sex_sum ~
                        offset(log(number_of_days)) +
                        contraception_hormonal +
                        age + net_income + relationship_duration_factor +
                              education_years +
                              bfi_extra + bfi_neuro + bfi_agree + bfi_consc + bfi_open +
                              religiosity,
                data = data, family = poisson(),
                file = "m_hc_sexfreqpen_controlled")

m_hc_sexfreq = brm(diary_sex_active_sum ~
                        offset(log(number_of_days)) +
                        contraception_hormonal +
                        age + net_income + relationship_duration_factor +
                              education_years +
                              bfi_extra + bfi_neuro + bfi_agree + bfi_consc + bfi_open +
                              religiosity,
                data = data, family = poisson(),
                file = "m_hc_sexfreq_controlled")

m_congruency_atrr_controlled = brm(attractiveness_partner ~
                          contraception_hormonal * congruent_contraception +
                             age + net_income + relationship_duration_factor +
                              education_years +
                              bfi_extra + bfi_neuro + bfi_agree + bfi_consc + bfi_open +
                              religiosity,
                data = data, family = gaussian(),
                file = "m_congruency_atrr_controlled")

m_congruency_relsat_controlled = brm(relationship_satisfaction ~
                          contraception_hormonal * congruent_contraception +
                             age + net_income + relationship_duration_factor +
                              education_years +
                              bfi_extra + bfi_neuro + bfi_agree + bfi_consc + bfi_open +
                              religiosity,
                data = data, family = gaussian(),
                file = "m_congruency_relsat_controlled")

m_congruency_sexsat_controlled = brm(satisfaction_sexual_intercourse ~
                          contraception_hormonal * congruent_contraception +
                             age + net_income + relationship_duration_factor +
                              education_years +
                              bfi_extra + bfi_neuro + bfi_agree + bfi_consc + bfi_open +
                              religiosity,
                data = data, family = gaussian(),
                file = "m_congruency_sexsat_controlled")

m_congruency_libido_controlled = brm(diary_libido_mean ~
                          contraception_hormonal * congruent_contraception +
                             age + net_income + relationship_duration_factor +
                              education_years +
                              bfi_extra + bfi_neuro + bfi_agree + bfi_consc + bfi_open +
                              religiosity,
                data = data, family = gaussian(),
                file = "m_congruency_libido_controlled")

m_hc_sexfreqpen = brm(diary_sex_active_sex_sum ~
                        offset(log(number_of_days)) +
                        contraception_hormonal * congruent_contraception +
                        age + net_income + relationship_duration_factor +
                              education_years +
                              bfi_extra + bfi_neuro + bfi_agree + bfi_consc + bfi_open +
                              religiosity,
                data = data, family = poisson(),
                file = "m_hc_sexfreqpen_controlled")

m_hc_sexfreq = brm(diary_sex_active_sum ~
                        offset(log(number_of_days)) +
                        contraception_hormonal * congruent_contraception +
                        age + net_income + relationship_duration_factor +
                              education_years +
                              bfi_extra + bfi_neuro + bfi_agree + bfi_consc + bfi_open +
                              religiosity,
                data = data, family = poisson(),
                file = "m_hc_sexfreq_controlled")

```

