---
title: "Analyses Effects of Contraception"
output:
  html_document:
    toc: true
    toc_depth: 4
    toc_float: true
    code_folding: 'hide'
    self_contained: false
---
  
## Data 
```{r results='hide',message=F,warning=F}
source("0_helpers.R")

load("data/cleaned_selected_wrangled.rdata")
```


## Selection Model {.tabset}
### Hormonal Contraception {.tabset}
#### Simple Model {.tabset}
##### Model
```{r}
m_selection_hc_simple = brm(contraception_hormonal ~
                              age + net_income + relationship_duration_factor,
                            data = data,
                            family = bernoulli("probit"),
                            file = "m_selection_hc_simple")
```

##### Summary
```{r}
kable(tidy(m_selection_hc_simple))
summary(m_selection_hc_simple)
```

##### Plots
```{r}
conditional_effects(m_selection_hc_simple, ask = FALSE)
```

##### Forest Plot for Effect Sizes {.active}
```{r}
m_selection_hc_simple %>%
  tidy() %>%
  filter(term != "b_Intercept",
         term != "lp__") %>%
  mutate(group = ifelse(term %contains% "b_relationship_duration_factor",
                        "Relationship Duration",
                        ifelse(term %contains% "b_net_income",
                               "Income",
                               NA)),
         term = ifelse(term == "b_age", "Age",
                ifelse(term == "b_net_incomeeuro_500_1000", "500-1000 Euro",
                ifelse(term == "b_net_incomeeuro_1000_2000", "1000-2000 Euro",
                ifelse(term == "b_net_incomeeuro_2000_3000", "2000-3000 Euro",
                ifelse(term == "b_net_incomeeuro_gt_3000", ">3000 Euro",
                ifelse(term == "b_net_incomedont_tell", "do not tell",
                ifelse(term == "b_relationship_duration_factorPartnered_upto12months",
                       "0-12 months",
                ifelse(term == "b_relationship_duration_factorPartnered_upto28months",
                       "13-28 months",
                ifelse(term == "b_relationship_duration_factorPartnered_upto52months",
                       "29-52 months",
                ifelse(term == "b_relationship_duration_factorPartnered_morethan52months",
                       ">52 months",
                       term)))))))))),
         group = ifelse(is.na(group), term, group),
         term = factor(term, levels = rev(c("Age",
                                        "500-1000 Euro", "1000-2000 Euro",
                                        "2000-3000 Euro", ">3000 Euro", "do not tell",
                                        "0-12 months", "13-28 months", "29-52 months",
                                        ">52 months")))) %>%
  ggplot(., aes(y = term, x = estimate, xmin = lower, xmax = upper, color = group)) +
  geom_pointinterval() + 
  apatheme +
  theme(legend.title = element_blank()) +
  labs(x = "Effect Size Estimate", y = "Predictor")
```


#### Complex Model {.tabset}
##### Model
```{r}
m_selection_hc_complex = brm(contraception_hormonal ~
                              age + net_income + relationship_duration_factor +
                              education_years +
                              bfi_extra + bfi_neuro + bfi_agree + bfi_consc + bfi_open +
                              religiosity,
                            data = data,
                            family = bernoulli("probit"),
                            file = "m_selection_hc_complex")
```

##### Summary
```{r}
tidy(m_selection_hc_complex)
summary(m_selection_hc_complex)
```

##### Plots
```{r}
conditional_effects(m_selection_hc_complex, ask = FALSE)
```

##### Forest Plot for Effect Sizes {.active}
```{r}
m_selection_hc_complex %>%
  tidy() %>%
  filter(term != "b_Intercept",
         term != "lp__") %>%
  mutate(group = ifelse(term %contains% "b_relationship_duration_factor",
                        "Relationship Duration",
                        ifelse(term %contains% "b_net_income",
                               "Income",
                               NA)),
         term = ifelse(term == "b_age", "Age",
                ifelse(term == "b_net_incomeeuro_500_1000", "500-1000 Euro",
                ifelse(term == "b_net_incomeeuro_1000_2000", "1000-2000 Euro",
                ifelse(term == "b_net_incomeeuro_2000_3000", "2000-3000 Euro",
                ifelse(term == "b_net_incomeeuro_gt_3000", ">3000 Euro",
                ifelse(term == "b_net_incomedont_tell", "do not tell",
                ifelse(term == "b_relationship_duration_factorPartnered_upto12months",
                       "0-12 months",
                ifelse(term == "b_relationship_duration_factorPartnered_upto28months",
                       "13-28 months",
                ifelse(term == "b_relationship_duration_factorPartnered_upto52months",
                       "29-52 months",
                ifelse(term == "b_relationship_duration_factorPartnered_morethan52months",
                       ">52 months",
                ifelse(term == "b_education_years", "Years of Education",
                ifelse(term == "b_bfi_extra", "Extraversion",
                ifelse(term == "b_bfi_neuro", "Neuroticism",
                ifelse(term == "b_bfi_agree", "Agreeableness",
                ifelse(term == "b_bfi_consc", "Conscientiousness",
                ifelse(term == "b_bfi_open", "Openness",
                ifelse(term == "b_religiosity", "Religiosity",
                       term))))))))))))))))),
         group = ifelse(is.na(group), term, group),
         term = factor(term, levels = rev(c("Age",
                                        "500-1000 Euro", "1000-2000 Euro",
                                        "2000-3000 Euro", ">3000 Euro", "do not tell",
                                        "0-12 months", "13-28 months", "29-52 months",
                                        ">52 months",
                                        "Years of Education",
                                        "Extraversion", "Neuroticism", "Agreeableness",
                                         "Conscientiousness","Openness","Religiosity")))) %>%
  ggplot(., aes(y = term, x = estimate, xmin = lower, xmax = upper, color = group)) +
  geom_pointinterval() + 
  apatheme +
  theme(legend.title = element_blank()) +
  labs(x = "Effect Size Estimate", y = "Predictor")
```


#### Comparison {.active}
```{r}
compare_models = loo(m_selection_hc_simple, m_selection_hc_complex)
```
LooIC first model: `r round(compare_models$loos$m_selection_hc_simple$estimates[3,1], 2)`

LooIC second model: `r round(compare_models$loos$m_selection_hc_complex$estimates[3,1], 2)`

Model Comparisons: The difference between models is `r round(compare_models$diffs[2,1], 2)` compared to a standard error of `r round(compare_models$diffs[2,2], 2)`

```{r}
compare_models
```

### (In)congruent use of hormonal contraceptives {.tabset}
#### Simple Model {.tabset}
##### Model
```{r}
m_selection_congruent_simple = brm(congruent_contraception ~
                              age + net_income + relationship_duration_factor,
                            data = data,
                            family = bernoulli("probit"),
                            file = "m_selection_congruent_simple")

m_selection_congruent_simple_includinghc = brm(congruent_contraception ~
                              age + net_income + relationship_duration_factor +
                                contraception_hormonal,
                            data = data,
                            family = bernoulli("probit"),
                            file = "m_selection_congruent_simple_includinghc")
```

##### Summary
```{r}
kable(tidy(m_selection_congruent_simple))
summary(m_selection_congruent_simple)

kable(tidy(m_selection_congruent_simple_includinghc))
summary(m_selection_congruent_simple_includinghc)
```

##### Plots
```{r}
conditional_effects(m_selection_congruent_simple, ask = FALSE)

conditional_effects(m_selection_congruent_simple_includinghc, ask = FALSE)

```

##### Forest Plot for Effect Sizes {.active}
```{r}
m_selection_congruent_simple %>%
  tidy() %>%
  filter(term != "b_Intercept",
         term != "lp__") %>%
  mutate(group = ifelse(term %contains% "b_relationship_duration_factor",
                        "Relationship Duration",
                        ifelse(term %contains% "b_net_income",
                               "Income",
                               NA)),
         term = ifelse(term == "b_age", "Age",
                ifelse(term == "b_net_incomeeuro_500_1000", "500-1000 Euro",
                ifelse(term == "b_net_incomeeuro_1000_2000", "1000-2000 Euro",
                ifelse(term == "b_net_incomeeuro_2000_3000", "2000-3000 Euro",
                ifelse(term == "b_net_incomeeuro_gt_3000", ">3000 Euro",
                ifelse(term == "b_net_incomedont_tell", "do not tell",
                ifelse(term == "b_relationship_duration_factorPartnered_upto12months",
                       "0-12 months",
                ifelse(term == "b_relationship_duration_factorPartnered_upto28months",
                       "13-28 months",
                ifelse(term == "b_relationship_duration_factorPartnered_upto52months",
                       "29-52 months",
                ifelse(term == "b_relationship_duration_factorPartnered_morethan52months",
                       ">52 months",
                       term)))))))))),
         group = ifelse(is.na(group), term, group),
         term = factor(term, levels = rev(c("Age",
                                        "500-1000 Euro", "1000-2000 Euro",
                                        "2000-3000 Euro", ">3000 Euro", "do not tell",
                                        "0-12 months", "13-28 months", "29-52 months",
                                        ">52 months")))) %>%
  ggplot(., aes(y = term, x = estimate, xmin = lower, xmax = upper, color = group)) +
  geom_pointinterval() + 
  apatheme +
  theme(legend.title = element_blank()) +
  labs(x = "Effect Size Estimate", y = "Predictor")

m_selection_congruent_simple_includinghc %>%
  tidy() %>%
  filter(term != "b_Intercept",
         term != "lp__") %>%
  mutate(group = ifelse(term %contains% "b_relationship_duration_factor",
                        "Relationship Duration",
                        ifelse(term %contains% "b_net_income",
                               "Income",
                               NA)),
         term = ifelse(term == "b_age", "Age",
                ifelse(term == "b_net_incomeeuro_500_1000", "500-1000 Euro",
                ifelse(term == "b_net_incomeeuro_1000_2000", "1000-2000 Euro",
                ifelse(term == "b_net_incomeeuro_2000_3000", "2000-3000 Euro",
                ifelse(term == "b_net_incomeeuro_gt_3000", ">3000 Euro",
                ifelse(term == "b_net_incomedont_tell", "do not tell",
                ifelse(term == "b_relationship_duration_factorPartnered_upto12months",
                       "0-12 months",
                ifelse(term == "b_relationship_duration_factorPartnered_upto28months",
                       "13-28 months",
                ifelse(term == "b_relationship_duration_factorPartnered_upto52months",
                       "29-52 months",
                ifelse(term == "b_relationship_duration_factorPartnered_morethan52months",
                       ">52 months",
                ifelse(term == "b_contraception_hormonalyes",
                       "Currently Using HCs",
                       term))))))))))),
         group = ifelse(is.na(group), term, group),
         term = factor(term, levels = rev(c("Age",
                                        "500-1000 Euro", "1000-2000 Euro",
                                        "2000-3000 Euro", ">3000 Euro", "do not tell",
                                        "0-12 months", "13-28 months", "29-52 months",
                                        ">52 months",
                                        "Currently Using HCs")))) %>%
  ggplot(., aes(y = term, x = estimate, xmin = lower, xmax = upper, color = group)) +
  geom_pointinterval() + 
  apatheme +
  theme(legend.title = element_blank()) +
  labs(x = "Effect Size Estimate", y = "Predictor")
```


#### Complex Model {.tabset}
##### Model
```{r}
m_selection_congruent_complex = brm(congruent_contraception ~
                              age + net_income + relationship_duration_factor +
                              education_years +
                              bfi_extra + bfi_neuro + bfi_agree + bfi_consc + bfi_open +
                              religiosity,
                            data = data,
                            family = bernoulli("probit"),
                            file = "m_selection_congruent_complex")

m_selection_congruent_complex_includinghc = brm(congruent_contraception ~
                              age + net_income + relationship_duration_factor  +
                                contraception_hormonal +
                                education_years +
                              bfi_extra + bfi_neuro + bfi_agree + bfi_consc + bfi_open +
                              religiosity,
                            data = data,
                            family = bernoulli("probit"),
                            file = "m_selection_congruent_complex_includinghc")
```

##### Summary
```{r}
tidy(m_selection_congruent_complex)
summary(m_selection_congruent_complex)

tidy(m_selection_congruent_complex_includinghc)
summary(m_selection_congruent_complex_includinghc)
```

##### Plots
```{r}
conditional_effects(m_selection_congruent_complex, ask = FALSE)
conditional_effects(m_selection_congruent_complex_includinghc, ask = FALSE)
```

##### Forest Plot for Effect Sizes {.active}
```{r}
m_selection_congruent_complex %>%
  tidy() %>%
  filter(term != "b_Intercept",
         term != "lp__") %>%
  mutate(group = ifelse(term %contains% "b_relationship_duration_factor",
                        "Relationship Duration",
                        ifelse(term %contains% "b_net_income",
                               "Income",
                               NA)),
         term = ifelse(term == "b_age", "Age",
                ifelse(term == "b_net_incomeeuro_500_1000", "500-1000 Euro",
                ifelse(term == "b_net_incomeeuro_1000_2000", "1000-2000 Euro",
                ifelse(term == "b_net_incomeeuro_2000_3000", "2000-3000 Euro",
                ifelse(term == "b_net_incomeeuro_gt_3000", ">3000 Euro",
                ifelse(term == "b_net_incomedont_tell", "do not tell",
                ifelse(term == "b_relationship_duration_factorPartnered_upto12months",
                       "0-12 months",
                ifelse(term == "b_relationship_duration_factorPartnered_upto28months",
                       "13-28 months",
                ifelse(term == "b_relationship_duration_factorPartnered_upto52months",
                       "29-52 months",
                ifelse(term == "b_relationship_duration_factorPartnered_morethan52months",
                       ">52 months",
                ifelse(term == "b_education_years", "Years of Education",
                ifelse(term == "b_bfi_extra", "Extraversion",
                ifelse(term == "b_bfi_neuro", "Neuroticism",
                ifelse(term == "b_bfi_agree", "Agreeableness",
                ifelse(term == "b_bfi_consc", "Conscientiousness",
                ifelse(term == "b_bfi_open", "Openness",
                ifelse(term == "b_religiosity", "Religiosity",
                       term))))))))))))))))),
         group = ifelse(is.na(group), term, group),
         term = factor(term, levels = rev(c("Age",
                                        "500-1000 Euro", "1000-2000 Euro",
                                        "2000-3000 Euro", ">3000 Euro", "do not tell",
                                        "0-12 months", "13-28 months", "29-52 months",
                                        ">52 months",
                                        "Years of Education",
                                        "Extraversion", "Neuroticism", "Agreeableness",
                                         "Conscientiousness","Openness","Religiosity")))) %>%
  ggplot(., aes(y = term, x = estimate, xmin = lower, xmax = upper, color = group)) +
  geom_pointinterval() + 
  apatheme +
  theme(legend.title = element_blank()) +
  labs(x = "Effect Size Estimate", y = "Predictor")


m_selection_congruent_complex_includinghc %>%
  tidy() %>%
  filter(term != "b_Intercept",
         term != "lp__") %>%
  mutate(group = ifelse(term %contains% "b_relationship_duration_factor",
                        "Relationship Duration",
                        ifelse(term %contains% "b_net_income",
                               "Income",
                               NA)),
         term = ifelse(term == "b_age", "Age",
                ifelse(term == "b_net_incomeeuro_500_1000", "500-1000 Euro",
                ifelse(term == "b_net_incomeeuro_1000_2000", "1000-2000 Euro",
                ifelse(term == "b_net_incomeeuro_2000_3000", "2000-3000 Euro",
                ifelse(term == "b_net_incomeeuro_gt_3000", ">3000 Euro",
                ifelse(term == "b_net_incomedont_tell", "do not tell",
                ifelse(term == "b_relationship_duration_factorPartnered_upto12months",
                       "0-12 months",
                ifelse(term == "b_relationship_duration_factorPartnered_upto28months",
                       "13-28 months",
                ifelse(term == "b_relationship_duration_factorPartnered_upto52months",
                       "29-52 months",
                ifelse(term == "b_relationship_duration_factorPartnered_morethan52months",
                       ">52 months",
                ifelse(term == "b_contraception_hormonalyes",
                       "Currently Using HCs",
                ifelse(term == "b_education_years", "Years of Education",
                ifelse(term == "b_bfi_extra", "Extraversion",
                ifelse(term == "b_bfi_neuro", "Neuroticism",
                ifelse(term == "b_bfi_agree", "Agreeableness",
                ifelse(term == "b_bfi_consc", "Conscientiousness",
                ifelse(term == "b_bfi_open", "Openness",
                ifelse(term == "b_religiosity", "Religiosity",
                       term)))))))))))))))))),
         group = ifelse(is.na(group), term, group),
         term = factor(term, levels = rev(c("Age",
                                        "500-1000 Euro", "1000-2000 Euro",
                                        "2000-3000 Euro", ">3000 Euro", "do not tell",
                                        "0-12 months", "13-28 months", "29-52 months",
                                        ">52 months",
                                        "Currently Using HCs",
                                        "Years of Education",
                                        "Extraversion", "Neuroticism", "Agreeableness",
                                         "Conscientiousness","Openness","Religiosity")))) %>%
  ggplot(., aes(y = term, x = estimate, xmin = lower, xmax = upper, color = group)) +
  geom_pointinterval() + 
  apatheme +
  theme(legend.title = element_blank()) +
  labs(x = "Effect Size Estimate", y = "Predictor")
```


#### Comparison {.active}
```{r}
compare_models = loo(m_selection_congruent_simple, m_selection_congruent_complex)
```
LooIC first model: `r round(compare_models$loos$m_selection_congruent_simple$estimates[3,1], 2)`

LooIC second model: `r round(compare_models$loos$m_selection_congruent_complex$estimates[3,1], 2)`

Model Comparisons: The difference between models is `r round(compare_models$diffs[2,1], 2)` compared to a standard error of `r round(compare_models$diffs[2,2], 2)`

```{r}
compare_models
```

## Effects of Hormonl Contraceptives {.tabset}
### Attractiveness of Partner {.tabset}
#### Model
```{r}
m_hc_atrr = brm(attractiveness_partner ~ contraception_hormonal,
                data = data, family = gaussian(),
                file = "m_hc_atrr")
```

##### Summary
```{r}
tidy(m_hc_atrr)
summary(m_hc_atrr)
```

##### Comparison with ROPE
```{r}
equivalence_test(m_hc_atrr, range = c(-0.07, 0.07))
```

##### Plots
```{r}
conditional_effects(m_hc_atrr, ask = FALSE)
```

##### Forest Plot for Effect Sizes {.active}
```{r}
m_hc_atrr %>%
  tidy() %>%
  filter(term != "b_Intercept",
         term != "lp__",
         term != "sigma") %>%
  mutate(term = ifelse(term == "b_contraception_hormonalyes", "Hormonal Contraception",
                        term),
         group = ifelse(term == "b_contraception_hormonalyes", "Contraception",
                        term),
    group = ifelse(is.na(group), term, group)) %>%
  ggplot(., aes(y = term, x = estimate, xmin = lower, xmax = upper, color = group)) +
  geom_pointinterval() + 
  geom_vline(xintercept = -0.07, linetype = "dotted") +
  geom_vline(xintercept = 0.07, linetype = "dotted") +
  apatheme +
  theme(legend.title = element_blank()) +
  labs(x = "Effect Size Estimate", y = "Predictor")
```

### Relationship Satisfaction {.tabset}
#### Model
```{r}
m_hc_relsat = brm(relationship_satisfaction ~ contraception_hormonal,
                data = data, family = gaussian(),
                file = "m_hc_relsat")
```

##### Summary
```{r}
tidy(m_hc_relsat)
summary(m_hc_relsat)
```

##### Comparison with ROPE
```{r}
equivalence_test(m_hc_relsat, range = c(-0.04, 0.04))
```

##### Plots
```{r}
conditional_effects(m_hc_relsat, ask = FALSE)
```

##### Forest Plot for Effect Sizes {.active}
```{r}
m_hc_relsat %>%
  tidy() %>%
  filter(term != "b_Intercept",
         term != "lp__",
         term != "sigma") %>%
  mutate(term = ifelse(term == "b_contraception_hormonalyes", "Hormonal Contraception",
                        term),
         group = ifelse(term == "b_contraception_hormonalyes", "Contraception",
                        term),
    group = ifelse(is.na(group), term, group)) %>%
  ggplot(., aes(y = term, x = estimate, xmin = lower, xmax = upper, color = group)) +
  geom_pointinterval() + 
  geom_vline(xintercept = -0.04, linetype = "dotted") +
  geom_vline(xintercept = 0.04, linetype = "dotted") +
  apatheme +
  theme(legend.title = element_blank()) +
  labs(x = "Effect Size Estimate", y = "Predictor")
```


### Sexual Satisfaction {.tabset}
#### Model
```{r}
m_hc_sexsat = brm(satisfaction_sexual_intercourse ~ contraception_hormonal,
                data = data, family = gaussian(),
                file = "m_hc_sexsat")
```

##### Summary
```{r}
tidy(m_hc_sexsat)
summary(m_hc_sexsat)
```

##### Comparison with ROPE
```{r}
equivalence_test(m_hc_sexsat, range = c(-0.11, 0.11))
```

##### Plots
```{r}
conditional_effects(m_hc_sexsat, ask = FALSE)
```

##### Forest Plot for Effect Sizes {.active}
```{r}
m_hc_sexsat %>%
  tidy() %>%
  filter(term != "b_Intercept",
         term != "lp__",
         term != "sigma") %>%
  mutate(term = ifelse(term == "b_contraception_hormonalyes", "Hormonal Contraception",
                        term),
         group = ifelse(term == "b_contraception_hormonalyes", "Contraception",
                        term),
    group = ifelse(is.na(group), term, group)) %>%
  ggplot(., aes(y = term, x = estimate, xmin = lower, xmax = upper, color = group)) +
  geom_pointinterval() + 
  geom_vline(xintercept = -0.11, linetype = "dotted") +
  geom_vline(xintercept = 0.11, linetype = "dotted") +
  apatheme +
  theme(legend.title = element_blank()) +
  labs(x = "Effect Size Estimate", y = "Predictor")
```

### Libido

#### Model
```{r}
m_hc_libido = brm(diary_libido_mean ~ contraception_hormonal,
                data = data, family = gaussian(),
                file = "m_hc_libido")
```

##### Summary
```{r}
tidy(m_hc_libido)
summary(m_hc_libido)
```

##### Comparison with ROPE
```{r}
equivalence_test(m_hc_libido, range = c(-0.06, 0.06))
```

##### Plots
```{r}
conditional_effects(m_hc_libido, ask = FALSE)
```

##### Forest Plot for Effect Sizes {.active}
```{r}
m_hc_libido %>%
  tidy() %>%
  filter(term != "b_Intercept",
         term != "lp__",
         term != "sigma") %>%
  mutate(term = ifelse(term == "b_contraception_hormonalyes", "Hormonal Contraception",
                        term),
         group = ifelse(term == "b_contraception_hormonalyes", "Contraception",
                        term),
    group = ifelse(is.na(group), term, group)) %>%
  ggplot(., aes(y = term, x = estimate, xmin = lower, xmax = upper, color = group)) +
  geom_pointinterval() + 
  geom_vline(xintercept = -0.06, linetype = "dotted") +
  geom_vline(xintercept = 0.06, linetype = "dotted") +
  apatheme +
  theme(legend.title = element_blank()) +
  labs(x = "Effect Size Estimate", y = "Predictor")
```

### Sexual Frequency (Penetrative Intercourse) {.tabset}
#### Model
```{r}
m_hc_sexfreqpen = brm(diary_sex_active_sex_mean ~ contraception_hormonal,
                data = data, family = gaussian(),
                file = "m_hc_sexfreqpen")
```

##### Summary
```{r}
tidy(m_hc_sexfreqpen)
summary(m_hc_sexfreqpen)
```

##### Comparison with ROPE
```{r}
equivalence_test(m_hc_sexfreqpen, range = c(-0.01, 0.01))
```

##### Plots
```{r}
conditional_effects(m_hc_sexfreqpen, ask = FALSE)
```

##### Forest Plot for Effect Sizes {.active}
```{r}
m_hc_sexfreqpen %>%
  tidy() %>%
  filter(term != "b_Intercept",
         term != "lp__",
         term != "sigma") %>%
  mutate(term = ifelse(term == "b_contraception_hormonalyes", "Hormonal Contraception",
                        term),
         group = ifelse(term == "b_contraception_hormonalyes", "Contraception",
                        term),
    group = ifelse(is.na(group), term, group)) %>%
  ggplot(., aes(y = term, x = estimate, xmin = lower, xmax = upper, color = group)) +
  geom_pointinterval() + 
  geom_vline(xintercept = -0.01, linetype = "dotted") +
  geom_vline(xintercept = 0.01, linetype = "dotted") +
  apatheme +
  theme(legend.title = element_blank()) +
  labs(x = "Effect Size Estimate", y = "Predictor")
```

### Sexual Frequency {.tabset}

#### Model
```{r}
m_hc_sexfreq = brm(diary_sex_active_mean ~ contraception_hormonal,
                data = data, family = gaussian(),
                file = "m_hc_sexfreq")
```

##### Summary
```{r}
tidy(m_hc_sexfreq)
summary(m_hc_sexfreq)
```

##### Comparison with ROPE
```{r}
equivalence_test(m_hc_sexfreq, range = c(-0.02, 0.02))
```

##### Plots
```{r}
conditional_effects(m_hc_sexfreq, ask = FALSE)
```

##### Forest Plot for Effect Sizes {.active}
```{r}
m_hc_sexfreq %>%
  tidy() %>%
  filter(term != "b_Intercept",
         term != "lp__",
         term != "sigma") %>%
  mutate(term = ifelse(term == "b_contraception_hormonalyes", "Hormonal Contraception",
                        term),
         group = ifelse(term == "b_contraception_hormonalyes", "Contraception",
                        term),
    group = ifelse(is.na(group), term, group)) %>%
  ggplot(., aes(y = term, x = estimate, xmin = lower, xmax = upper, color = group)) +
  geom_pointinterval() + 
  geom_vline(xintercept = -0.02, linetype = "dotted") +
  geom_vline(xintercept = 0.02, linetype = "dotted") +
  apatheme +
  theme(legend.title = element_blank()) +
  labs(x = "Effect Size Estimate", y = "Predictor")
```

## Effects of (in)congruenct HC use {.tabset}
### Attractiveness of Partner  {.tabset}
#### Model
```{r}
m_congruency_atrr = brm(attractiveness_partner ~
                          contraception_hormonal * congruent_contraception,
                data = data, family = gaussian(),
                file = "m_congruency_atrr")
```

##### Summary
```{r}
tidy(m_congruency_atrr)
summary(m_congruency_atrr)
```

##### Comparison with ROPE
```{r}
equivalence_test(m_congruency_atrr, range = c(-0.07, 0.07))
```

##### Plots
```{r}
conditional_effects(m_congruency_atrr, ask = FALSE)
```

##### Forest Plot for Effect Sizes {.active}
```{r}
m_congruency_atrr %>%
  tidy() %>%
  filter(term != "b_Intercept",
         term != "lp__",
         term != "sigma") %>%
  mutate(term = ifelse(term == "b_contraception_hormonalyes", "Hormonal Contraception",
                ifelse(term == "b_congruent_contraception1", "Congruent Contraception",
                ifelse(term == "b_contraception_hormonalyes:congruent_contraception1",
                       "Interaction Hormonal Contracpetion and Congruent Contraception",
                       term))),
         group = ifelse(term %contains% "ontraception", "Contraception",
                        term),
         group = ifelse(is.na(group), term, group),
         term = factor(term, levels = rev(c("Hormonal Contraception",
                                            "Congruent Contraception",
                                            "Interaction Hormonal Contracpetion and Congruent Contraception")))) %>%
  ggplot(., aes(y = term, x = estimate, xmin = lower, xmax = upper, color = group)) +
  geom_pointinterval() + 
  geom_vline(xintercept = -0.07, linetype = "dotted") +
  geom_vline(xintercept = 0.07, linetype = "dotted") +
  apatheme +
  theme(legend.title = element_blank()) +
  labs(x = "Effect Size Estimate", y = "Predictor")
```

### Relationship Satisfaction {.tabset}
#### Model
```{r}
m_congruency_relsat = brm(relationship_satisfaction ~
                          contraception_hormonal * congruent_contraception,
                data = data, family = gaussian(),
                file = "m_congruency_relsat")
```

##### Summary
```{r}
tidy(m_congruency_relsat)
summary(m_congruency_relsat)
```

##### Comparison with ROPE
```{r}
equivalence_test(m_congruency_relsat, range = c(-0.04, 0.04))
```

##### Plots
```{r}
conditional_effects(m_congruency_relsat, ask = FALSE)
```

##### Forest Plot for Effect Sizes {.active}
```{r}
m_congruency_relsat %>%
  tidy() %>%
  filter(term != "b_Intercept",
         term != "lp__",
         term != "sigma") %>%
  mutate(term = ifelse(term == "b_contraception_hormonalyes", "Hormonal Contraception",
                ifelse(term == "b_congruent_contraception1", "Congruent Contraception",
                ifelse(term == "b_contraception_hormonalyes:congruent_contraception1",
                       "Interaction Hormonal Contracpetion and Congruent Contraception",
                       term))),
         group = ifelse(term %contains% "ontraception", "Contraception",
                        term),
         group = ifelse(is.na(group), term, group),
         term = factor(term, levels = rev(c("Hormonal Contraception",
                                            "Congruent Contraception",
                                            "Interaction Hormonal Contracpetion and Congruent Contraception")))) %>%
  ggplot(., aes(y = term, x = estimate, xmin = lower, xmax = upper, color = group)) +
  geom_pointinterval() + 
  geom_vline(xintercept = -0.04, linetype = "dotted") +
  geom_vline(xintercept = 0.04, linetype = "dotted") +
  apatheme +
  theme(legend.title = element_blank()) +
  labs(x = "Effect Size Estimate", y = "Predictor")
```

### Sexual Satisfaction {.tabset}
#### Model
```{r}
m_congruency_sexsat = brm(satisfaction_sexual_intercourse ~
                          contraception_hormonal * congruent_contraception,
                data = data, family = gaussian(),
                file = "m_congruency_sexsat")
```

##### Summary
```{r}
tidy(m_congruency_sexsat)
summary(m_congruency_sexsat)
```

##### Comparison with ROPE
```{r}
equivalence_test(m_congruency_sexsat, range = c(-0.11, 0.11))
```

##### Plots
```{r}
conditional_effects(m_congruency_sexsat, ask = FALSE)
```

##### Forest Plot for Effect Sizes {.active}
```{r}
m_congruency_sexsat %>%
  tidy() %>%
  filter(term != "b_Intercept",
         term != "lp__",
         term != "sigma") %>%
  mutate(term = ifelse(term == "b_contraception_hormonalyes", "Hormonal Contraception",
                ifelse(term == "b_congruent_contraception1", "Congruent Contraception",
                ifelse(term == "b_contraception_hormonalyes:congruent_contraception1",
                       "Interaction Hormonal Contracpetion and Congruent Contraception",
                       term))),
         group = ifelse(term %contains% "ontraception", "Contraception",
                        term),
         group = ifelse(is.na(group), term, group),
         term = factor(term, levels = rev(c("Hormonal Contraception",
                                            "Congruent Contraception",
                                            "Interaction Hormonal Contracpetion and Congruent Contraception")))) %>%
  ggplot(., aes(y = term, x = estimate, xmin = lower, xmax = upper, color = group)) +
  geom_pointinterval() + 
  geom_vline(xintercept = -0.11, linetype = "dotted") +
  geom_vline(xintercept = 0.11, linetype = "dotted") +
  apatheme +
  theme(legend.title = element_blank()) +
  labs(x = "Effect Size Estimate", y = "Predictor")
```

### Libido {.tabset}
#### Model
```{r}
m_congruency_libido = brm(diary_libido_mean ~
                          contraception_hormonal * congruent_contraception,
                data = data, family = gaussian(),
                file = "m_congruency_libido")

```

##### Summary
```{r}
tidy(m_congruency_libido)
summary(m_congruency_libido)
```

##### Comparison with ROPE
```{r}
equivalence_test(m_congruency_libido, range = c(-0.06, 0.06))
```

##### Plots
```{r}
conditional_effects(m_congruency_libido, ask = FALSE)
```

##### Forest Plot for Effect Sizes {.active}
```{r}
m_congruency_libido %>%
  tidy() %>%
  filter(term != "b_Intercept",
         term != "lp__",
         term != "sigma") %>%
  mutate(term = ifelse(term == "b_contraception_hormonalyes", "Hormonal Contraception",
                ifelse(term == "b_congruent_contraception1", "Congruent Contraception",
                ifelse(term == "b_contraception_hormonalyes:congruent_contraception1",
                       "Interaction Hormonal Contracpetion and Congruent Contraception",
                       term))),
         group = ifelse(term %contains% "ontraception", "Contraception",
                        term),
         group = ifelse(is.na(group), term, group),
         term = factor(term, levels = rev(c("Hormonal Contraception",
                                            "Congruent Contraception",
                                            "Interaction Hormonal Contracpetion and Congruent Contraception")))) %>%
  ggplot(., aes(y = term, x = estimate, xmin = lower, xmax = upper, color = group)) +
  geom_pointinterval() + 
  geom_vline(xintercept = -0.06, linetype = "dotted") +
  geom_vline(xintercept = 0.06, linetype = "dotted") +
  apatheme +
  theme(legend.title = element_blank()) +
  labs(x = "Effect Size Estimate", y = "Predictor")
```

### Sexual Frequency (Penetrative Intercourse) {.tabset}
#### Model
```{r}
m_congruency_sexfreqpen = brm(diary_sex_active_sex_mean ~
                          contraception_hormonal * congruent_contraception,
                data = data, family = gaussian(),
                file = "m_congruency_sexfreqpen")
```

##### Summary
```{r}
tidy(m_congruency_sexfreqpen)
summary(m_congruency_sexfreqpen)
```

##### Comparison with ROPE
```{r}
equivalence_test(m_congruency_sexfreqpen, range = c(-0.01, 0.01))
```

##### Plots
```{r}
conditional_effects(m_congruency_sexfreqpen, ask = FALSE)
```

##### Forest Plot for Effect Sizes {.active}
```{r}
m_congruency_sexfreqpen %>%
  tidy() %>%
  filter(term != "b_Intercept",
         term != "lp__",
         term != "sigma") %>%
  mutate(term = ifelse(term == "b_contraception_hormonalyes", "Hormonal Contraception",
                ifelse(term == "b_congruent_contraception1", "Congruent Contraception",
                ifelse(term == "b_contraception_hormonalyes:congruent_contraception1",
                       "Interaction Hormonal Contracpetion and Congruent Contraception",
                       term))),
         group = ifelse(term %contains% "ontraception", "Contraception",
                        term),
         group = ifelse(is.na(group), term, group),
         term = factor(term, levels = rev(c("Hormonal Contraception",
                                            "Congruent Contraception",
                                            "Interaction Hormonal Contracpetion and Congruent Contraception")))) %>%
  ggplot(., aes(y = term, x = estimate, xmin = lower, xmax = upper, color = group)) +
  geom_pointinterval() + 
  geom_vline(xintercept = -0.01, linetype = "dotted") +
  geom_vline(xintercept = 0.01, linetype = "dotted") +
  apatheme +
  theme(legend.title = element_blank()) +
  labs(x = "Effect Size Estimate", y = "Predictor")
```

#### Sexual Freguency {.tabset}
#### Model
```{r}
m_congruency_sexfreq = brm(diary_sex_active_mean ~
                          contraception_hormonal * congruent_contraception,
                data = data, family = gaussian(),
                file = "m_congruency_sexfreq")
```

##### Summary
```{r}
tidy(m_congruency_sexfreq)
summary(m_congruency_sexfreq)
```

##### Comparison with ROPE
```{r}
equivalence_test(m_congruency_sexfreq, range = c(-0.02, 0.02))
```

##### Plots
```{r}
conditional_effects(m_congruency_sexfreq, ask = FALSE)
```

##### Forest Plot for Effect Sizes {.active}
```{r}
m_congruency_sexfreq %>%
  tidy() %>%
  filter(term != "b_Intercept",
         term != "lp__",
         term != "sigma") %>%
  mutate(term = ifelse(term == "b_contraception_hormonalyes", "Hormonal Contraception",
                ifelse(term == "b_congruent_contraception1", "Congruent Contraception",
                ifelse(term == "b_contraception_hormonalyes:congruent_contraception1",
                       "Interaction Hormonal Contracpetion and Congruent Contraception",
                       term))),
         group = ifelse(term %contains% "ontraception", "Contraception",
                        term),
         group = ifelse(is.na(group), term, group),
         term = factor(term, levels = rev(c("Hormonal Contraception",
                                            "Congruent Contraception",
                                            "Interaction Hormonal Contracpetion and Congruent Contraception")))) %>%
  ggplot(., aes(y = term, x = estimate, xmin = lower, xmax = upper, color = group)) +
  geom_pointinterval() + 
  geom_vline(xintercept = -0.02, linetype = "dotted") +
  geom_vline(xintercept = 0.02, linetype = "dotted") +
  apatheme +
  theme(legend.title = element_blank()) +
  labs(x = "Effect Size Estimate", y = "Predictor")
```

## Controlloed Models
```{r}
m_hc_atrr_controlled = brm(attractiveness_partner ~ contraception_hormonal +
                             age + net_income + relationship_duration_factor +
                              education_years +
                              bfi_extra + bfi_neuro + bfi_agree + bfi_consc + bfi_open +
                              religiosity,
                data = data, family = gaussian(),
                file = "m_hc_atrr_controlled")

m_hc_relsat_controlled = brm(relationship_satisfaction ~ contraception_hormonal +
                             age + net_income + relationship_duration_factor +
                              education_years +
                              bfi_extra + bfi_neuro + bfi_agree + bfi_consc + bfi_open +
                              religiosity,
                data = data, family = gaussian(),
                file = "m_hc_relsat_controlled")

m_hc_sexsat_controlled = brm(satisfaction_sexual_intercourse ~ contraception_hormonal +
                             age + net_income + relationship_duration_factor +
                              education_years +
                              bfi_extra + bfi_neuro + bfi_agree + bfi_consc + bfi_open +
                              religiosity,
                data = data, family = gaussian(),
                file = "m_hc_sexsat_controlled")

m_hc_libido_controlled = brm(diary_libido_mean ~ contraception_hormonal +
                             age + net_income + relationship_duration_factor +
                              education_years +
                              bfi_extra + bfi_neuro + bfi_agree + bfi_consc + bfi_open +
                              religiosity,
                data = data, family = gaussian(),
                file = "m_hc_libido")

m_hc_sexfreq_controlled = brm(diary_sex_active_mean ~ contraception_hormonal +
                             age + net_income + relationship_duration_factor +
                              education_years +
                              bfi_extra + bfi_neuro + bfi_agree + bfi_consc + bfi_open +
                              religiosity,
                data = data, family = gaussian(),
                file = "m_hc_sexfreq_controlled")

m_hc_sexfreqpen_controlled = brm(diary_sex_active_sex_mean ~ contraception_hormonal +
                             age + net_income + relationship_duration_factor +
                              education_years +
                              bfi_extra + bfi_neuro + bfi_agree + bfi_consc + bfi_open +
                              religiosity,
                data = data, family = gaussian(),
                file = "m_hc_sexfreqpen_controlled")

m_congruency_atrr_controlled = brm(attractiveness_partner ~
                          contraception_hormonal * congruent_contraception +
                             age + net_income + relationship_duration_factor +
                              education_years +
                              bfi_extra + bfi_neuro + bfi_agree + bfi_consc + bfi_open +
                              religiosity,
                data = data, family = gaussian(),
                file = "m_congruency_atrr_controlled")

m_congruency_relsat_controlled = brm(relationship_satisfaction ~
                          contraception_hormonal * congruent_contraception +
                             age + net_income + relationship_duration_factor +
                              education_years +
                              bfi_extra + bfi_neuro + bfi_agree + bfi_consc + bfi_open +
                              religiosity,
                data = data, family = gaussian(),
                file = "m_congruency_relsat_controlled")

m_congruency_sexsat_controlled = brm(satisfaction_sexual_intercourse ~
                          contraception_hormonal * congruent_contraception +
                             age + net_income + relationship_duration_factor +
                              education_years +
                              bfi_extra + bfi_neuro + bfi_agree + bfi_consc + bfi_open +
                              religiosity,
                data = data, family = gaussian(),
                file = "m_congruency_sexsat_controlled")

m_congruency_libido_controlled = brm(diary_libido_mean ~
                          contraception_hormonal * congruent_contraception +
                             age + net_income + relationship_duration_factor +
                              education_years +
                              bfi_extra + bfi_neuro + bfi_agree + bfi_consc + bfi_open +
                              religiosity,
                data = data, family = gaussian(),
                file = "m_congruency_libido_controlled")

m_congruency_sexfreq_controlled = brm(diary_sex_active_mean ~
                          contraception_hormonal * congruent_contraception +
                             age + net_income + relationship_duration_factor +
                              education_years +
                              bfi_extra + bfi_neuro + bfi_agree + bfi_consc + bfi_open +
                              religiosity,
                data = data, family = gaussian(),
                file = "m_congruency_sexfreq_controlled")

m_congruency_sexfreqpen_controlled = brm(diary_sex_active_sex_mean ~
                          contraception_hormonal * congruent_contraception +
                             age + net_income + relationship_duration_factor +
                              education_years +
                              bfi_extra + bfi_neuro + bfi_agree + bfi_consc + bfi_open +
                              religiosity,
                data = data, family = gaussian(),
                file = "m_congruency_sexfreqpen_controlled")

```

