
# Datawrangling {.tabset}

## Data and Functions
```{r data and function, results='hide',message=F,warning=F}
source("0_helpers.R")
knitr::opts_chunk$set(echo = TRUE, warning=FALSE)
pander::panderOptions("table.split.table", Inf)
pander::panderOptions('round',2)
pander::panderOptions('digits',2)
pander::panderOptions('keep.trailing.zeros',TRUE)

load("data/cleaned_selected.rdata")
```


## Select Variables {.tabset}
### Initial Survey
```{r select variables}
data = all_surveys %>%
  select(session,
         age,
         education_years,
         net_income,
         starts_with("bfi_agree"),
         starts_with("bfi_consc"),
         starts_with("bfi_open"),
         starts_with("bfi_extra"),
         starts_with("bfi_neuro"),
         religiosity,
         pregnant_stress,
         duration_relationship_years,
         duration_relationship_month,
         days_with_partner,
         nights_with_partner,
         starts_with("soi_r"),
         soi_r_behavior,
         soi_r_desire,
         number_sexual_partner,
         contraception_at_all,
         contraception_method,
         contraception_approach,
         contraception_method_broad,
         contraception_meeting_partner,
         partner_attractiveness_face,
         partner_attractiveness_body,
         relationship_satisfaction_overall,
         relationship_satisfaction_2,
         relationship_satisfaction_3,
         relationship_problems_R,
         relationship_conflict_R,
         satisfaction_sexual_intercourse,
         reasons_for_exclusion,
         pregnant_trying)
```

### Diary
```{r select variables diary}
data_diary = diary %>%
  select(session,
         reasons_for_exclusion,
         high_libido,
         sex_active, sex_activity_anal_sex, sex_activity_bdsm_dom, sex_activity_bdsm_sub,
         sex_activity_cuddling, sex_activity_cunnilingus, sex_activity_cybersex,
         sex_activity_dirty_talk,
         sex_activity_fellatio, sex_activity_kissing,  sex_activity_masturbated_by_partner,
         sex_activity_masturbated_partner, sex_activity_masturbation, sex_activity_other,
         sex_activity_phone_skype_sex, sex_activity_pornography, sex_activity_sex, 
         sex_activity_touch_other, 
         sex_activity_toys, sex_activity_unclear,  sex_other, sex_solo, sex_unclear,
         days_done)
```


## Exclusion {.tabset}
### Initial Survey
```{r exclusion initial survey}
n_excluded = data %>% filter(reasons_for_exclusion != "") %>% nrow()
data = data %>% filter(reasons_for_exclusion == "")
```
`r n_excluded` people were excluded.

### Diary  {.tabset}
#### Exclusion criteria based on initial
```{r}
session_codes = data$session

data_diary = data_diary %>%
  filter(session %in% session_codes)

length(data_diary$session)
```
The `r length(unique(data_diary$session))` participants filled out `r length(data_diary$session)`.

#### Skipped diary entry
```{r}
n_skipped_diary = data_diary %>%
  filter(reasons_for_exclusion %contains% "skipped_diary_entry") %>%
  count()

data_diary = data_diary %>%
  filter(!(reasons_for_exclusion %contains% "skipped_diary_entry"))
```
`r n_skipped_diary` days were skipped.

#### Dishonest answers
```{r}
n_dishonest = data_diary %>%
  filter(reasons_for_exclusion %contains% "dishonest") %>%
  count()

data_diary = data_diary %>%
  filter(!(reasons_for_exclusion %contains% "dishonest"))
```
`r n_dishonest` days contained dishonest answers.

#### Filled out less than 14 days
```{r}
number_of_days = data_diary %>%
  group_by(session) %>%
  summarise(n = n()) %>%
  rename(number_of_days = n)
  
data_diary = left_join(data_diary, number_of_days, by = "session")

data_diary_include = data_diary %>%
  filter(as.numeric(number_of_days) >= 14)

data_diary_exclude = data_diary %>%
  filter(as.numeric(number_of_days) < 14)

data_diary = data_diary_include
```
`r length(unique(data_diary_exclude$session))` participants were excluded because they filled out less than 14 days - resulting in `r length(data_diary_exclude$session)` excluded days.

#### Summary {.active}
In total `r length(unique(data_diary$session))` participants with `r length(data_diary$session)` diary days were included for the analyses in which outcomes were based on diary information. 

## Wrangle data {.tabset .active}
### Relationship status (single vs partnered)
```{r}
data = data %>% mutate(
  relationship_status = ifelse(is.na(duration_relationship_month), "Single", "Partnered"))

qplot(data$relationship_status) + coord_flip()
```

### Relationship duration {.active .tabset}
#### Linear relationship duration
```{r}
data = data %>%
  mutate(relationship_duration = duration_relationship_years * 12 +
           duration_relationship_month)

qplot(data$relationship_duration)
```

#### Factor1 relationship duration
Divide relationship duration into quartiles
```{r}
data = data %>%
   mutate(relationship_duration_factor = 
            factor(ifelse(relationship_status == "Single",
                   "Single",
                   ifelse(relationship_duration <= 12,
                          "upto12months",
                          ifelse(relationship_duration <= 28, 
                                 "upto28months",
                                 ifelse(relationship_duration <= 52,
                                        "upto52months",
                                        ifelse(relationship_duration > 52,
                                        "morethan52months",
                                        NA))))),
                   levels = c("Single", "upto12months",
                              "upto28months", "upto52months",
                              "morethan52months")))


data %>% 
  group_by(relationship_duration_factor) %>%
  summarise(count = n()) %>%
  add_column(duration_in_years = c("Single",
                                   "upto1year",
                                   "upto2.3years",
                                   "upto4.3years",
                                   "morethan4.3years")) %>%
  select(relationship_duration_factor, duration_in_years, count) %>%
  kable()
 

qplot(data$relationship_duration_factor)


ggplot(data, aes(relationship_duration)) +
  geom_histogram(aes(fill = relationship_duration_factor), bins = 200) +
  theme(legend.title = element_blank(), legend.position = "bottom")

```

#### Factor2 relationship duration
Divide relationship duration into 8 quantiles
```{r}
quantiles = quantile(as.numeric(data$relationship_duration),
                     na.rm = T,
                     probs = c(0, 0.125, 0.25, 0.375, 0.5,0.625, 0.75, 0.875, 1))

data = data %>%
  mutate(relationship_duration_factor2 = 
           factor(ifelse(relationship_status == "Single",
                  "Single",
                  ifelse(relationship_duration <= quantiles[2],
                         "upto6months",
                         ifelse(relationship_duration <= quantiles[3],
                                "upto12months",
                                ifelse(relationship_duration <= quantiles[4],
                                       "upto20months",
                                       ifelse(relationship_duration <= quantiles[5],
                                              "upto28months",
           ifelse(relationship_duration <= quantiles[6],
                  "upto38months",
                  ifelse(relationship_duration <= quantiles[7],
                         "upto52months",
                         ifelse(relationship_duration <= quantiles[8],
                                "upto85months",
                                ifelse(relationship_duration > quantiles[8],
                                       "morethan85months",
                                       NA))))))))),
           levels = c("Single", "upto6months", "upto12months",
                      "upto20months", "upto28months",
                      "upto38months", "upto52months",
                      "upto85months", "morethan85months")))

data %>% 
  group_by(relationship_duration_factor2) %>%
  summarise(count = n()) %>%
  add_column(duration_in_years = c("Single",
                                   "upto0.5years",
                                   "upto1year",
                                   "upto1.7year",
                                   "upto2.3years",
                                   "upto3.2years",
                                   "upto4.3years",
                                   "upto7.1years",
                                   "morethan7.1years")) %>%
  select(relationship_duration_factor2, duration_in_years, count)  %>%
  kable()

qplot(data$relationship_duration_factor2) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))

ggplot(data, aes(relationship_duration)) +
  geom_histogram(aes(fill = relationship_duration_factor2), bins = 200) +
  theme(legend.title = element_blank(), legend.position = "bottom")

```


#### Factor3 relationship duration
https://sci-hub.st/10.1016/j.ssresearch.2015.01.009
Effects of relationship duration, cohabitation, and marriage on the frequency of intercourse in couples: Findings from German panel data

Relationship Duration
* 0-5 months
* 6-11 months
* 1-2 years
* 2-3 years
* 3-4 years
* 4-5 years
* 5-6 years
* 6-8 years
* 8-10 years
* 10-12 years
* 12-14 years
* 14-16 years
* > 16 years


```{r}
data = data %>%
  mutate(relationship_duration_factor3 = 
           factor(ifelse(relationship_status == "Single",
                  "Single",
                  ifelse(relationship_duration < 6,
                         "0to5months",
                         ifelse(relationship_duration < 12,
                                "6to11months",
                                ifelse(relationship_duration <= 24,
                                       "1to2years",
                                       ifelse(relationship_duration <= 36,
                                              "2to3years",
           ifelse(relationship_duration <= 48,
                  "3to4years",
                  ifelse(relationship_duration <= 60,
                         "4to5years",
                         ifelse(relationship_duration <= 72,
                                "5to6years",
                                ifelse(relationship_duration <= 96,
                                       "6to8years",
                                       ifelse(relationship_duration <= 120,
                                              "8to10years",
           ifelse(relationship_duration > 120, "morethan10years",
                  NA))))))))))),
           levels = c("Single", "0to5months", "6to11months",
                      "1to2years", "2to3years",
                      "3to4years", "4to5years",
                      "5to6years", "6to8years",
                      "8to10years", "morethan10years")))

data %>% 
  group_by(relationship_duration_factor3) %>%
  summarise(count = n()) %>%
  kable()
  
  
qplot(data$relationship_duration_factor3) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))


ggplot(data, aes(relationship_duration)) +
  geom_histogram(aes(fill = relationship_duration_factor3), bins = 200) +
  theme(legend.title = element_blank(), legend.position = "bottom")

```


