
# Datawrangling {.tabset}

## Data and Functions
```{r data and function, results='hide',message=F,warning=F}
source("0_helpers.R")
pander::panderOptions("table.split.table", Inf)
pander::panderOptions('round',2)
pander::panderOptions('digits',2)
pander::panderOptions('keep.trailing.zeros',TRUE)

load("data/cleaned_selected_wrangled.rdata")
```

## Wrangle data {.tabset .active}

### Relationship duration {.active .tabset}
#### Linear relationship duration
```{r}
qplot(data$relationship_duration)
```

#### Factor1 relationship duration
Divide relationship duration into quartiles
```{r}
data = data %>%
   mutate(relationship_duration_factor_quartiles = 
            factor(ifelse(relationship_status == "Single",
                   "Single",
                   ifelse(relationship_duration <= 12,
                          "upto12months",
                          ifelse(relationship_duration <= 28, 
                                 "upto28months",
                                 ifelse(relationship_duration <= 52,
                                        "upto52months",
                                        ifelse(relationship_duration > 52,
                                        "morethan52months",
                                        NA))))),
                   levels = c("Single", "upto12months",
                              "upto28months", "upto52months",
                              "morethan52months")))


data %>% 
  group_by(relationship_duration_factor_quartiles) %>%
  summarise(count = n()) %>%
  add_column(duration_in_years = c("Single",
                                   "upto1year",
                                   "upto2.3years",
                                   "upto4.3years",
                                   "morethan4.3years")) %>%
  select(relationship_duration_factor_quartiles, duration_in_years, count) %>%
  kable()
 

qplot(data$relationship_duration_factor_quartiles)


plot = ggplot(data, aes(relationship_duration)) +
  geom_histogram(aes(fill = relationship_duration_factor_quartiles), bins = 300) +
  labs(x = "Relationship Duration (in months)",
       y = "Count") + 
  scale_x_continuous(breaks = c(c(0:30) * 12),
                     labels = c(c(0:30) * 12)) +
  apatheme +
  #theme(legend.position = "bottom") +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
  scale_fill_manual(name = "Categories\nRelationship\nDuration",
                    labels = c("0‒12 months",
                                 "13‒28 months",
                                 "29‒52 months",
                                 "> 52 months"),
                    values = c("#1B9E77", "#7570B3", "#D95F02", "#E7298A"))

jpeg('Relationship Duration.jpg', 
     width = 700, height = 500, quality = 100)
plot
dev.off()

```

#### Factor2 relationship duration
Divide relationship duration into 8 quantiles
```{r}
quantiles = quantile(as.numeric(data$relationship_duration),
                     na.rm = T,
                     probs = c(0, 0.125, 0.25, 0.375, 0.5,0.625, 0.75, 0.875, 1))

data = data %>%
  mutate(relationship_duration_factor_finegrained = 
           factor(ifelse(relationship_status == "Single",
                  "Single",
                  ifelse(relationship_duration <= quantiles[2],
                         "upto6months",
                         ifelse(relationship_duration <= quantiles[3],
                                "upto12months",
                                ifelse(relationship_duration <= quantiles[4],
                                       "upto20months",
                                       ifelse(relationship_duration <= quantiles[5],
                                              "upto28months",
           ifelse(relationship_duration <= quantiles[6],
                  "upto38months",
                  ifelse(relationship_duration <= quantiles[7],
                         "upto52months",
                         ifelse(relationship_duration <= quantiles[8],
                                "upto85months",
                                ifelse(relationship_duration > quantiles[8],
                                       "morethan85months",
                                       NA))))))))),
           levels = c("Single", "upto6months", "upto12months",
                      "upto20months", "upto28months",
                      "upto38months", "upto52months",
                      "upto85months", "morethan85months")))

data %>% 
  group_by(relationship_duration_factor_finegrained) %>%
  summarise(count = n()) %>%
  add_column(duration_in_years = c("Single",
                                   "upto0.5years",
                                   "upto1year",
                                   "upto1.7year",
                                   "upto2.3years",
                                   "upto3.2years",
                                   "upto4.3years",
                                   "upto7.1years",
                                   "morethan7.1years")) %>%
  select(relationship_duration_factor_finegrained, duration_in_years, count)  %>%
  kable()

qplot(data$relationship_duration_factor_finegrained) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))

ggplot(data, aes(relationship_duration)) +
  geom_histogram(aes(fill = relationship_duration_factor_finegrained), bins = 200) +
  theme(legend.title = element_blank(), legend.position = "bottom")

```


#### Factor3 relationship duration
https://sci-hub.st/10.1016/j.ssresearch.2015.01.009
Effects of relationship duration, cohabitation, and marriage on the frequency of intercourse in couples: Findings from German panel data

Relationship Duration
* 0-5 months
* 6-11 months
* 1-2 years
* 2-3 years
* 3-4 years
* 4-5 years
* 5-6 years
* 6-8 years
* 8-10 years
* 10-12 years
* 12-14 years
* 14-16 years
* > 16 years


```{r}
data = data %>%
  mutate(relationship_duration_factor_schroeder = 
           factor(ifelse(relationship_status == "Single",
                  "Single",
                  ifelse(relationship_duration < 6,
                         "0to5months",
                         ifelse(relationship_duration < 12,
                                "6to11months",
                                ifelse(relationship_duration <= 24,
                                       "1to2years",
                                       ifelse(relationship_duration <= 36,
                                              "2to3years",
           ifelse(relationship_duration <= 48,
                  "3to4years",
                  ifelse(relationship_duration <= 60,
                         "4to5years",
                         ifelse(relationship_duration <= 72,
                                "5to6years",
                                ifelse(relationship_duration <= 96,
                                       "6to8years",
                                       ifelse(relationship_duration <= 120,
                                              "8to10years",
           ifelse(relationship_duration > 120, "morethan10years",
                  NA))))))))))),
           levels = c("Single", "0to5months", "6to11months",
                      "1to2years", "2to3years",
                      "3to4years", "4to5years",
                      "5to6years", "6to8years",
                      "8to10years", "morethan10years")))

data %>% 
  group_by(relationship_duration_factor_schroeder) %>%
  summarise(count = n()) %>%
  kable()
  
  
qplot(data$relationship_duration_factor_schroeder) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))


ggplot(data, aes(relationship_duration)) +
  geom_histogram(aes(fill = relationship_duration_factor_schroeder), bins = 200) +
  theme(legend.title = element_blank(), legend.position = "bottom")

```

## Analyses {.active}
### Libido
#### Factor quartiles
```{r}
library(brms)

m_simple_factor_quartiles = brm(
  diary_libido_mean ~ relationship_duration_factor_quartiles,
  data = data,
  family = gaussian())

m_complex_factor_quartiles = brm(
  diary_libido_mean ~ relationship_duration_factor_quartiles +
    contraception_hormonal +
    age + education_years + net_income + bfi_open + bfi_consc + bfi_extra +
    bfi_agree + bfi_neuro + religiosity,
  data = data,
  family = gaussian())
```

#### Factor finegrained
```{r}
m_simple_factor_finegrained = brm(
  diary_libido_mean ~ relationship_duration_factor_finegrained,
  data = data,
  family = gaussian())

m_complex_factor_finegrained = brm(
  diary_libido_mean ~ relationship_duration_factor_finegrained +
    contraception_hormonal +
    age + education_years + net_income + bfi_open + bfi_consc + bfi_extra +
    bfi_agree + bfi_neuro + religiosity,
  data = data,
  family = gaussian())
```

#### Factor Schröder
```{r}
m_simple_factor_schroeder = brm(
  diary_libido_mean ~ relationship_duration_factor_schroeder,
  data = data,
  family = gaussian())

m_complex_factor_schroeder = brm(
  diary_libido_mean ~ relationship_duration_factor_schroeder +
    contraception_hormonal +
    age + education_years + net_income + bfi_open + bfi_consc + bfi_extra +
    bfi_agree + bfi_neuro + religiosity,
  data = data,
  family = gaussian())
```


#### Comparisons {.tabset .active}
##### Simple models
```{r}
library(loo)
comp_simple_quart_fine = loo(m_simple_factor_quartiles,
                             m_simple_factor_finegrained)
comp_simple_quart_fine

comp_simple_quart_schroeder = loo(m_simple_factor_quartiles,
                             m_simple_factor_schroeder)
comp_simple_quart_schroeder

comp_simple_fine_schroeder = loo(m_simple_factor_finegrained,
                             m_simple_factor_schroeder)
comp_simple_fine_schroeder

```

##### Complex models
```{r}
comp_complex_quart_fine = loo(m_complex_factor_quartiles,
                             m_complex_factor_finegrained)
comp_complex_quart_fine

comp_complex_quart_schroeder = loo(m_complex_factor_quartiles,
                             m_complex_factor_schroeder)
comp_complex_quart_schroeder

comp_complex_fine_schroeder = loo(m_complex_factor_finegrained,
                             m_complex_factor_schroeder)
comp_complex_fine_schroeder
```

### Sex Frequency
#### Factor quartiles
```{r}
m_simple_factor_quartiles = brm(
  diary_sex_active_sex_mean ~ relationship_duration_factor_quartiles,
  data = data,
  family = gaussian())

m_complex_factor_quartiles = brm(
  diary_sex_active_sex_mean ~ relationship_duration_factor_quartiles +
    contraception_hormonal +
    age + education_years + net_income + bfi_open + bfi_consc + bfi_extra +
    bfi_agree + bfi_neuro + religiosity,
  data = data,
  family = gaussian())
```

#### Factor finegrained
```{r}
m_simple_factor_finegrained = brm(
  diary_sex_active_sex_mean ~ relationship_duration_factor_finegrained,
  data = data,
  family = gaussian())

m_complex_factor_finegrained = brm(
  diary_sex_active_sex_mean ~ relationship_duration_factor_finegrained +
    contraception_hormonal +
    age + education_years + net_income + bfi_open + bfi_consc + bfi_extra +
    bfi_agree + bfi_neuro + religiosity,
  data = data,
  family = gaussian())
```

#### Factor Schröder
```{r}
m_simple_factor_schroeder = brm(
  diary_sex_active_sex_mean ~ relationship_duration_factor_schroeder,
  data = data,
  family = gaussian())

m_complex_factor_schroeder = brm(
  diary_sex_active_sex_mean ~ relationship_duration_factor_schroeder +
    contraception_hormonal +
    age + education_years + net_income + bfi_open + bfi_consc + bfi_extra +
    bfi_agree + bfi_neuro + religiosity,
  data = data,
  family = gaussian())
```


#### Comparisons {.tabset .active}
##### Simple models
```{r}
library(loo)
comp_simple_quart_fine = loo(m_simple_factor_quartiles,
                             m_simple_factor_finegrained)
comp_simple_quart_fine

comp_simple_quart_schroeder = loo(m_simple_factor_quartiles,
                             m_simple_factor_schroeder)
comp_simple_quart_schroeder

comp_simple_fine_schroeder = loo(m_simple_factor_finegrained,
                             m_simple_factor_schroeder)
comp_simple_fine_schroeder

```

##### Complex models
```{r}
comp_complex_quart_fine = loo(m_complex_factor_quartiles,
                             m_complex_factor_finegrained)
comp_complex_quart_fine

comp_complex_quart_schroeder = loo(m_complex_factor_quartiles,
                             m_complex_factor_schroeder)
comp_complex_quart_schroeder

comp_complex_fine_schroeder = loo(m_complex_factor_finegrained,
                             m_complex_factor_schroeder)
comp_complex_fine_schroeder
```

### Plots
```{r}
ggplot(data, aes(relationship_duration_factor_finegrained, diary_libido_mean)) +
  geom_jitter() +
  stat_summary(fun.data=mean_cl_normal, geom="pointrange", color="red")

ggplot(data, aes(relationship_duration_factor_finegrained, diary_sex_active_sex_mean)) +
  geom_jitter() +
  stat_summary(fun.data=mean_cl_normal, geom="pointrange", color="red")

ggplot(data, aes(relationship_duration_factor_finegrained, partner_attractiveness_body)) +
  geom_jitter() +
  stat_summary(fun.data=mean_cl_normal, geom="pointrange", color="red")

ggplot(data, aes(relationship_duration_factor_finegrained, relationship_satisfaction_overall)) +
  geom_jitter() +
  stat_summary(fun.data=mean_cl_normal, geom="pointrange", color="red")

ggplot(data, aes(relationship_duration_factor_finegrained, satisfaction_sexual_intercourse)) +
  geom_jitter() +
  stat_summary(fun.data=mean_cl_normal, geom="pointrange", color="red")
```

