---
pagetitle: "Effects of Contraception"
csl: apa-custom-no-issue.csl
nocite: |
    @R @packrat @rmarkdown @knitr @formr @pander @lubridate @stringr @broom @effects @ggplot2 @tidyr @svglite @dplyr @reshape2 @lmerTest @devtools @formatR @lazyeval @scales @car @xlsx @lme4
---

# Effects of Contraception {.tabset .tabset-sticky}

```{r message=FALSE, warning=FALSE}
# bibliography: packrat_bibliography.bibtex
source("0_helpers.R")
```

# To the [codebook](2_codebook.html)


We used these [helper functions](0_helpers.html). These are the [.Rprofile settings](.Rprofile.html).

1. First we [wrangled the data](0_import_data.html).
2. Then we looked at some [descriptives](1_descriptives.html).
3. Then we [analysed](2_analyses.html) it.
3. And [tested robustness](3_robustness_analyses_new.html).

## Authors & Acknowledgements {.tabset .tabset-sticky}

### Authors
Laura J. Botzet & Ruben Arslan

### Acknowledgements {.active}


#### Package bibliography {.tabset .tabset-sticky}

##### Session info
```{r}
# Make packrat bibliography
# packrat_bibliography(overwrite_bib = TRUE, silent = TRUE)
# Turn the .R files into .Rmd files, turn those into .html, remove the .Rmd files
# spin_R_files_to_site_html()
sessionInfo()
```

##### References {.active}
