---
pagetitle: "Contraception"
csl: apa-custom-no-issue.csl
nocite: |
    @R @packrat @rmarkdown @knitr @formr @pander @lubridate @stringr @broom @effects @ggplot2 @tidyr @svglite @dplyr @reshape2 @lmerTest @devtools @formatR @lazyeval @scales @car @xlsx @lme4
---

# Hormonal Contraception and Sexuality: Causal Effects, Unobserved Selection, or Reverse Causality? {.tabset .tabset-sticky}

```{r message=FALSE, warning=FALSE}
# bibliography: packrat_bibliography.bibtex
source("0_helpers.R")
```

We used these [helper functions](0_helpers.R).

1. First [exclusion criteria were applied](1_exclusion.html).
2. Then [scales were aggregated and contraception groups were formed](2_datawrangling.html).
3. Some [descriptives](3_descriptives.html) and a [codebook](4_codebook.html) can be found here.
4. All [analyses of selection effects](5_analyses_selection.html) are available here.
5. Here are the [analyses of effects of contraceptive use and congruent contraceptive use](6_analyses_effects.html) including controlled and uncontrolled models.
6. In a last step, [sensitivity of effects to unobserved confounders](7_analyses_sensitivity.html) was estimated.
7. Click [here](8_plots.html) for all plots of the manuscript.

Here are further information about the [factor relationship duration](99_relationship_duration.html).

#### Package bibliography {.tabset .tabset-sticky}

##### Session info
```{r}
# Make packrat bibliography
# packrat_bibliography(overwrite_bib = TRUE, silent = TRUE)
# Turn the .R files into .Rmd files, turn those into .html, remove the .Rmd files
# spin_R_files_to_site_html()
sessionInfo()
```

##### References {.active}
